### 2024-02-15 01_latex/MScThesis_Econ.tex
Initial Commit and Document Setup

\documentclass[12pt,a4paper]{article}
\usepackage[
	left 	= 2.54cm,
	right 	= 2.54cm, 
	top 		= 2.54cm,
	bottom 	= 2.54cm,
]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[OT1]{fontenc}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{caption}

\usepackage[style=apa, backend=biber]{biblatex}
\addbibresource[]{ref.bib}
\addbibresource[]{DevEcon_Project.txt}
\renewcommand{\baselinestretch}{1.25}

\usepackage[hidelinks]{hyperref}
\hypersetup{
	colorlinks = true,
	urlcolor   = blue,
	linkcolor  = black, 
	citecolor  = blue, 
}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{\slshape Unterweger}
\chead{}
\rhead{\slshape \nouppercase{\leftmark}}

\usepackage{titlesec,xcolor}
\titleformat{\section}{\bfseries}{\thesection}{0.5em}{}
\titlespacing{\section}{0pt}{3ex plus 1ex minus 0.2ex}{10pt}
\setlength{\headheight}{14.49998pt}

\usepackage{titlesec,xcolor}
\titleformat{\subsection}{\bfseries}{\thesubsection}{0.5em}{}
\titlespacing{\subsection}{0pt}{3ex plus 1ex minus 0.2ex}{10pt}
\setlength{\headheight}{14.49998pt}

%------------------------------------------------------------------%

\author{Lucas Paul Unterweger}
\title{On the Duality of Frequentist Point Estimates and Bayesian Shrinkage Priors: An Extension based on the Triple-Gamma-Prior}

\begin{document}

\begin{titlepage}
\center
\vfill
\includegraphics[scale=0.1]{WU.png}
\vfill
\begin{tabular}[t]{lc}
Student-ID:  & 11913169 \\
Degree Program: & 
Master of Science in Economics (Science Track) \\
Examiner: & Peter Knaus, PhD \\
Submission date: & TBA \\
\end{tabular}
\vfill
{\large \textbf{On the Duality of Frequentist Point Estimates and Bayesian Shrinkage Priors}\\
\normalsize \textit{An Extension based on the Triple-Gamma-Prior}}
\vfill
by\\ \vspace{3mm}
{\Large Lucas Unterweger \href{https://github.com/therealLucasPaul}{\includegraphics[scale=0.01]{GitHub.png}}}\\
(Student-ID: 11913169)\\
\vfill

\thispagestyle{empty}
\pagebreak
\end{titlepage}
\newcounter{savepage}
\pagenumbering{roman}
\thispagestyle{empty}

\begin{abstract}
Lorem ipsum...
\end{abstract}

\clearpage
\thispagestyle{plain}
\tableofcontents
\pagebreak
\setcounter{savepage}{\arabic{page}}
\pagenumbering{arabic}

\pagebreak
\section{Introduction}
\section{Theoretical Section}
\section{Simulation Section}

\pagebreak
\pagenumbering{roman}
\setcounter{page}{\thesavepage}
\pagestyle{plain}
\addcontentsline{toc}{section}{References}
%\bibliographystyle{apalike}
%\bibliography{ref.bib}
\printbibliography[]
\clearpage
\appendix
\end{document}

### 2024-02-15 02_simulation/simulation_script.R
Add on Prev Commit

@@ -1,0 +1,2 @@
+# Simulation Script
+## Master's Thesis 2024

### 2024-03-11 01_latex/MScThesis_Econ.tex
Some test code on LASSO

@@
 \pagebreak
+%----- Introduction -----
 \section{Introduction}
+
+%----- Literature Review -----
+\section{Literature Review}
+\subsection{Bayesian View}
+\subsection{Frequentist View}
+\subsection{Machine Learning Literature combating Model Complexity}
+
+%----- Theoretical Section
 \section{Theoretical Section}
+\subsection{Model Complexity}
+\subsection{Under- and Overfitting}
+\subsubsection{Regularization}
+\subsubsection{Shrinkage Priors}
+\subsection{Duality of the Ridge Regression}
+%----- Model Setup and Derivation
+\section{Model Setup and Derivation}
+Mathematical derivation of TGP into frequentist view?
+
+%----- Simulation Section
 \section{Simulation Section}
+Use the earlier derivation, code up the functions and simulate data to check behaviour for different datasets. Compare to base OLS, Ridge and Lasso Regression?
+\subsection{Computational Performance}
+\subsection{Implementation as R Package?}
+
+%----- Small Applied Section
+\section{Small Applied Section}
+Here I am planning to apply the TGP using Peter's Bayesian Package and the self coded frequentist code on a small dataset.
+\section{Conclusion}
+\section{Possible Extensions and Criticism}
+\section{References}
 

### 2024-04-09 01_latex/MScThesis_Econ.tex
First Implementation of TGR Estimate
- Basic Mathematical Derivation
- First implementation of Triple Gamma Regularization Estimate

@@
 \usepackage{caption}
+\usepackage{amssymb}
 
@@
 
+%% Command Overrides
+\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
+\newcommand{\MC}{\textbf{(Missing Citation)}} %Command to signal missing citations
+
 %------------------------------------------------------------------%
@@
 \vfill
-{\large \textbf{On the Duality of Frequentist Point Estimates and Bayesian Shrinkage Priors}\\
+{\large \textbf{Triple-Gamma-Regularization} \textit{or}\\ \textbf{On the Duality of Frequentist Point Estimates and Bayesian Shrinkage Priors}\\
 \normalsize \textit{An Extension based on the Triple-Gamma-Prior}}
@@
 \section{Introduction}
-
+Willam of Ockham, born in Ockham, Surrey, probably lived between 1287 and 1348 and is nowadays recognized as a pre-eminent philosopher of the middle ages.
+Although     his name itself is no common knowledge, a principle carrying his name is: \textit{Ockham's Razor}.
+Interestingly, the main formulation of the principle (\textit{Entia non sunt multiplicanda praeter necessitatem} [plurality should not be posited without necessity]) can not be traced back to Ockham directly, but variations of it can be found in Ockham's writings.
+Since then nonetheless, the principle has long been used by statisticians and other researchers as a a scientific credo to capture the notion that "the simpler of two explanations is to be preferred" \parencite{Lazar2010}.
 %----- Literature Review -----
@@
 %----- Model Setup and Derivation
+\newpage
 \section{Model Setup and Derivation}
-Mathematical derivation of TGP into frequentist view?
+Coming to the theoretical framework of the \textit{triple-gamma-regularization}, let's assume we have a response variable $y$ and $p$ predictors along with $n$ data points.
+More formally, let $y=[y_1  \quad y_2 \cdots y_n]^T$ and $x_i = [x_{i1} \quad x_{i2} \cdots x_{in}]^T$ with $\forall i\in \{1,...,n\}: y_i, x_i \in \mathbb{R}$.
+Here, $x_i$ is the $i$-th predictor, thus resulting in the design matrix $X = [x_1 \quad x_2 \cdots x_p]$.
+\\
 
+Starting from the Bayesian framework, the standard linear regression model is given by
+\[
+y_i = x_i^T\cdot \beta + \varepsilon_i \quad i\in \{1,...,n\} 
+\]
+with the assumed distribution of $\varepsilon_i \sim N(0,\sigma^2)$.
+Thus it follows that $y\sim N_n(X\beta,\sigma^2I)$.
+The posterior distribution of the parameter vector $\beta$, according to Bayes' Rule, is then proportional to the product of the likelihood of the data and the prior distribution, which can be seen in equation \ref{eq:bayes}.
+\begin{equation}\label{eq:bayes}
+p(\beta|y, X, \sigma^2) \propto \mathcal{L}(y|\beta, \sigma^2, X)\times p(\beta)
+\end{equation}
+
+As stated above, each data point $y_i$ is assumed to be identically and independently drawn from a normal distribution with mean $X\beta$ and variance $\sigma_i^2$, thus:
+\begin{align}
+\mathcal{L}(\mathbf{y}|\beta, \sigma^2, X) 	&= \prod_i^n p(y_i|\beta, \sigma^2, X_i) \nonumber\\
+						&= \prod_i^n \frac{1}{\sqrt{2\pi\sigma^2}} \exp\left(-\frac{1}{2}\left(\frac{x_i-\mu}{\sigma}\right)^2\right) \nonumber\\
+						&= \frac{1}{(2\pi\sigma^2)^{n/2}}\exp\left(-\frac{1}{2\sigma^2}(\mathbf{y}-\mathbf{X}\beta)^\top(\mathbf{y}-\mathbf{X}\beta)\right) \label{eq:likelihood}
+\end{align}
+
+The log of the likelihood function is then given by 
+\begin{align*}
+\log \mathcal{L}( \mathbf{y} |\beta, \sigma^2 , \mathbf{X}) &= \log \left( \frac{1}{(2\pi\sigma^2)^{n/2}} \exp\left(-\frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^\top (\mathbf{y} - \mathbf{X}\beta)\right) \right) \\
+&= \log \left( \frac{1}{(2\pi\sigma^2)^{n/2}} \right) + \log \exp\left(-\frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^\top (\mathbf{y} - \mathbf{X}\beta)\right) \\
+&= -\frac{n}{2} \log(2\pi\sigma^2) - \frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^\top (\mathbf{y} - \mathbf{X}\beta)\\
+&\propto - \frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^\top (\mathbf{y} - \mathbf{X}\beta) = - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2\\
+\end{align*}
+
+The marginal prior distribution for the parameter vector $\beta$ stems from the Triple-Gamma-Prior constructed in \textcite{TGP2020} given in formula Theorem 1 (a) and is given by
+\begin{align*}
+p(\sqrt{\beta_j}|\phi^\xi, a^\xi, c^\xi) &= \frac{\Gamma(c^\xi + \frac{1}{2})}{\sqrt{2\pi \phi^\xi}\cdot B(a^\xi, c^\xi)}\cdot U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\\
+&\propto U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)
+\end{align*}
+As this prior is specified for the parameter $\sqrt{\beta_j}$, we transform the prior by squaring the parameter to gain
+\begin{align*}
+p(\beta_j|\phi^\xi, a^\xi, c^\xi) &\propto U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)
+\end{align*}
+Now, assuming that the parameters are independent a priori, the prior distribution is given by
+\begin{align}
+p(\beta) 	&= \prod_j^p p(\beta_j) \nonumber\\
+			&= \prod_j^p p(\beta_j|\phi^\xi, a^\xi, c^\xi) \nonumber\\
+			&\propto \prod_j^p U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right) \nonumber\\
+			&= \prod_j^p \frac{1}{\Gamma(c^\xi + \frac{1}{2})}\int_0^\infty e^{-(\frac{\beta_j^2}{2\phi^\xi})t}t^{c^\xi + \frac{1}{2}-1}(1+t)^{\frac{3}{2}-a^\xi-c^\xi + \frac{1}{2}-1}dt \nonumber\\
+			&\propto \prod_j^p \int_0^\infty \exp\left(-\frac{\beta_j^2}{2\phi^\xi}t\right)t^{c^\xi - \frac{1}{2}}(1+t)^{1-a^\xi-c^\xi} dt \label{eq:prior}
+\end{align}
+
+Here, in line 1 the assumption of independence between the parameters has been used to describe the distribution of the parameter vector as the product of its individual parameter distributions.
+In line 2, the marginal prior from \textcite{TGP2020} has been used as the prior distribution for each individual parameter $\beta_j$.
+In line 3, scaling parameters have been removed by using the proportionality assumption.
+The last two lines of the derivation insert the definition of the confluent hyper-geometric function of the second kind and again apply proportionality.\\
+
+Taking the $\log$ of the prior distribution and using the properties of the logarithmic function yields the general result
+\[
+\log(p(\beta))=\log(\prod_j^p p(\beta_j|\phi^\xi, a^\xi, c^\xi))=\sum_j^p \log(p(\beta_j|\phi^\xi, a^\xi, c^\xi))
+\]
+
+A common approach to estimation in regularization settings is the \textit{maximum a posteriori probability (MAP)} estimator \MC ,which is defined as
+\[
+\hat{\beta}_{MAP}(x) = \underset{\beta \in \mathbb{R}^p}{\argmax}\left\{f(x|\beta)g(\beta)\right\}
+\]
+where $f(x|\beta)$ describes the the probability density function of a variable $x$, which is parametrized by the parameter vector $\beta$.
+The second function $g(\beta)$ incorporates our prior information about the parameter vector $\beta$ into the optimization problem.\\
+
+Returning to our specific problem at hand, the posterior distribution of our parameter vector $\mathbf{\beta}$ can be retrieved by applying Bayes' theorem and the previously gained results in equations \ref{eq:prior} and \ref{eq:likelihood}.
+Thus, the posterior distribution of the parameter vector $\beta$ is proportional to
+\begin{align}
+p(\beta|y, X, \sigma^2) 	&\propto p(y|X,\beta,\sigma)\times p(\beta) \nonumber\\
+						&\propto \frac{1}{(2\pi\sigma^2)^{n/2}}e^{-\frac{1}{2\sigma^2}(y-X\beta)^T(y-X\beta)} \times \prod_j^p U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\label{eq:posterior}
+\end{align}
+
+Making use of the monotonicity of the logarithmic function and seeing that it is easier to optimize the log-posterior, Taking the log of the posterior probability distribution, we take the log of result \ref{eq:posterior}.
+\begin{align}
+\log(\beta| X, y, \sigma^2) 	&= \log\left(\frac{1}{(2\pi\sigma^2)^{n/2}}\right) - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \log\left(\prod_j^p U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\right)\nonumber\\
+							&= \log\left(\frac{1}{(2\pi\sigma^2)^{n/2}}\right) - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \sum_j^p \log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\right)\nonumber\\
+							&\propto -\frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \sum_j^p \log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\right)\nonumber\\
+\end{align}
+By minimizing the negative log-posterior, we can retrieve the \textit{maximum a posteriori probability (MAP)} estimator using \textbf{Triple-Gamma-Regularization}:
+\begin{equation}
+\hat{\beta}_{MAP} = \underset{\beta \in \mathbb{R}^p}{\argmin} \left(\frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 - \sum_j^p \log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\right)\right)
+\end{equation}
+
+\newpage
+\textbf{BREAK}
+\begin{equation}
+U(a,b,z) = \frac{1}{\Gamma(a)}\int_0^\infty e^{-zt}t^{a-1}(1+t)^{b-a-1}dt
+\end{equation}
 %----- Simulation Section

### 2024-04-09 03_notes/mathematical_notes.tex
First Implementation of TGR Estimate
- Basic Mathematical Derivation
- First implementation of Triple Gamma Regularization Estimate

\documentclass[12pt,a4paper]{article}
\usepackage[
	left 	= 2.54cm,
	right 	= 2.54cm, 
	top 		= 2.54cm,
	bottom 	= 2.54cm,
]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[OT1]{fontenc}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{caption}

\usepackage[style=apa, backend=biber]{biblatex}
\addbibresource[]{ref.bib}
\addbibresource[]{DevEcon_Project.txt}
\renewcommand{\baselinestretch}{1.25}

\usepackage[hidelinks]{hyperref}
\hypersetup{
	colorlinks = true,
	urlcolor   = blue,
	linkcolor  = black, 
	citecolor  = blue, 
}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{\slshape Unterweger}
\chead{}
\rhead{\slshape \nouppercase{\leftmark}}

\usepackage{titlesec,xcolor}
\titleformat{\section}{\bfseries}{\thesection}{0.5em}{}
\titlespacing{\section}{0pt}{3ex plus 1ex minus 0.2ex}{10pt}
\setlength{\headheight}{14.49998pt}

\usepackage{titlesec,xcolor}
\titleformat{\subsection}{\bfseries}{\thesubsection}{0.5em}{}
\titlespacing{\subsection}{0pt}{3ex plus 1ex minus 0.2ex}{10pt}
\setlength{\headheight}{14.49998pt}

\author{Lucas Paul Unterweger}
\title{Mathematical Notes MSc Thesis}
\begin{document}
\maketitle

\section{Important Prior Distributions}

\textbf{Normal Distribution}
\[
f(x|\mu, \sigma) = \frac{1}{\sigma\sqrt{2\pi}} e^{-\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^2}
\]

\textbf{Gamma Distribution}
\begin{equation*}
f(x|\alpha,\beta) = \frac{\beta^\alpha}{\Gamma(\alpha)} x^{\alpha-1} e^{-\beta x}, \quad x > 0
\end{equation*}
where $\alpha$ is the shape parameter, $\beta$ is the rate parameter, and $\Gamma(\cdot)$ is the gamma function.

\textbf{Beta Distribution}
\begin{equation*}
f(x|a,b) = \frac{x^{a-1}(1-x)^{b-1}}{B(a,b)}
\end{equation*}
where $x \in [0,1]$, $a > 0$, $b > 0$, and $B(a,b)$ is the Beta function defined as:
\begin{equation*}
B(a,b) = \frac{\Gamma(a)\Gamma(b)}{\Gamma(a+b)}
\end{equation*}
where $\Gamma$ is the gamma function.\\

\section{Other Functions}
\textbf{Confluent Hyper-Geometrics Function of the second kind (Tricomi's (confluent hypergeometric) function)}
\[
U(a,b,z) = \frac{1}{\Gamma(a)}\int_0^\infty e^{-zt}t^{a-1}(1+t)^{b-a-1}dt
\]
\textbf{Marginal Prior with $\phi^\xi = \frac{2c^\xi}{\kappa_B^2a^\xi}$}
\begin{align*}
p(\sqrt{\theta_j}|\phi^\xi, a^\xi, c^\xi) &= \frac{\Gamma(c^\xi + \frac{1}{2})}{\sqrt{2\pi \phi^\xi}\cdot B(a^\xi, c^\xi)}\cdot U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\theta_j}{2\phi^\xi}\right)\\
&\propto U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\theta_j}{2\phi^\xi}\right)
\end{align*}

\section{Bayesian Regression}
Consider a Bayesian regression model where the relationship between the independent variable $x$ and the dependent variable $y$ is modeled as:
\begin{equation*}
y = \beta_0 + \beta_1 x + \epsilon
\end{equation*}
where $\epsilon$ is the error term assumed to follow a normal distribution with mean $0$ and variance $\sigma^2$.

We assume the following conjugate prior distributions for the parameters:
\begin{align*}
\beta_0 & \sim \mathcal{N}(\mu_0, \tau_0^2) \\
\beta_1 & \sim \mathcal{N}(\mu_1, \tau_1^2) \\
\sigma^2 & \sim \text{Inv-Gamma}(\alpha, \beta)
\end{align*}

The likelihood function for the observed data $(x_i, y_i)$, $i = 1, \ldots, n$, is given by:
\begin{equation*}
L(\beta_0, \beta_1, \sigma^2 | x, y) = \prod_{i=1}^{n} f(y_i | \beta_0, \beta_1, x_i, \sigma^2)
\end{equation*}
where $f(y_i | \beta_0, \beta_1, x_i, \sigma^2)$ is the probability density function (PDF) of the normal distribution.

The posterior distribution of the parameters, denoted as $\pi(\beta_0, \beta_1, \sigma^2 | x, y)$, is proportional to the product of the likelihood function and the prior distributions:
\begin{equation*}
\pi(\beta_0, \beta_1, \sigma^2 | x, y) \propto L(\beta_0, \beta_1, \sigma^2 | x, y) \times \pi(\beta_0) \times \pi(\beta_1) \times \pi(\sigma^2)
\end{equation*}

The maximum a posteriori (MAP) estimation involves maximizing the log-posterior function:
\begin{equation*}
\ell(\beta_0, \beta_1, \sigma^2 | x, y) = \sum_{i=1}^{n} \log f(y_i | \beta_0, \beta_1, x_i, \sigma^2) + \log \pi(\beta_0) + \log \pi(\beta_1) + \log \pi(\sigma^2)
\end{equation*}
with respect to the parameters $\beta_0$, $\beta_1$, and $\sigma^2$.

The estimates of the parameters, denoted as $\hat{\beta}_0$, $\hat{\beta}_1$, and $\hat{\sigma}^2$, can be obtained by maximizing the log-posterior function.

\newpage

\section{Derviation Idea}
\begin{equation*}
post(\beta, \sigma^2 | x, y) \propto L(\beta, \sigma^2 | x, y) \times prior(\beta, \sigma^2)
\end{equation*}
\end{document}

### 2024-05-08 01_latex/MScThesis_Econ.tex
Sicherheitscommit
Changes in Derivation Section; Altered Chapter Structure;

@@
 \addbibresource[]{ref.bib}
-\addbibresource[]{DevEcon_Project.txt}
 \renewcommand{\baselinestretch}{1.25}
@@
 %----- Literature Review -----
+
 \section{Literature Review}
@@
 \subsection{Frequentist View}
-\subsection{Machine Learning Literature combating Model Complexity}
 
 %----- Theoretical Section
-\section{Theoretical Section}
+\section{Theoretical Section}\label{sec:theorysuper}
 \subsection{Model Complexity}
+Overfitting is a problem.
+Especially when dimensionality issues arise.
+For example, 50 observations and 20 features.
+Model will perform well/almost perfect on training data, but will do terrible on training data.\\
 \subsection{Under- and Overfitting}
+
+General problem: Fit vs. Complexity. What to choose and where is the optimal balance?
+
+Solutions (find source, seen in LMU course): (1) More data (Not always feasible) (2) Better data (Same issue) (3) Reduce Model Complexity (Regularization) (4) Less aggressive optimization (Maybe short review; Idea: Stop optimization when generalization error degrades)
+
 \subsubsection{Regularization}
-\subsubsection{Shrinkage Priors}
+Ad Solution (3) because it is relatively easy to implement: Simple approach => Start with simplest model and iteratively add one feature OR iteratively get rid of feature by feature.
+(Problem: Very arbitrary and hard to reasonably do) Thus, adjust risk function minimization.
+Important: Regularization adjusts generalization error, not training error!
+
+Short break: Talk about Taxonomy by Kukacka et al 2017 on the differing use of the term "regularization"
+
+What is needed: 
+\[
+R_{reg}(\beta) = R_{emp}(\beta)+ \lambda \cdot J(\beta)
+\]
+where $R_{emp}(\beta) = \sum_i^n L(y_i, f(x_i, \beta))$.
+Note: Regularization term does not depend on data, just on parametrization.
+$\lambda$ controls the strength of regularization.
+Thus, $\lambda = 0$ means simple MSE optimization and $\lambda \to \infty$ chooses simplest model.
+As $\lambda$ is set manually, this also bears some problems.
+However, typical solution is cross-validation.
+\subsubsection{Short Deviation to Bayesian Shrinkage Priors}
+
 \subsection{Duality of the Ridge Regression}
+
+\subsection{Triple-Gamma-Prior by \textcite{TGP2020}}
+
 %----- Model Setup and Derivation
@@
 
-The marginal prior distribution for the parameter vector $\beta$ stems from the Triple-Gamma-Prior constructed in \textcite{TGP2020} given in formula Theorem 1 (a) and is given by
+The marginal prior distribution for the parameter vector $\beta$ stems from the Triple-Gamma-Prior constructed in \textcite{TGP2020} given in Theorem 1 (a) and is given by
 \begin{align*}
@@
 \end{align*}
+Here, $U(a,b,z)$ refers the confluent hyper-geometric function of the second kind which was introduced by \textcite{Tricomi1947}.
 As this prior is specified for the parameter $\sqrt{\beta_j}$, we transform the prior by squaring the parameter to gain
@@
 In line 3, scaling parameters have been removed by using the proportionality assumption.
-The last two lines of the derivation insert the definition of the confluent hyper-geometric function of the second kind and again apply proportionality.\\
+The last two lines of the derivation insert the integral representation of the confluent hyper-geometric function of the second kind, $U(a,b,z)$, which is valid in the case of a positive real part for the first parameter ($\mathfrak{Re}(a) > 0$) and again apply proportionality.\\
 
@@
 p(\beta|y, X, \sigma^2) 	&\propto p(y|X,\beta,\sigma)\times p(\beta) \nonumber\\
-						&\propto \frac{1}{(2\pi\sigma^2)^{n/2}}e^{-\frac{1}{2\sigma^2}(y-X\beta)^T(y-X\beta)} \times \prod_j^p U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\label{eq:posterior}
+						&\propto \frac{1}{(2\pi\sigma^2)^{n/2}}e^{-\frac{1}{2\sigma^2}(y-X\beta)^T(y-X\beta)} \times \prod_j^p U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\label{eq:posterior}
 \end{align}
@@
 \begin{align}
-\log(\beta| X, y, \sigma^2) 	&= \log\left(\frac{1}{(2\pi\sigma^2)^{n/2}}\right) - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \log\left(\prod_j^p U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\right)\nonumber\\
-							&= \log\left(\frac{1}{(2\pi\sigma^2)^{n/2}}\right) - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \sum_j^p \log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\right)\nonumber\\
-							&\propto -\frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \sum_j^p \log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\right)\nonumber\\
+\log(\beta| X, y, \sigma^2) 	&= \log\left(\frac{1}{(2\pi\sigma^2)^{n/2}}\right) - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \log\left(\prod_j^p U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right)\nonumber\\
+							&= \log\left(\frac{1}{(2\pi\sigma^2)^{n/2}}\right) - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta^2}_2^2 + \sum_j^p \log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\right)\nonumber\\
+							&\propto -\frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \sum_j^p \log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right)\nonumber\\
 \end{align}
-By minimizing the negative log-posterior, we can retrieve the \textit{maximum a posteriori probability (MAP)} estimator using \textbf{Triple-Gamma-Regularization}:
-\begin{equation}
-\hat{\beta}_{MAP} = \underset{\beta \in \mathbb{R}^p}{\argmin} \left(\frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 - \sum_j^p \log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\right)\right)
+
+To align with the general specification structure of regularization problems, which can be seen from equation \textbf{missEQ}, a parameter $\lambda$ will be multiplicatively added in front of the penalty term, which makes it possible to adjust the strength of the influence that the penalty has on the chosen parameters.
+By minimizing the negative log-posterior adjusted with $\lambda$, we can retrieve the \textit{maximum a posteriori probability (MAP)} estimator using \textbf{Triple-Gamma-Regularization}:
+\begin{equation}\label{eq:tgr}
+\hat{\beta}_{MAP} = \underset{\beta \in \mathbb{R}^p}{\argmin} \left(\frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \lambda \sum_j^p -\log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right)\right)
 \end{equation}
@@
 \newpage
-\textbf{BREAK}
-\begin{equation}
-U(a,b,z) = \frac{1}{\Gamma(a)}\int_0^\infty e^{-zt}t^{a-1}(1+t)^{b-a-1}dt
-\end{equation}
+\subsection{Varying the Hyperparameters}
+After closer inspection of equation \ref{eq:tgr}, it can easily be seen that this resembles the general penalized regression already seen in \textcite{ESLpage398} and in section \ref{sec:theorysuper} as $R(\beta) + \lambda\cdot J(\beta)$.
+The first term, alos called the empirical loss in machine learning literature, is the widely known residual sum of squares:
+\[
+R(\beta)=\frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2
+\] 
+The second part of the optimization problem can be viewed as a penalty imposed on the total risk based on the size of the estimates:
+\[
+J(\beta) = \sum_j^p -\log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right)
+\]
+In contrast to the \textit{LASSO} penalty, which uses the the absolute value of the coefficient, or the \textit{Ridge} penalty, which uses the square of the estimate, this penalty derived from \textcite{TGP2020} is based on the $\log$ of the confluent hyper-geometric of the second kind.
+Notably, this penalty term has three additional hyper-parameters: $c^\xi$, $a^\xi$ and $\kappa$ as $\phi^\xi = (2c^\xi)/(\kappa^2_B a^\xi)$.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/simpleTGpenalty.png}
+\caption{Basic Representation of the Triple-Gamma-Penalty using Hyperparameters $c^\xi = 0.1, \kappa_B = 2, a^\xi = 0.75$ compared to \textit{LASSO} and \textit{Ridge} Penalties}
+\label{fig:basicTGPen}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInA.png}
+\caption{Triple-Gamma-Penalty using different values of $a^\xi$}
+\label{fig:basicTGPen}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInC.png}
+\caption{Triple-Gamma-Penalty using different values of $c^\xi$}
+\label{fig:basicTGPen}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInKappa.png}
+\caption{Triple-Gamma-Penalty using different values of $\kappa_B$}
+\label{fig:basicTGPen}
+\end{figure}
+
+\subsection{Restricted Strong Convexity (RSC) of the Triple-Gamma-Regularization}
+
+\subsection{Alternative Specification (with +1 to mimic artan)}
+
+\subsection{Approaches to Estimation}
+
 %----- Simulation Section
@@
 \subsection{Computational Performance}
-\subsection{Implementation as R Package?}
+Talking about Gradient Descent Methods in more depth. Why Gradient Clipping. Maybe more modern estimation techniques? 
+\subsection{Implementation as Python Library}
+
+How to use it. 
+Explanation of Functions. Input - Output Tables
 

### 2024-05-08 02_simulation/log_hyperu.py

@@ -84,7 +84,7 @@ class log_hyperu_shift(torch.autograd.Function):
     def forward(ctx, a, b, x):
 
         u_res = robust_hyperu(a, b, x)
-        result = torch.log(u_res) # TODO: Add +1 for shift version
+        result = torch.log(u_res+1)
 
         ctx.mark_non_differentiable(a)
         ctx.mark_non_differentiable(b)

### 2024-05-08 02_simulation/tgr.py

@@ -1,0 +1,58 @@
+# this is the base package for triple gamma regularizazion
+import torch
+import torch.nn as nn
+import torch.optim as optim
+
+import log_hyperu as hyperu
+
+# Triple-Gamma-Regularization
+
+class TripleGammaRegularization(nn.Module):
+    def __init__(self, num_features):
+        super(TripleGammaRegularization, self).__init__()
+        self.linear = nn.Linear(4, 1)
+
+    def forward(self, x):
+        return self.linear(x)
+
+def TripleGammaReg_Loss(Y_HAT, Y, coefficients, lamda, a, c, kappa, norm):
+    # Compute Phi value for third parameter input of the hypergeometric function
+    phi = (2*c)/((kappa**2)*a)
+    
+    # Compute the squared loss ||y - X*beta||^2_2 (Using the variables: ||Y - Y_HAT||^2_2
+    squared_loss = nn.MSELoss()(Y_HAT, Y)
+    
+    # Compute the penalty term using Triple Gamma Regularization
+    if(norm == True):
+        penalty_term = torch.sum(-hyperu.log_hyperu(torch.tensor([[c+0.5]]),torch.tensor([[1.5-a]]),(coefficients**2)/(2*phi))+hyperu.log_hyperu(torch.tensor([[c+0.5]]),torch.tensor([[1.5-a]]),torch.tensor([[0.0]])))
+    else:
+        penalty_term = torch.sum(-hyperu.log_hyperu(torch.tensor([[c+0.5]]),torch.tensor([[1.5-a]]),(coefficients**2)/(2*phi)))
+
+
+    # Copmute the sum of the squared loss and the penalty term
+    total_loss = squared_loss + lamda*penalty_term
+    
+    return total_loss
+
+def TripleGammaModel(X, y, penalty, a, c, kappa,  norm=True, num_epochs=1000, lr=0.01):
+    model = TripleGammaRegularization(X.shape[1])
+    optimizer = optim.SGD(model.parameters(), lr=lr)
+    coef_list = list()
+    loss_list = list()
+
+    for epoch in range(num_epochs):
+        optimizer.zero_grad()
+        outputs = model(X)
+        loss = TripleGammaReg_Loss(outputs, y, model.linear.weight, penalty, a, c, kappa, norm)
+        loss.backward()
+        coef_list.append(model.linear.weight)
+        loss_list.append(loss)
+        
+        #Gradient Clipping???
[…]

### 2024-05-08 01_latex/MScThesis_Econ.tex
Midday Commit
Continued with Theoretical Regularization Section

@@
 \usepackage{amssymb}
+
+% Colorbox for Notes ------
+\usepackage{tcolorbox}
+\usepackage{xcolor}
+\definecolor{lightblue}{RGB}{173,216,230}
+
+\newenvironment{lightbluebox}{%
+    \begin{tcolorbox}[colback=lightblue, colframe=lightblue, fontupper=\itshape]%
+}{%
+    \end{tcolorbox}%
+}
+%---------------------------
 
@@
 Since then nonetheless, the principle has long been used by statisticians and other researchers as a a scientific credo to capture the notion that "the simpler of two explanations is to be preferred" \parencite{Lazar2010}.
-%----- Literature Review -----
-
-\section{Literature Review}
-\subsection{Bayesian View}
-\subsection{Frequentist View}
 
@@
 \subsubsection{Regularization}
+
+Focusing on option three to battle model complexity, regularization methods have been studied thoroughly since the 1990s.
+However, the emergence of data science - and especially machine learning - as a standalone field of study has led to a broader meaning of the term \textit{regularization}.
+This phenomenon has been discussed by \textcite{Taxonomy2017}, where the authors establish a taxonomy to distinguish between multiple different definitions.
+In the traditional sense, as can be seen in \textcite[167--170]{ESL2009}, \textit{regularization} refers to a general class of problems of the form
+\[
+\underset{f \in \mathcal{H}}{\min}\left\{\sum_{i=1}^N L(y_i, f(x_i)) + \lambda{J}(f)\right\}
+\]
+where $L(.)$ refers to a loss function defined as some function of the true values and the predicted values and $J(f)$ is penalty based on the chosen functional from a space of functions $\mathcal{H}$.
+In the context of penalized linear regression, this is equivalent to finding the set of risk minimizing coefficients $\hat{\beta}$ from the set of all possible combinations of coefficients $\boldsymbol{\beta}$.
+\MC Thus, resulting in the general class of regularization problems of the form:
+\[
+\underset{\beta \in \boldsymbol{\beta}}{\min}\left\{\sum_{i=1}^N L(y_i, f_\beta(x_i)) + \lambda{J}(\beta)\right\}
+\]
+where $f_\beta(x_i)$ is a linear function of the inputs $x_i$ parametrized by the coefficients $\beta$.
+Hence, in this setting, regularization deals with penalizing the risk function based on the value of the chosen set of coefficients.
+\\
+However, this only describes a subset of \textit{regularization} methods as stated by \textcite{Taxonomy2017}. The authors use a more general definition of regularization:\\
+
+\textbf{Defintion 1. Regularization} is any supplementary technique that aims at making the model generalize better, i.e. produce better results on the test set.\\
+
+Building on that, they split up the majority of \textit{regularization} methods into  (1) methods applied to the data set like transformations or modifications of the inputs, (2) methods altering the selected model family , (3) methods applied to the error/loss function $L(y_i, f_\beta(x_i))$ , (4) methods applied to regularization/penalty term as described above and (5) alterations of the optimization procedure itself.
+
+\begin{lightbluebox}
+Vielleicht noch genauer auf die Taxonomy eingehen? 
+\end{lightbluebox}
+
+Unsurprisingly, this thesis is concerned with the fourth group of regularization methods, which add a penalty/regularizer term $J(\beta)$ into the risk function, but before advancing to literature that deals with this kind of problem, it is necessary to establish a terminology which will be used throughout this thesis.
+\textbf{TODO}
+
+Let $\mathcal{D}$ be a training data set with $n \in \mathbb{N}$ observations, where every  consists of a target variable $y_i \in \mathbb{R}$ along with a number of corresponding inputs $x_i \in \mathbb{R}$.
+Given a linear function $f_\beta(x_i)$ of the inputs parametrized by coefficients $\beta \in \boldsymbol{\beta}$, $L(y_i f_\beta(x_i))$ is the \textbf{Loss} function measuring the discrepancy between the actual target $y_i$ and the output of the linear function $f_\beta(x_i)$.
+According to \textcite{Vapnik1991}, the \textbf{Empirical Risk Functional} is then
+\[
+R_{emp}(\beta) = \frac{1}{n} \sum_{i=1}^n L(y_i, f_\beta(x_i)).
+\]
+\textbf{Regularization} in this thesis' context refers then to adding some penalty function $J(\beta)$ dependent on the set of parameters $\beta$, multiplied by some weighting parameter $\lambda$, to the empirical risk functional $R_{emp}(\beta)$.
+Thus, $R_{reg} = R_{emp}(\beta) + \lambda\cdot J(\beta)$.
+This results in the overall optimization problem
+\begin{align*}
+&\underset{\beta \in \boldsymbol{\beta}}{\argmin}\left\{R_{reg}(\beta)\right\}\\
+&=\underset{\beta \in \boldsymbol{\beta}}{\argmin}\left\{R_{emp}(\beta) + \lambda\cdot J(\beta)\right\}\\
+&=\underset{\beta \in \boldsymbol{\beta}}{\argmin}\left\{\sum_{i=1}^n L(y_i, f_\beta(x_i)) + \lambda\cdot J(\beta)\right\}
+\end{align*}
+
+It is important to note here that as $J(\beta)$ is only a function of the coefficients $\beta$, it only affects the generalization error of the model, not the training error given by the empirical risk functional $R_{emp}(\beta)$.
+
+\begin{lightbluebox}
 Ad Solution (3) because it is relatively easy to implement: Simple approach => Start with simplest model and iteratively add one feature OR iteratively get rid of feature by feature.
@@
 However, typical solution is cross-validation.
+
+\textbf{Literature}
+\parencite{Taxonomy2017}
+\end{lightbluebox}
+\newpage
+
+%----- Literature Review -----
+\section{Literature Review}
+
+The concept of a penalized regression has been around for quite some time and been studied widely in various fields of scientific research.
+
 \subsubsection{Short Deviation to Bayesian Shrinkage Priors}

### 2024-05-16 01_latex/MScThesis_Econ.tex
Changes after CFRL Issue
Changes in Theory and Hyperparameter Section

@@
 \usepackage{amssymb}
+\usepackage{tikz}
 
@@
 %----- Theoretical Section
+\newpage
 \section{Theoretical Section}\label{sec:theorysuper}
@@
 
-It is important to note here that as $J(\beta)$ is only a function of the coefficients $\beta$, it only affects the generalization error of the model, not the training error given by the empirical risk functional $R_{emp}(\beta)$.
+It is important to note here that as $J(\beta)$ is only a function of the coefficients $\beta$ and neither the targets $y_i$ nor the inputs $x_i$.
+It only affects the generalization error of the model, not the training error given by the empirical risk functional $R_{emp}(\beta)$.
 
@@
 \end{lightbluebox}
+
+\subsection{Short Deviation to Bayesian Shrinkage Priors}
+
 \newpage
@@
 The concept of a penalized regression has been around for quite some time and been studied widely in various fields of scientific research.
+Arguably, this methodological approach to penalized regression started with the publication of two pieces of literature published by Arthur Hoerl and Robert Kennard in 1970 \parencite{HoerlKennard1970a, HoerlKennard1970b}.
+With these two papers the authors introduced the widely known \textit{Ridge Regression}, which has been developed from the previously known concept of Ridge analysis.
+In its core, the authors were trying to tackle the problem of high variances of the regression coefficients in high-dimensional problem settings.
+This shrinkage estimator, which uses the squared coefficient as a penalty term, "attempt[s] to shrink the coefficients to
+reduce these variances, while adding some bias." \parencite{Hoerl2020} This closely resembles the previously discussed issue of the \textit{Bias-Variance-Tradeoff}, which has been discussed in the \textit{Under- and Overfitting} chapter in section \ref{sec:theorysuper} (Roger W.
+Hoerl, Arthur Hoerl's son, published a historical overview of the development of the concept of \textit{Ridge Regression} in 2020 \parencite{Hoerl2020}).
+The closed from solution of the Ridge estimator is given by
+$$\hat{\beta}_{Ridge} = \left(X^TX+\lambda I\right)^{-1}X^Ty$$,
+which adjusts the OLS estimator by shifting the main diagonal entries of the design matrix by $\lambda$ ($\lambda \geq 0$).
+It can be shown that this closed form estimator is equivalent to a Lagrangian problem of the following form \parencite{VanWieringen2015}:
+$$\hat{\beta}_{Ridge}(\lambda) = \underset{\beta}{\argmin}\left\{\norm{y-X\beta}_2^2 + \lambda\norm{\beta}_2^2\right\}$$
+This resembles an example of the above defined regularization framework with squared residual loss and a penalty term of the form $\norm{\beta}_2^2$, which only depends on the parameter $\beta$.
+In case of $\lambda$ being equal to zero, this reduces to the \textit{maximum likelihood (ML) estimator}.
 
-\subsubsection{Short Deviation to Bayesian Shrinkage Priors}
+The publications of Arthur Hoerl and Robert Kennard have led to further advancements, although it took more than 25 years, in shrinkage estimation or related concepts.
+One concept which is almost as famous \textit{Ridge Regression} is the \textit{Least Absolute Shrinkage and Selection Operator}, more commonly know as \textit{LASSO}, developed by \textcite{Tibishirani1996}.
+He argues that the two at the time most prominent shrinkage methods - Ridge and Subset Selection - both have their drawbacks.
+Ridge regression on the one hand is an optimization problem which continuously shrinks coefficients towards zero, but doesn't select them in a discrete sense, which makes it hard to interpret these models.
+Subset Selection on the other hand chooses variables in a discrete sense - a variables either stays within the model or it doesn't - and thus creates easily interpretable models, but "[s]mall changes in the data can result in very different models being selected and this can reduce its prediction accuracy." \parencite{Tibishirani1996} \textit{LASSO} is trying to combine both methods' advantages by using $\norm{\beta}_1$ as a penalty term.\\
+\begin{lightbluebox}
+Bit more on LASSO?
+\end{lightbluebox}
+
+\textit{LASSO} and to some extend \textit{Ridge} can be viewed as a special case of a $l_p$-norm regularization with corresponding values for $p$ ($p = 1$ for LASSO and $p=2$ for Ridge) \parencite{FrankFriedman1993}.
+
+$$\norm{\beta}_p =  \left(\sum_{i=1}^p|\beta_i|^p\right)^{1/p}$$
+
+An approach combining these two methods is called \textit{Elastic Net} regularization and has been developed by \\
+\begin{lightbluebox}
+Talk about Elastic Net
+\end{lightbluebox}
+
+\begin{lightbluebox}
+Talk about non-convex penalties
+\end{lightbluebox}
+
+\begin{lightbluebox}
+Use tree to classify regularization methods.
+\end{lightbluebox}
+\begin{center}
+\begin{tikzpicture}[
+    level 1/.style={sibling distance=5.2cm},
+    level 2/.style={sibling distance=2.6cm},
+    level 3/.style={sibling distance=2.6cm, level distance=2.5cm},
+    every node/.style={draw, rectangle, align=center}
+]
+\node {Classification of \\ Penalty Terms}
+    child { node {Behaviour at Zero}
+        child { node {Singularity} child { node {TG, \\ MCP,\\ SCAD, \\ LAPLACE, \\ LASSO}}}
+        child { node {Differentiable} child { node {Gaussian,\\ Ridge}}}
+    }
+    child { node {(Non-)Convexity}
+        child { node {Convex} child { node {LASSO, \\ Ridge}}}
+        child { node {Concave} child { node {TG,\\ Gaussian, \\ Arctan}}}
+    }
+    child { node {Behaviour at Limits}
+        child { node {Divergent} child { node {TG,\\ LASSO, \\ Ridge}}}
+        child { node {Convergent} child { node {Arctan, \\ Gaussian}}}
+    };
+\end{tikzpicture}
+
+\end{center}
 
@@
 
+The main motivation for this thesis stems from the striking duality that exists between Bayesian shrinkage priors and approaches to regularization.
+Both approaches aim at tackeling the issue of model complexity and overfitting by making it necessary for the data to be more convincing that the value of an estimate is statistically significant differnt from zero.
+Bayesian statistics use specific prior distributions with a usually a lot of mass around zero and heavy tails.
+Popular examples...
+
 \subsection{Triple-Gamma-Prior by \textcite{TGP2020}}
+A new development in the are of shrinkage priors has been made by \textcite{TGP2020}
 
@@
 After closer inspection of equation \ref{eq:tgr}, it can easily be seen that this resembles the general penalized regression already seen in \textcite{ESLpage398} and in section \ref{sec:theorysuper} as $R(\beta) + \lambda\cdot J(\beta)$.
-The first term, alos called the empirical loss in machine learning literature, is the widely known residual sum of squares:
+The first term, also called the empirical loss in machine learning literature, is the widely known residual sum of squares:
 \[
@@
 \[
-J(\beta) = \sum_j^p -\log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right)
+J_{TG}(\beta) = \sum_j^p -\log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right)
 \]
 In contrast to the \textit{LASSO} penalty, which uses the the absolute value of the coefficient, or the \textit{Ridge} penalty, which uses the square of the estimate, this penalty derived from \textcite{TGP2020} is based on the $\log$ of the confluent hyper-geometric of the second kind.
-Notably, this penalty term has three additional hyper-parameters: $c^\xi$, $a^\xi$ and $\kappa$ as $\phi^\xi = (2c^\xi)/(\kappa^2_B a^\xi)$.
+Notably, this penalty term has three additional hyper-parameters: $c^\xi$, $a^\xi$ and $\kappa_B$ as $\phi^\xi = (2c^\xi)/(\kappa^2_B a^\xi)$.
+Here, the restrictions $a^\xi>0.5$ and $0 < c^\xi < \infty$ are necessary to ensure that the penalty for a $\beta_j$ being equal to zero remains finite and not diverges to negative infinity at zero.
+This results, which has already been presented and proven as part of Theorem 2 in \textcite[5--6]{TGP2020}, ensures that the negative $\log$ of the hypergeometric function remains finite and thus does not produce parameter estimates which are zero for every variables.
+(\textbf{BESSER SCHREIBEN?})\\
+\begin{lightbluebox}
+Write more to fill this page
+\end{lightbluebox}
+\newpage
+
+\textit{Variations of the Hyperparameter $a^\xi$}\\
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInA.png}
+\caption{Triple-Gamma-Penalty using different values of $a^\xi$}
+\label{fig:basicTGPen}
+\end{figure}
+
+\textit{Variations of the Hyperparameter $c^\xi$}\\
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInC.png}
+\caption{Triple-Gamma-Penalty using different values of $c^\xi$}
+\label{fig:basicTGPen}
+\end{figure}
+
+\textit{Variations of the Hyperparameter $\kappa_B$}\\
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInKappa.png}
+\caption{Triple-Gamma-Penalty using different values of $\kappa_B$}
+\label{fig:basicTGPen}
+\end{figure}
+
+\subsection{Comparison to already existing Penalty Terms}\label{subsec:comparepenalties}
 
@@
 
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInA.png}
-\caption{Triple-Gamma-Penalty using different values of $a^\xi$}
-\label{fig:basicTGPen}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInC.png}
-\caption{Triple-Gamma-Penalty using different values of $c^\xi$}
-\label{fig:basicTGPen}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInKappa.png}
-\caption{Triple-Gamma-Penalty using different values of $\kappa_B$}
-\label{fig:basicTGPen}
-\end{figure}
-
 \subsection{Restricted Strong Convexity (RSC) of the Triple-Gamma-Regularization}
@@
 \subsection{Alternative Specification (with +1 to mimic artan)}
+
+As previously mentioned, the \textit{Arctan} penalty developed by \textcite{WangZhu2016} has a similar structure as the \textit{Triple-Gamma-Penalty} in small neighbourhoods near $\beta = 0$ when using specific hyper-parameters (see section \ref{subsec:comparepenalties}).
+The distinctive structural difference between these two penalties emerge when looking at the limits when  $\underset{\beta \to +/- \infty}{\lim J_{TG}(\beta)}$
 

### 2024-05-16 02_simulation/tgr.py

@@ -10,7 +10,7 @@ import log_hyperu as hyperu
 class TripleGammaRegularization(nn.Module):
     def __init__(self, num_features):
         super(TripleGammaRegularization, self).__init__()
-        self.linear = nn.Linear(4, 1)
+        self.linear = nn.Linear(12, 1, bias=False)
 
     def forward(self, x):
         return self.linear(x)

### 2024-05-16 01_latex/MScThesis_Econ.tex
Contd Section on Hyperparameters

@@
 \usepackage{lscape}
-\usepackage{multirow}
-\usepackage{booktabs}
 \usepackage{graphicx}
@@
 \usepackage{tikz}
+
+% Packages for Tables -----
+\usepackage{multirow}
+\usepackage{booktabs}
+\usepackage[justification=centering]{caption} % Centers the caption
+% -----
 
@@
 
+The first hyper-parameter which can be adjusted is $a^\xi$.
+A plot with a set of different values for $a^\xi$ can be found in figure \ref{fig:VariationInA}.
+As already mentioned earlier, the necessary restriction for for this hyper-parameter is that it has to be strictly greater than $0.5$ to guarantee the finiteness of the penalty.
+To demonstrate the effects of changes in $a^\xi$, the other parameters have been set to $c^\xi=0.1$ and $\kappa_B=2$.
+It can easily be seen from the figure that $a^\xi$ steers the sharpness of the penalty in small neighbourhoods around $\beta=0$.
+As $a^\xi$ increases, the penalty because smoother at $\beta=0$ with it eventually converging a \textit{Gaussian Penalty} like behaviour.
+From a modelling perspective, this opens up the possibility of steering the degree of variable selection the penalty performs.
+Nonetheless, the overall structure of the penalty in the tails does not change systematically apart from a parallel shift, which can be readjusted by specifying a different weighting parameter $\lambda$ or a different value for $\kappa_B$ (more on effect of $\kappa_B$ on the penalty can be found later in this chapter).\\
+
 \begin{figure}[!h]
@@
 \caption{Triple-Gamma-Penalty using different values of $a^\xi$}
-\label{fig:basicTGPen}
+\label{fig:VariationInA}
 \end{figure}
 
+Seeing this, it is apparent that a value of $a^\xi$ close but strictly larger that $0.5$ mimics the behaviour of the \textit{Arctan Penalty} by \textcite{WangZhu2016} in small neighbourhoods of $\beta=0$.
+Similar, large positive values for $a^\xi$ lead to a \textit{Gaussian Penalty} like behaviour in small neighbourhoods of $\beta = 0$ as recently proposed by \textcite{JohnVettamWu2022}.\\
+
 \textit{Variations of the Hyperparameter $c^\xi$}\\
+
+In contrast to the hyperparameter $a^\xi$, which mainly affects the behaviour at and around $\beta=0$, changes in $c^\xi$ mainly affect the behaviour in the tails.
 
@@
 \end{figure}
+
+%---- Table Summarizing the Effects of Changes in the Hyperparameters
+
+\begin{table}[!h]
+\centering
+\begin{tabular}{lcccccc}\toprule
+		& \multicolumn{2}{c}{Change} & \multicolumn{3}{c}{Mathematical Properties}\\
+		\cmidrule(r{4pt}){2-3} \cmidrule(l){4-5}
+Variable     	& \textbf{Positive} Change  & \textbf{Negative} Change & Defined Range & Misc.\\\midrule
+$a^\xi$  	& 11034 & 1.3e-7 & 3.9 & 15846 \\
+$c^\xi$ 		& 21952 & 1.3e-7 & 6.2 & 31516 \\
+$\kappa_B$ 	& 15883 & 5.2e-8 & 7.1 & 32023 \\\bottomrule
+\end{tabular}
+\caption{Summary of the effects of changes in the hyperparameters $a^\xi$, $c^\xi$ and $\kappa_B$ on the penalty structure}
+\label{tab:VariationsInHyperparameters}
+\end{table}
+\newpage
 

### 2024-05-23 01_latex/MScThesis_Econ.tex
End of Day Commit 230524
Started Simulation Code; Added More on Hyperparameters

@@
 \usepackage[justification=centering]{caption} % Centers the caption
+\usepackage{makecell}
+\usepackage{lscape}
 % -----
@@
 \vfill
-{\large \textbf{Triple-Gamma-Regularization} \textit{or}\\ \textbf{On the Duality of Frequentist Point Estimates and Bayesian Shrinkage Priors}\\
-\normalsize \textit{An Extension based on the Triple-Gamma-Prior}}
+{\large \textbf{Triple-Gamma-Regularization} \\
+\normalsize \textit{A Flexible Non-Convex Regularization Penalty based on the Triple-Gamma-Prior}}
+
+% Old Title
+%\textit{or}\\ \textbf{On the Duality of Frequentist Point Estimates and Bayesian %Shrinkage Priors}\\
+%\normalsize \textit{An Extension based on the Triple-Gamma-Prior}}
+
 \vfill
@@
 \subsection{Short Deviation to Bayesian Shrinkage Priors}
+Explain how Bayesians battle model complexity.
 
@@
 \end{center}
+
+Vielleicht als Tabelle mit drei Spalten.
 
@@
 Similar, large positive values for $a^\xi$ lead to a \textit{Gaussian Penalty} like behaviour in small neighbourhoods of $\beta = 0$ as recently proposed by \textcite{JohnVettamWu2022}.\\
+\newpage
 
@@
 In contrast to the hyperparameter $a^\xi$, which mainly affects the behaviour at and around $\beta=0$, changes in $c^\xi$ mainly affect the behaviour in the tails.
+However, the effect that a change in $c^\xi$ has on the penalty structure can be split up in two rough subsets of $(0,\infty)$.
+The effect of the first subset of values for $c^\xi$ which are strictly greater than $0$ but less or equal than $0.1$ can be found in figure \ref{fig:ChangeInC_SmallValues} (as already mentioned before, by definition, $c^\xi$ has to be strictly greater than zero: $c^\xi > 0$).
+Here, it can be seen that as the values for $c^\xi$ become smaller, a shifting effect takes place which generally does not influence the overall structure of the penalty, but increases the amount of penalty which is added to the risk function for $\beta$-values which are different from zero (In a sense, this has a similar effect to changes in $\kappa_B$, which will be explained later).
+Or, to put it differently, with values of $c^\xi$ closer to zero, the data has be become even more convincing that the value is significantly different from zero.\\
 
@@
 \centering
-\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInC.png}
-\caption{Triple-Gamma-Penalty using different values of $c^\xi$}
-\label{fig:basicTGPen}
+\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInC_Part2.png}
+\caption{Triple-Gamma-Penalty using different values of $c^\xi$ with $0 < c^\xi \leq 0.1$}
+\label{fig:ChangeInC_SmallValues}
+\end{figure}
+
+However, the more interesting effect that a change in $c^\xi$ has on the penalty structure can be seen for values of $c^\xi$ that are greater than $0.1$.
+In figure \ref{fig:ChangeInC_LargeValues}, a plot can be found with the Triple-Gamma-Penalty for larger values of $c^\xi$.
+Again, starting from the baseline with $c^\xi = 0.1$, higher values for this hyper-parameter mainly change the behaviour of the penalty in the tails.
+A result that has already been shown by \textcite{TGP2020} in Table 1, where multiple different hyper-parameter settings are presented, is that with an increasing value for $c^\xi$ and with $a^\xi = 1$ \textbf{as well as kappaB = ??}, the Triple-Gamma-Prior converges to a \textit{LASSO} like shrinkage behaviour.
+A property which carries over to the proposed regularization setting when using the proposed hyper-parameter values, thus showing that the Triple-Gamma-Penalty can be used both as a non-convex penalty as well as a \textit{LASSO} penalty, creating increased flexibility in modelling approaches.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInC_Part1.png}
+\caption{Triple-Gamma-Penalty using different values of $c^\xi$ with $c^\xi \geq 0.1$}
+\label{fig:ChangeInC_LargeValues}
 \end{figure}
@@
 \textit{Variations of the Hyperparameter $\kappa_B$}\\
+
+The third and final hyper-parameter $\kappa_B$ enters the Triple-Gamma-Penalty $J_{TG}(\beta)$ as part of $\phi^\xi = \frac{2c^\xi}{\kappa_B^2 a^\xi}$ as can be seen from equation \ref{eq:tgr}.
+Notably, $\kappa_B$ is squared and thus only the absolute value of $\kappa_B$, $|\kappa_B|$, influences the structure of the penalty.
 
@@
 
+\newpage
 %---- Table Summarizing the Effects of Changes in the Hyperparameters
-
+\begin{landscape}
 \begin{table}[!h]
-\centering
+\begin{center}
 \begin{tabular}{lcccccc}\toprule
-		& \multicolumn{2}{c}{Change} & \multicolumn{3}{c}{Mathematical Properties}\\
+		& \multicolumn{2}{l}{Change} & \multicolumn{3}{c}{Mathematical Properties}\\
 		\cmidrule(r{4pt}){2-3} \cmidrule(l){4-5}
 Variable     	& \textbf{Positive} Change  & \textbf{Negative} Change & Defined Range & Misc.\\\midrule
-$a^\xi$  	& 11034 & 1.3e-7 & 3.9 & 15846 \\
-$c^\xi$ 		& 21952 & 1.3e-7 & 6.2 & 31516 \\
-$\kappa_B$ 	& 15883 & 5.2e-8 & 7.1 & 32023 \\\bottomrule
+$a^\xi$  	& \makecell{Shifting towards\\ \textit{Gaussian}-like behaviour\\ at $\beta = 0$} & \makecell{Shifting towards singularity\\ at $\beta = 0$; Higher\\ immediate penalty for coefficients\\ $\beta \neq 0$} & $(0.5, \infty)$ & Expl.\\
+$c^\xi$ 		& \makecell{Generally, convergence towards \\ convexity and, given certain \\ settings for $a^\xi$ and\\ $\kappa_B$, LASSO.
+Higher values\\ increase the additional penalty\\ for higher absolute values of $\beta$.} &  \makecell{For values smaller \\ than $0.1$, similar effect\\ to increase in $a^\xi$} & $(0, \infty)$ & Expl.
+\\
+$\kappa_B$ 	& 15883 & 5.2e-8 & $(-\infty, \infty)/{0}$ & Expl. \\\bottomrule
 \end{tabular}
@@
 \end{table}
+\end{center}
+\end{landscape}
 \newpage
@@
 \centering
-\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/simpleTGpenalty.png}
+\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/ComparisonToOtherPenalties.png}
 \caption{Basic Representation of the Triple-Gamma-Penalty using Hyperparameters $c^\xi = 0.1, \kappa_B = 2, a^\xi = 0.75$ compared to \textit{LASSO} and \textit{Ridge} Penalties}
@@
 Talking about Gradient Descent Methods in more depth. Why Gradient Clipping. Maybe more modern estimation techniques?
-\subsection{Implementation as Python Library}
+
+See how computation times change when increasing the size of the data set or when the number of parameter changes. => Use Stochastic Gradient Descent (SGD)
+\subsection{Implementation as Python Package}
 

### 2024-06-12 01_latex/MScThesis_Econ.tex
Safety Commit

@@
 \clearpage
+
+\section*{Acknowledgements}
+\thispagestyle{empty}
+
+I like to acknowledge ...
+
+\clearpage
+
 \thispagestyle{plain}
@@
 %----- Literature Review -----
-\section{Literature Review}
+\section{Literature Review}\label{sec:litreview}
 
@@
 Notably, $\kappa_B$ is squared and thus only the absolute value of $\kappa_B$, $|\kappa_B|$, influences the structure of the penalty.
+The overall third function value is defined as $\frac{\beta_j^2}{2\phi^\xi}$ and by plugging in $\phi^\xi$ we get $\frac{\beta_j^2\kappa_ B^2a^\xi}{4c^\xi}$, it can be seen that a value of $\kappa_B = 0$ leads to the entire parameter value being zero for all values of $\beta_j$.
+Hence, a change in $\beta_j$ won't influence the penalty and furthermore won't have an influence on the overall risk minimization problem, the result being that the optimal set of parameters will only depend on the chosen loss function.\\
 
-\begin{figure}[!h]
+For all values of $\kappa_B \neq 0$, the value of the hyper-parameter will influence the penalty structure.
+A plot with several different values for the absolute value of $\kappa_B$ can be found in figure \ref{fig:TGPenalty_ChangeInKappa}.
+
+\begin{figure}[t]
 \centering
@@
 \caption{Triple-Gamma-Penalty using different values of $\kappa_B$}
-\label{fig:basicTGPen}
+\label{fig:TGPenalty_ChangeInKappa}
 \end{figure}
@@
 \\
-$\kappa_B$ 	& 15883 & 5.2e-8 & $(-\infty, \infty)/{0}$ & Expl. \\\bottomrule
+$\kappa_B$ 	& 15883 & 5.2e-8 & $(-\infty, \infty)/\{0\}$ & Expl. \\\bottomrule
 \end{tabular}
@@
 \label{tab:VariationsInHyperparameters}
+\end{center}
 \end{table}
-\end{center}
 \end{landscape}
@@
 
+As already mentioned in section \ref{sec:litreview}, several other penalty terms have already been widely studied in the literature.
+Convex penalties like \textit{Ridge} \parencite{HoerlKennard1970a} or non-convex penalties like the \textit{Ar(c)tan} \parencite{WangZhu2016} and Gaussian \parencite{JohnVettamWu2022} have managed to establish itself as prominent approaches to regularization.
+It is now certainly of interest to see how the \textit{Triple-Gamma} penalty compares to the established methods.
+Seeing that, due to its flexibility, there is not \textit{one} \textit{Triple-Gamma} penalty, three distinct hyper-parameter setting have been chosen to represent the proposed penalty term.
+
 \begin{figure}[!h]
 \centering
-\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/ComparisonToOtherPenalties.png}
+\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_Comparison.png}
 \caption{Basic Representation of the Triple-Gamma-Penalty using Hyperparameters $c^\xi = 0.1, \kappa_B = 2, a^\xi = 0.75$ compared to \textit{LASSO} and \textit{Ridge} Penalties}
@@
 %----- Small Applied Section
-\section{Small Applied Section}
-Here I am planning to apply the TGP using Peter's Bayesian Package and the self coded frequentist code on a small dataset.
+%\section{Small Applied Section}
+%Here I am planning to apply the TGP using Peter's Bayesian Package and the self coded frequentist code on a small dataset.
+\section{Possible Extensions and Criticism}
 \section{Conclusion}
-\section{Possible Extensions and Criticism}
+
+\newpage
+\section{List of Figures}
+\listoffigures
+
+\newpage
+\section{List of Tables}
+\listoftables
+
+\newpage
 \section{References}

### 2024-06-12 02_simulation/tgr.py

@@ -10,7 +10,7 @@ import log_hyperu as hyperu
 class TripleGammaRegularization(nn.Module):
     def __init__(self, num_features):
         super(TripleGammaRegularization, self).__init__()
-        self.linear = nn.Linear(12, 1, bias=False)
+        self.linear = nn.Linear(10, 1, bias=False)
 
     def forward(self, x):
         return self.linear(x)
@@ -49,10 +49,10 @@ def TripleGammaModel(X, y, penalty, a, c, kappa,  norm=True, num_epochs=1000, lr
         loss_list.append(loss)
         
         #Gradient Clipping???
-        nn.utils.clip_grad_norm_(model.parameters(), 1.0)
+        #nn.utils.clip_grad_norm_(model.parameters(), 1.0)
         optimizer.step()
 
-        if (epoch+1) % 100 == 0:
-            print(f'Epoch [{epoch+1}/{num_epochs}], Loss: {loss.item()}')
+        #if (epoch+1) % 100 == 0:
+        #    print(f'Epoch [{epoch+1}/{num_epochs}], Loss: {loss.item()}')
 
     return model, coef_list, loss_list

### 2024-06-12 06_general_code/support_plots.R

@@ -1,0 +1,66 @@
+#### Packages
+library(ggplot2)
+library(GPBayes)
+library(tidyverse)
+####
+a = 5
+c = 0.25
+kappa = 2.2
+phi = (2*c)/(kappa^2*a)
+outputdf = data.frame(TG_func=numeric(),
+                      arctan=numeric(),
+                      input=numeric(),
+                      gaussian=numeric())
+for (x in seq(-10,10,0.01)){
+  value = (1.17)*(-log(HypergU(c+0.5,1.5-a,(x^2)/(2*phi))+1)+log(HypergU(c+0.5,1.5-a,0)+1))
+  arctan_value = (2/pi)*atan(abs(x))
+  gausian_value = 1 - exp(1)^(-x^2)
+  outputdf = rbind(outputdf, data.frame(TG_func=value,gaussian = gausian_value, input=x, arctan=arctan_value))
+  
+}
+
+ggplot(outputdf, aes(x=input)) +
+  geom_line(aes(y=3*TG_func, color="Triple-Gamma"), size=1)+
+  #geom_line(aes(y=arctan, color="Arctan"),size=1)+
+  geom_line(aes(y=gaussian, color="Gaussian"),size=1)+
+  scale_color_manual(name = "Pentalty Term", values = c("Gaussian"="green","Triple-Gamma" = "darkblue", "Arctan" = "red"))+
+  labs(x="Beta Values", y="Penalty")+
+  theme_minimal()
+
+
+### Variations in A
+c = 0.1
+kappa = 2
+range_x=20
+intervals = 0.01
+n = range_x/intervals
+a_values = c(0.51,0.75,1,5)
+matrix_output = matrix(nrow=n+1, ncol=length(a_values)+1)
+matrix_output[,1] = seq(-10,10,0.01)
+counter = 2
+
+for (a in a_values){
+  phi = (2*c)/(kappa^2*a)
+  value = c()
+  for (x in seq(-10,10,0.01)){
+    value = c(value,-log(HypergU(c+0.5,1.5-a,(x^2)/(2*phi)))+log(HypergU(c+0.5,1.5-a,0)))
+  }
+  matrix_output[,counter] = value
+  counter=counter+1
+}
+
+colnames(matrix_output) <- c("Input",paste0("a=",a_values))
+matrix_output <- as.data.frame(matrix_output)
+
+ggplot(matrix_output, aes(x=Input)) +
[…]

### 2024-06-12 06_general_code/test_code.R

@@ -1,0 +1,44 @@
+tstat <- 3.5
+n <- 20
+df <- n*2 - 2
+pval <- 2 * (1-pt(abs(tstat), df))
+
+
+y <- c(3.14, 1.3, 1.5)
+mu_mle <- mean(y)
+lambda_mle <- (length(y)*mu_mle^2)/(sum((y-mu_mle)^2/y))
+print(mu_mle)
+
+library(ggplot2)
+
+set.seed(12345)
+x <- as.data.frame(matrix(rnorm(50, 10, 2),nrow=5,ncol=10))
+beta <- as.data.frame(c(0,0,0,3,0,0,0,0,0,2))
+y <-  as.matrix(x) %*%  as.matrix(beta) + rnorm(5, 2, 4)
+data <- cbind(y,x)
+lm(y~., data = data)
+
+cv_model<- glmnet::cv.glmnet(as.matrix(x), as.matrix(y), alpha = 1)
+best_lambda <- cv_model$lambda.min
+coef(glmnet::glmnet(x, y, alpha = 0, lambda = 10))
+
+y
+x 
+
+ggplot(data.frame(Y=y, X=x), aes(X,Y))+
+  geom_point(size = 2, col = 'red')+
+  geom_smooth(method = "lm", formula = y ~ poly(x, 8), aes(color = "7"), se = F)+
+  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(color = "4"), se = F)+
+  labs(color = "Polynomial Degree") +
+  scale_color_brewer(palette = "Set1") +
+  ggtitle("Sparse Data Setting with Polynomial Fit") +
+  theme_classic()+
+  theme(panel.grid.major = element_line())
+
+options(scipen = 10)
+colnames(ytrain) = "Y"
+dataset = cbind(ytrain, xtrain)
+mod1 <- lm(Y ~., data = dataset)
+summary(mod1)
+
+

### 2024-07-24 01_latex/MScThesis_Econ.tex
Saftey Commit - BackupVersion

@@
 }
+
+\definecolor{green1}{HTML}{2CA02C}
+\definecolor{blue1}{HTML}{1F77B4}
+\definecolor{red1}{HTML}{D62728}
+\definecolor{orange1}{HTML}{FF7F0E}
 
@@
 \section{Theoretical Section}\label{sec:theorysuper}
-\subsection{Model Complexity}
-Overfitting is a problem.
-Especially when dimensionality issues arise.
-For example, 50 observations and 20 features.
-Model will perform well/almost perfect on training data, but will do terrible on training data.\\
-\subsection{Under- and Overfitting}
+Generally speaking, a major part of statistical learning deals with trying to describe a certain output variable $Y$ with a set of input variables $X_1, \cdots, X_p$ by trying to find a functional form $f$ which uses the given information in the inputs and - ideally - describes the hidden relationship between $Y$ and the inputs $X_i$ as accurately as possible.
+However, it comes as no surprise that the functional form $f$ depends on the statistical problem at hand.
+What type of data has been collected?
+Are we assuming a linear or non-linear relationship between the predictors?
+How much data is available and can its quality be guaranteed?
+But more importantly, it is necessary to ask the question whether the goal of the statistical learning method is \textit{inference} or \textit{prediction}.\\
+
+The first of these two goals - \textit{inference} - aims at understanding the relationship that may or may not exist between the input variables $X_i$ and the output $Y$.
+Especially applied sciences like Economics, Psychology and Medicine often try to find a (causal) relationship within their theoretical framework to evaluate a policy, a medication or a new form of therapy.
+Linear models for example often provide a simple and straightforward framework which provide the scientist with interpretable effects.
+\textit{Prediction} on the other hand aims at forecasting the output variable $Y$ as accurately as possible and using every bit of information that is available, but disregards interpretability.
+\parencite{ESL,21} These goals can be summarized by viewing it as a decision between \textit{prediction accuracy} and \textit{model interpretability}, which has thoroughly been explained by \textcite{ESL}.\\
+
+For the purpose of this thesis, the following chapters will restrict itself to the case of linear models, hence where assume that the functional form $f$ is linear in its inputs.
+The commonly known \textit{least squares estimator} is one way of estimating such a functional form and due to its many desirable properties has gained popularity in various  scientific fields.
+
+\subsection{Model Complexity and the Problem of Under- and Overfitting}
+
+\begin{lightbluebox}
+- BIAS VARIANCE TRADE-OFF
+- DIMENSIONALITY PROBLEM
 
 General problem: Fit vs. Complexity. What to choose and where is the optimal balance?
+\end{lightbluebox}
+
+In general, a linear regression model fitted with least squares on a sufficient amount of data points ($n \gg p$) will produce estimates which both have low bias and low variance and thus tends to perform well out of sample.
+However, problems arise with this approach arise when the sample size decreases, because the variance in the estimates will increase.
+The main idea behind this can be easily be visualized by trying to fit a polynomial curve on a two dimensional space and then altering the available sample for polynomials of different order.
+\begin{figure}
+\centering
+\includegraphics[scale=0.5]{PolynomialFit_Plot.png}
+\caption{1st and 8th order polynomial fit to data \\ (\textcolor{green1}{Green} \& \textcolor{blue1}{Blue} Lines fitted with red data point; \textcolor{orange1}{Orange} \& \textcolor{red1}{Red} Lines fitted without).}
+\label{fig:polyfit}
+\end{figure}
+
+Such a plot can be found in figure \ref{fig:polyfit}.
+Here, the black points represent the main data sample plotted on a two-dimensional $Y$-$X$-space.
+The red dot plotted at $(5,4)$ represents the additional data point which is used to alter the respective sample.
+Polynomials of specific orders can now be used to emulate certain levels of model complexity.
+For example, a first order polynomial has two coefficients to estimate: the intercept $\beta_0$ and the slope $\beta_1$.
+A polynomial of order of order eight has nine coefficients to estimate.
+What can now be seen in figure \ref{fig:polyfit} is the change in estimates if we include/exclude the additional red data point.
+A first-order polynomial needs at least two data points and as $n=9 > p = 2$, the overall fit of the polynomial doesn't change drastically with the additional tenth data point.
+In the case of the eighth-order polynomial, we need at least nine data points to create a fit as we have nine predictors (one intercept and one coefficient for each of the eight powers).
+In this case $n=p$ and adding another data point drastically changes the estimates coefficients, which means that the model won't perform well in out-of-sample scenarios.
+This emphasizes the importance a sufficient sample size when fitting linear models.
+And this leads us to the core field of study of this thesis: What are ways to improve the generalization of a linear model in scenarios where the sample size is not sufficiently large enough?
+
+\begin{lightbluebox}
+
+- WAYS TO BATTLE COMPLEXITY
 
 Solutions (find source, seen in LMU course): (1) More data (Not always feasible) (2) Better data (Same issue) (3) Reduce Model Complexity (Regularization) (4) Less aggressive optimization (Maybe short review; Idea: Stop optimization when generalization error degrades)
+\end{lightbluebox}
 
@@
 
-\subsection{Short Deviation to Bayesian Shrinkage Priors}
+\subsection{Bayesian View on Battling Model Complexity using Shrinkage Priors}
 Explain how Bayesians battle model complexity.
@@
 
-An approach combining these two methods is called \textit{Elastic Net} regularization and has been developed by \\
-\begin{lightbluebox}
-Talk about Elastic Net
-\end{lightbluebox}
+Work published by researchers in the nineties, like the previously mentioned \textcite{FrankFriedman1993} or \textcite{Fu1998}, as well as more recent literature like \textcite{WangEtAl2020} have repeatedly shown there is no go-to-method to tackle regularization problems, as the effectiveness of a specific approach highly depends on the data siuation at hand.
+Due to this particular situation in the literature, several other methods have been proposed in the recent years and decades.
+An approach combining \textit{Ridge} and \textit{LASSO} two methods is called \textit{Elastic Net} regularization and has been developed by \textcite{ZouHastie2005}.
+The authors there elaborate on some of the shortcomings of the LASSO method.
+For example, in a special case where there are more predictors $p$ than data points $n$ ($p > n$), LASSO only selects up to $n$ variables due to the nature of the convex optimization problem.
+Should several of the included variables be highly \textit{pairwise} correlated with each other, \textit{LASSO} tends to only select on of these variables.
+In its core, \textit{Elastic Net Regularization} linearly combines the penalty terms of \textit{Ridge} and \textit{LASSO} regularization, yielding a loss function of the form:\\
+$$J(\beta) = \lambda_1 \norm{\beta}_2^2 + \lambda_2 \norm{\beta}_1$$
+The authors have	 shown that, especially when it comes to encouraging the aforementioned grouping effects, \textit{Elastic Net} tends to perform better than the \textit{LASSO}.\\
 
-\begin{lightbluebox}
-Talk about non-convex penalties
-\end{lightbluebox}
+Recent years however have opened up a new subfield of approaches to regularization.
+Methods like \textit{LASSO, Bridge} \parencite{FrankFriedman1993}, \textit{Ridge} and \textit{Elastic Net}\footnote{Elastic Net, due to its mathematical definition, can be view as a generalization of \textit{Ridge} and \textit{LASSO}.} are convex functions in its parameters and are thus usually classified as \textit{Convex Regularization Penalties}.
+Recently, the literature has shifted towards penalties which are non-convex functions in its parameters, usually called \textit{Non-Convex Regularization Penalties}\footnote{Note: They are called \textit{non-convex} penalties and not \textit{concave} penalties, because non-convexity does not necessarily imply concavity.}.
+One recent example of such a penalty includes \textcite{JohnVettamWu2022}, who proposed a penalty structure called \textit{Gaussian penalty} and which is based on a Gaussian-like function by using $J(\beta) = 1 - e^{-\kappa\beta^2}$.
+Another method proposed by \textcite{WangZhu2016} is called the \textit{Atan penalty} - or \textit{Arctan} penalty - an makes use of the favourable properties of the \textit{Arctan} function by using the penalty $J(\beta, \gamma) = (\gamma + \frac{2}{\pi})\arctan(\frac{|\beta|}{\gamma})$.
 
@@
 As already mentioned in section \ref{sec:litreview}, several other penalty terms have already been widely studied in the literature.
-Convex penalties like \textit{Ridge} \parencite{HoerlKennard1970a} or non-convex penalties like the \textit{Ar(c)tan} \parencite{WangZhu2016} and Gaussian \parencite{JohnVettamWu2022} have managed to establish itself as prominent approaches to regularization.
+Convex penalties like \textit{Ridge} \parencite{HoerlKennard1970a} or non-convex penalties like the \textit{Ar(c)tan} \parencite{WangZhu2016} and \textit{Gaussian} \parencite{JohnVettamWu2022} have managed to establish itself as prominent approaches to regularization.
 It is now certainly of interest to see how the \textit{Triple-Gamma} penalty compares to the established methods.

### 2024-07-28 01_latex/MScThesis_Econ.tex
commit 28072024

@@
 
-\subsection{Bayesian View on Battling Model Complexity using Shrinkage Priors}
+\subsection{Bayesian View on Battling Model Complexity using Shrinkage Priors}\label{sec:BayesianShrinkagePriors}
 Explain how Bayesians battle model complexity.
@@
 One recent example of such a penalty includes \textcite{JohnVettamWu2022}, who proposed a penalty structure called \textit{Gaussian penalty} and which is based on a Gaussian-like function by using $J(\beta) = 1 - e^{-\kappa\beta^2}$.
-Another method proposed by \textcite{WangZhu2016} is called the \textit{Atan penalty} - or \textit{Arctan} penalty - an makes use of the favourable properties of the \textit{Arctan} function by using the penalty $J(\beta, \gamma) = (\gamma + \frac{2}{\pi})\arctan(\frac{|\beta|}{\gamma})$.
+Another method proposed by \textcite{WangZhu2016} is called the \textit{Atan penalty} - or \textit{Arctan} penalty - and makes use of the favourable properties of the \textit{Arctan} function by using the penalty $J(\beta, \gamma) = (\gamma + \frac{2}{\pi})\arctan(\frac{|\beta|}{\gamma})$.
+Several others include \textit{SCAD} \parencite{FanLi2001}, \textit{MCP} \parencite{Zhang2010} or \textit{Laplace} \parencite{TrzaskoManduca2009} penalties.\\
 
-\begin{lightbluebox}
-Use tree to classify regularization methods.
-\end{lightbluebox}
+Seeing this vast array of different pieces of literature immediately raises the question on advantages and disadvantages of specific methods and why so many have established itself in this particular field of study.
+Keeping in mind that the effectiveness of a method still highly depends on the data situation at hand, it is still important to distinguish methods based on its mathematical properties.
+\textcite{JohnVettamWu2022} have distinguished methods based on two broad criteria: (1) How does a penalty behave in small neighbourhoods around zero?
+(Is it smooth or singular at origin?) and (2) Is the underlying function convex or non-convex?
+To better incorporate the proposed concept of this thesis into this body of literature, I am proposing a third property to distinguish penalty terms: (3) How does the function behave in the limits?
+(Does it converge or diverge?) \\
+
 \begin{center}
@@
     child { node {Behaviour at Zero}
-        child { node {Singularity} child { node {TG, \\ MCP,\\ SCAD, \\ LAPLACE, \\ LASSO}}}
-        child { node {Differentiable} child { node {Gaussian,\\ Ridge}}}
+        child { node {Singularity} }
+        child { node {Smooth at \\ Origin}}
     }
     child { node {(Non-)Convexity}
-        child { node {Convex} child { node {LASSO, \\ Ridge}}}
-        child { node {Concave} child { node {TG,\\ Gaussian, \\ Arctan}}}
+        child { node {Convex}}
+        child { node {Non-Convex}}
     }
     child { node {Behaviour at Limits}
-        child { node {Divergent} child { node {TG,\\ LASSO, \\ Ridge}}}
-        child { node {Convergent} child { node {Arctan, \\ Gaussian}}}
+        child { node {Divergent}}
+        child { node {Convergent}}
     };
 \end{tikzpicture}  
-
 \end{center}
 
-Vielleicht als Tabelle mit drei Spalten.
+As already mentioned earlier in section \ref{sec:theorysuper}, a penalty function is a function dependent on the parameter of the model and it does not depend on the data at hand.
+Thus, changes in your data set does not effect the penalty directly, but only the overall optimization problem through the empirical risk functional $R_{emp}$.
+The following table classifies some of the existing concepts based on the three criteria mentioned earlier.
+A visualisation of them can be found in figure \ref{fig:DifferentPenalties} in chapter \ref{subsec:comparepenalties}.\\
 
-\subsection{Duality of the Ridge Regression}
+Depending on what property a penalty has, it can perform specific tasks or provide challenges in application.
+As thoroughly described by \parencite{JohnVettamWu2022}, penalties with a singularity at origin tend to be suitable when the goal of the statistical analysis is variable selection but "could pose theoretical and computational challenges when the focus is on regularization alone without variable selection." In addition, it has been shown in the literature that "objective functions which are a sum of a nonconvex, singular-at-origin penalty function coupled with either a smooth nonconvex loss function or a nonsmooth convex loss function, often fails to satisfy a theoretical condition known as ‘Clarke regularity’." (A result presented in \textcite{QiCuiLiuPang2021})
+Convex penalties are generally easier to implement using common optimization algorithms than non-convex penalties and, more importantly, penalties which are divergent and its limits, which most convex penalties are, yield biased results.
+Due to the fact that, when using divergent and convex penalties like LASSO and Ridge, the additional penalty for larger estimates keeps rising with estimates which deviate from zero, estimates are getting artificially pulled towards zero and are thus biased.
+Non-Convex penalties, which are usually convergent in its limits towards $-\infty$ and $+\infty$, tend to yield unbiased results as the additional penalty becomes zero as soon as a certain threshold is crossed (Again, referring to the visualisation in figure \ref{fig:DifferentPenalties}).
+\begin{table}[!h]
+\begin{center}
+\begin{tabular}{lcccc}\toprule
+ \multicolumn{2}{c}{Penalty} & \multicolumn{3}{c}{Classification}\\
+		\cmidrule(r{4pt}){1-2} \cmidrule(l){3-5}
+Penalty     	& Reference  & \makecell{Behaviour\\ at Origin} & (Non-)Convexity & Limits\\\midrule
 
-The main motivation for this thesis stems from the striking duality that exists between Bayesian shrinkage priors and approaches to regularization.
-Both approaches aim at tackeling the issue of model complexity and overfitting by making it necessary for the data to be more convincing that the value of an estimate is statistically significant differnt from zero.
-Bayesian statistics use specific prior distributions with a usually a lot of mass around zero and heavy tails.
-Popular examples...
+LASSO 	& \textcite{Tibishirani1996}	& Singular	&	Convex 	& Divergent\\
+Ridge 	& \textcite{HoerlKennard1970a}	& Smooth		& Convex			& Divergent\\
+Gaussian & \textcite{JohnVettamWu2022}	& Smooth		& Non-Convex 	& Convergent\\
+Ar(c)tan 	& \textcite{WangZhu2016}	& Singular 	& Non-Convex 	& Convergent\\
+Elastic-Net & \textcite{ZouHastie2005} & Singular & Convex &\\
+Bridge & \textcite{FrankFriedman1993}& Both &&\\
+MCAP & \textcite{Zhang2010}& Singular & Non-Convex &\\
+SCAD & \textcite{FanLi2001} & Singular & Non-Convex &\\
+Laplace & \textcite{TrzaskoManduca2009} & Non-Convex &&\\
+Triple-Gamma & - & \makecell{Depending\\ on parameters} & Non-Convex & Divergent \\
+
+\end{tabular}
+\caption{Classification of several Penalties}
+\label{tab:ClassificationOfPenalties}
+\end{center}
+\end{table}
+
+\section{Bayesian-Frequentist Duality of Ridge and LASSO Regression}
+
+The main motivation for this thesis stems from a striking duality that exists between Bayesian shrinkage priors (discussed in chapter \ref{sec:BayesianShrinkagePriors}) and the frequentist approach using regularization.
+Both approaches aim at tackling the issue of model complexity and overfitting by making it necessary for the data to be more convincing that the value of an estimate is statistically significant different from zero.
+As mentioned, Bayesian statistics use specific prior distributions with a usually a lot of mass around zero and heavy tails, whereas frequentist statisticians usually alter their optimization problems incorporating penalty terms into into their loss functions.
+On a first glance, these two approaches have no immediate mathematical connection, however this turns out to be wrong.\\
+
+In a Bayesian setting, one usually assumes that the parameter vector $\mathbb{\beta}$ has a prior distribution $p(\mathbb{\beta}$.
+By multiplying it with the likelihood of the data $f(y|X,\beta)$ and by utilizing Bayes' rule, one retrieves the posterior distribution of the parameter distribution, up to a proportionality constant:
+
+$$p(\beta|y,X) \propto f(y|X, \beta) \times p(\beta)$$
+
+It turns out, as can be seen in \textcite[248--250]{ESL2009} and \textcite{VanWieringen2015} among others, that when choosing certain prior distributions and using standard assumptions in Bayesian modelling (ie the individual parameters of the parameter vector are independent a prior and the errors of the standard linear model are drawn from a normal distribution), that the moments of the posterior distributions correspond to the point estimates of a regularization approach in a frequentist setting.
+As this idea is essential to the entire thesis, a shortened derivation of this duality for the case of \textit{Ridge} regression will now be shown.\\
+
+Assuming that a response variable $y_i$ follows a linear model with $k$ variables and errors $\epsilon_i \sim \mathcal{N}(0, \sigma^2)$, then the likelihood of the data is given by
+$$\mathcal{L}(y|X,\beta)=\frac{1}{(2\pi\sigma^2)^{n/2}}\exp\left(-\frac{1}{2\sigma^2}\sum_{i=1}^n\epsilon_i^2\right).$$
+
+Under the previously mentioned assumption that $p(\beta) = \prod_{i=1}^k$ and by choosing a Gaussian distribution with mean zero and variance $\tau^2$, we gain the prior distribution
+$$p(\beta) = \frac{1}{(2\pi\tau^2)^{p/2}}\exp\left(-\frac{1}{2\tau^2}\norm{\beta}_2^2\right).$$
+
+Putting both together using Bayes' theorem yields and taking the $\log$ of the distribution yields
+$$\log(p(\beta|y,X)) \propto -\frac{1}{2\sigma^2}\sum_{i=1}^n \epsilon_i^2  - \frac{1}{2\tau^2}\norm{\beta}_2^2.$$
+
+By viewing $\frac{1}{2\tau^2}$ as the weighting parameter $\lambda$, which controls the strength of the regularization.
+The \textit{maximum-a-priori} estimate $\hat{\beta}_{MAP}$, which can be viewed as trying to find the $\underset{\beta}{\argmax}$ of the $\log$-posterior, can be used to construct the following optimization problem:
+
+$$\hat{\beta}_{MAP} = \underset{\beta}{\argmin}\left\{\frac{1}{2\sigma^2}\sum_{i=1}^n \epsilon_i^2  + \frac{1}{2\tau^2}\norm{\beta}_2^2\right\}$$
+
+This optimization problem constitutes the connection between the Bayesian and the frequentist approach as it can be interpreted as (1) finding the mode of the posterior distribution when using a Gaussian prior distribution and (2) finding the parameters which minimize the loss when using a Ridge regression with $\lambda = 1/(2\tau^2)$.
+The same connection exists for the case of \textit{LASSO} regression which can be derived using the same procedure and a double-exponential - also called \textit{Laplace} - distribution with mean zero and some scale parameter $\tau$ as the prior for the parameter vector $\beta$.
 
 \subsection{Triple-Gamma-Prior by \textcite{TGP2020}}
-A new development in the are of shrinkage priors has been made by \textcite{TGP2020}
+This opens up a path of possibility to utilize this connection and derive a new regularization penalty by using a different shrinkage prior.
+Recently, a new development in the are of shrinkage priors has been made by \textcite{TGP2020}, who proposed a new shrinkage prior called the \textit{Triple-Gamma-Prior} which has several advantageous properties and also comes with a closed-form solution of the marginal prior distribution for $\beta$, which sets the building block for this thesis' research question:
+
+\begin{quote}
+Can the closed-form marginal distribution of the Triple-Gamma-Prior
+be used to derive a new regularization penalty and do its advantages
+carry over into the frequentist framework?
+\end{quote}
+
+Yet, before diving into the mathematical core of this thesis which derives said concept, it is necessary to have a look at the Triple-Gamma-Prior in depth to explain why this particular prior might prove itself to provide a useful building block for a novel regularization penalty.
 
@@
 More formally, let $y=[y_1  \quad y_2 \cdots y_n]^T$ and $x_i = [x_{i1} \quad x_{i2} \cdots x_{in}]^T$ with $\forall i\in \{1,...,n\}: y_i, x_i \in \mathbb{R}$.
-Here, $x_i$ is the $i$-th predictor, thus resulting in the design matrix $X = [x_1 \quad x_2 \cdots x_p]$.
-\\
+Here, $x_i$ is the $i$-th predictor, thus resulting in the design matrix $X = [x_1 \quad x_2 \cdots x_p]$.\\
 
@@
 
+\begin{lightbluebox}
+Describe differences
+\end{lightbluebox}
+
 \begin{figure}[!h]
@@
 \caption{Basic Representation of the Triple-Gamma-Penalty using Hyperparameters $c^\xi = 0.1, \kappa_B = 2, a^\xi = 0.75$ compared to \textit{LASSO} and \textit{Ridge} Penalties}
-\label{fig:basicTGPen}
+\label{fig:DifferentPenalties}
 \end{figure}
@@
 \subsection{Restricted Strong Convexity (RSC) of the Triple-Gamma-Regularization}
+
+\begin{lightbluebox}
+Weglassen?
+\end{lightbluebox}
 
@@
 
+\begin{lightbluebox}
+Propose different conecpts?
+\end{lightbluebox}
 \subsection{Approaches to Estimation}
@@
 Use the earlier derivation, code up the functions and simulate data to check behaviour for different datasets. Compare to base OLS, Ridge and Lasso Regression?
+
+\begin{lightbluebox}
+Ganze Simulation
+\end{lightbluebox}
+
+\subsection{Implementation as Python Package}
+\begin{lightbluebox}
+How to use it. 
+Explanation of Functions. Input - Output Tables
+\end{lightbluebox}
+
 \subsection{Computational Performance}
@@
 See how computation times change when increasing the size of the data set or when the number of parameter changes. => Use Stochastic Gradient Descent (SGD)
-\subsection{Implementation as Python Package}
 
-How to use it. 
-Explanation of Functions. Input - Output Tables
+\begin{lightbluebox}
+Kurzes Ansprechen von Computations Efficieny
+\end{lightbluebox}
 
@@
 \section{Possible Extensions and Criticism}
+
+\subsection{Implementation as Python Package}
+\begin{lightbluebox}
+Interessante unifying properties, aber langsam implementiert. 
+\end{lightbluebox}
 \section{Conclusion}
-
+\subsection{Implementation as Python Package}
+\begin{lightbluebox}
+ENDE
+\end{lightbluebox}
 \newpage
@@
 
-\pagebreak
 \pagenumbering{roman}

### 2024-08-06 01_latex/MScThesis_Econ.tex
Saftey Commit

@@
 \usepackage{lscape}
+\usepackage{adjustbox}
+
 % -----
@@
 
+\begin{lightbluebox}
+Finish Intro
+\end{lightbluebox}
+
+The remaining thesis is structure as follows: Section 3 will provide a literature review about the history of regularization and advancements in the field along with an overview of established concepts and their respective advantages and disadvantages.
+Section 4 will quickly discuss the mathematical building block for this thesis by showcasing the bridge between regularization and Bayesian shrinkage prior as well as introduce the Triple-Gamma-Prior by \textcite{TGP2020} as the shrinkage prior of choice.
+Section 5 will then derive the proposed penalty by utilizing the bridge explained in section 4.
+Section 6 will then apply the newly derived regularization penalty and apply it in the context of a simulation study to see its effects and possible fields of application.
+The remaining sections 7 and 8 will discuss shortcomings of the method and possible extensions and end with a summarizing conclusion.
+
 %----- Theoretical Section
@@
 This emphasizes the importance a sufficient sample size when fitting linear models.
-And this leads us to the core field of study of this thesis: What are ways to improve the generalization of a linear model in scenarios where the sample size is not sufficiently large enough?
+And this leads us to the core field of study of this thesis: What are ways to improve the generalization of a linear model in scenarios where the sample size is not sufficiently large enough or high-dimensionality becomes a problem?\\
 
-\begin{lightbluebox}
-
-- WAYS TO BATTLE COMPLEXITY
-
-Solutions (find source, seen in LMU course): (1) More data (Not always feasible) (2) Better data (Same issue) (3) Reduce Model Complexity (Regularization) (4) Less aggressive optimization (Maybe short review; Idea: Stop optimization when generalization error degrades)
-\end{lightbluebox}
+As already pointed out by \textcite{FanLi2006} almost 20 years ago, "high dimensional data analysis will be the most important research topic in statistics in the 21st century" and the advancements in data availability in recent decades have supported their hypothesis.
+The main problem to solve is how to accurately approach the problem of feature selection and make models generalize better.
+A first approach could be to increase the sample size to re-establish the unbiasedness of methods like OLS, however either the problem at hand involves a scenario with only few data points to begin with, or due to an extensive number of features, the collection of a sufficient amount of data points is practically not feasible.
+Another approach could be to use common variable selection methods like \textit{AIC} and \textit{BIC}, but as \textcite{FanLi2006} point out, "[t]raditional variable selection such as $C_p$, AIC and BIC involves a combinatorial optimization problem, which is NP-hard, with computational time increasing exponentially with the dimensionality." A third and computationally more feasible approach involves a concept called \textit{penalized regression}, more commonly known as \textit{Regularization}.
 
@@
 
-\begin{lightbluebox}
-Vielleicht noch genauer auf die Taxonomy eingehen? 
-\end{lightbluebox}
-
-Unsurprisingly, this thesis is concerned with the fourth group of regularization methods, which add a penalty/regularizer term $J(\beta)$ into the risk function, but before advancing to literature that deals with this kind of problem, it is necessary to establish a terminology which will be used throughout this thesis.
-\textbf{TODO}
+Unsurprisingly, this thesis is concerned with the fourth group of regularization methods, which add a penalty/regularization term $J(\beta)$ into the risk function, but before advancing to literature that deals with this kind of problem, it is necessary to establish a terminology which will be used throughout this thesis.
+This terminology will be the following:
 
@@
 This results in the overall optimization problem
-\begin{align*}
-&\underset{\beta \in \boldsymbol{\beta}}{\argmin}\left\{R_{reg}(\beta)\right\}\\
-&=\underset{\beta \in \boldsymbol{\beta}}{\argmin}\left\{R_{emp}(\beta) + \lambda\cdot J(\beta)\right\}\\
-&=\underset{\beta \in \boldsymbol{\beta}}{\argmin}\left\{\sum_{i=1}^n L(y_i, f_\beta(x_i)) + \lambda\cdot J(\beta)\right\}
-\end{align*}
+\begin{align}
+&\underset{\beta \in \boldsymbol{\beta}}{\argmin}\left\{R_{reg}(\beta)\right\}\nonumber\\
+&=\underset{\beta \in \boldsymbol{\beta}}{\argmin}\left\{R_{emp}(\beta) + \lambda\cdot J(\beta)\right\}\nonumber\\
+&=\underset{\beta \in \boldsymbol{\beta}}{\argmin}\left\{\sum_{i=1}^n L(y_i, f_\beta(x_i)) + \lambda\cdot J(\beta)\right\}\label{eq:genreg}
+\end{align}
 
@@
 
+\subsection{Bayesian View on Battling Model Complexity using Shrinkage Priors}\label{sec:BayesianShrinkagePriors}
+To build on the mathematical connection between the Bayesian and Frequentist approach to battle model complexity, which will be used as the building block of this thesis later on, it is necessary to make a quick detour and quickly recap on how Bayesian statisticians tackle model complexity.
+
 \begin{lightbluebox}
-Ad Solution (3) because it is relatively easy to implement: Simple approach => Start with simplest model and iteratively add one feature OR iteratively get rid of feature by feature.
-(Problem: Very arbitrary and hard to reasonably do) Thus, adjust risk function minimization.
-Important: Regularization adjusts generalization error, not training error!
-
-Short break: Talk about Taxonomy by Kukacka et al 2017 on the differing use of the term "regularization"
-
-What is needed: 
-\[
-R_{reg}(\beta) = R_{emp}(\beta)+ \lambda \cdot J(\beta)
-\]
-where $R_{emp}(\beta) = \sum_i^n L(y_i, f(x_i, \beta))$.
-Note: Regularization term does not depend on data, just on parametrization.
-$\lambda$ controls the strength of regularization.
-Thus, $\lambda = 0$ means simple MSE optimization and $\lambda \to \infty$ chooses simplest model.
-As $\lambda$ is set manually, this also bears some problems.
-However, typical solution is cross-validation.
-
-\textbf{Literature}
-\parencite{Taxonomy2017}
+Explain Shrinkage Prior
 \end{lightbluebox}
-
-\subsection{Bayesian View on Battling Model Complexity using Shrinkage Priors}\label{sec:BayesianShrinkagePriors}
-Explain how Bayesians battle model complexity.
 
@@
 Subset Selection on the other hand chooses variables in a discrete sense - a variables either stays within the model or it doesn't - and thus creates easily interpretable models, but "[s]mall changes in the data can result in very different models being selected and this can reduce its prediction accuracy." \parencite{Tibishirani1996} \textit{LASSO} is trying to combine both methods' advantages by using $\norm{\beta}_1$ as a penalty term.\\
-\begin{lightbluebox}
-Bit more on LASSO?
-\end{lightbluebox}
 
@@
 
+\begin{lightbluebox}
+Describe TRIPLE GAMMA PRIOR
+\end{lightbluebox}
+
 %----- Model Setup and Derivation
 \newpage
-\section{Model Setup and Derivation}
+\section{Model Setup and Derivation}\label{sec:modelderivation}
 Coming to the theoretical framework of the \textit{triple-gamma-regularization}, let's assume we have a response variable $y$ and $p$ predictors along with $n$ data points.
@@
 \[
-y_i = x_i^T\cdot \beta + \varepsilon_i \quad i\in \{1,...,n\} 
+y_i = x_i^T\cdot \beta + \varepsilon_i \quad i\in \{1,...,n\}. 
 \]
@@
 &= -\frac{n}{2} \log(2\pi\sigma^2) - \frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^\top (\mathbf{y} - \mathbf{X}\beta)\\
-&\propto - \frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^\top (\mathbf{y} - \mathbf{X}\beta) = - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2\\
+&\propto - \frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^\top (\mathbf{y} - \mathbf{X}\beta) = - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2.\\
 \end{align*}
@@
 p(\sqrt{\beta_j}|\phi^\xi, a^\xi, c^\xi) &= \frac{\Gamma(c^\xi + \frac{1}{2})}{\sqrt{2\pi \phi^\xi}\cdot B(a^\xi, c^\xi)}\cdot U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\\
-&\propto U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)
+&\propto U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right).
 \end{align*}
@@
 \begin{align*}
-p(\beta_j|\phi^\xi, a^\xi, c^\xi) &\propto U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)
+p(\beta_j|\phi^\xi, a^\xi, c^\xi) &\propto U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right).
 \end{align*}
@@
 			&= \prod_j^p \frac{1}{\Gamma(c^\xi + \frac{1}{2})}\int_0^\infty e^{-(\frac{\beta_j^2}{2\phi^\xi})t}t^{c^\xi + \frac{1}{2}-1}(1+t)^{\frac{3}{2}-a^\xi-c^\xi + \frac{1}{2}-1}dt \nonumber\\
-			&\propto \prod_j^p \int_0^\infty \exp\left(-\frac{\beta_j^2}{2\phi^\xi}t\right)t^{c^\xi - \frac{1}{2}}(1+t)^{1-a^\xi-c^\xi} dt \label{eq:prior}
+			&\propto \prod_j^p \int_0^\infty \exp\left(-\frac{\beta_j^2}{2\phi^\xi}t\right)t^{c^\xi - \frac{1}{2}}(1+t)^{1-a^\xi-c^\xi} dt. \label{eq:prior}
 \end{align}
@@
 \[
-\log(p(\beta))=\log(\prod_j^p p(\beta_j|\phi^\xi, a^\xi, c^\xi))=\sum_j^p \log(p(\beta_j|\phi^\xi, a^\xi, c^\xi))
+\log(p(\beta))=\log(\prod_j^p p(\beta_j|\phi^\xi, a^\xi, c^\xi))=\sum_j^p \log(p(\beta_j|\phi^\xi, a^\xi, c^\xi)).
 \]
 
-A common approach to estimation in regularization settings is the \textit{maximum a posteriori probability (MAP)} estimator \MC ,which is defined as
+A common approach to estimation in regularization settings is the \textit{maximum a posteriori probability (MAP)} estimator, which is defined as
 \[
-\hat{\beta}_{MAP}(x) = \underset{\beta \in \mathbb{R}^p}{\argmax}\left\{f(x|\beta)g(\beta)\right\}
+\hat{\beta}_{MAP}(x) = \underset{\beta \in \mathbb{R}^p}{\argmax}\left\{f(x|\beta)g(\beta)\right\}.
 \]
@@
 p(\beta|y, X, \sigma^2) 	&\propto p(y|X,\beta,\sigma)\times p(\beta) \nonumber\\
-						&\propto \frac{1}{(2\pi\sigma^2)^{n/2}}e^{-\frac{1}{2\sigma^2}(y-X\beta)^T(y-X\beta)} \times \prod_j^p U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\label{eq:posterior}
+						&\propto \frac{1}{(2\pi\sigma^2)^{n/2}}e^{-\frac{1}{2\sigma^2}(y-X\beta)^T(y-X\beta)} \times \prod_j^p U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right).\label{eq:posterior}
 \end{align}
@@
 							&= \log\left(\frac{1}{(2\pi\sigma^2)^{n/2}}\right) - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta^2}_2^2 + \sum_j^p \log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\right)\nonumber\\
-							&\propto -\frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \sum_j^p \log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right)\nonumber\\
+							&\propto -\frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \sum_j^p \log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right)\nonumber
 \end{align}
 
-To align with the general specification structure of regularization problems, which can be seen from equation \textbf{missEQ}, a parameter $\lambda$ will be multiplicatively added in front of the penalty term, which makes it possible to adjust the strength of the influence that the penalty has on the chosen parameters.
+To align with the general specification structure of regularization problems, which can be seen from equation \ref{eq:genreg}, a parameter $\lambda$ will be multiplicatively added in front of the penalty term, which makes it possible to adjust the strength of the influence that the penalty has on the chosen parameters.
 By minimizing the negative log-posterior adjusted with $\lambda$, we can retrieve the \textit{maximum a posteriori probability (MAP)} estimator using \textbf{Triple-Gamma-Regularization}:
@@
 \subsection{Varying the Hyperparameters}
-After closer inspection of equation \ref{eq:tgr}, it can easily be seen that this resembles the general penalized regression already seen in \textcite{ESLpage398} and in section \ref{sec:theorysuper} as $R(\beta) + \lambda\cdot J(\beta)$.
+After closer inspection of equation \ref{eq:tgr}, it can easily be seen that this resembles the general penalized regression already seen in \textcite[398]{ESL2009} and in section \ref{sec:theorysuper} as $R(\beta) + \lambda\cdot J(\beta)$.
 The first term, also called the empirical loss in machine learning literature, is the widely known residual sum of squares:
@@
 \]
-In contrast to the \textit{LASSO} penalty, which uses the the absolute value of the coefficient, or the \textit{Ridge} penalty, which uses the square of the estimate, this penalty derived from \textcite{TGP2020} is based on the $\log$ of the confluent hyper-geometric of the second kind.
+In contrast to the \textit{LASSO} penalty, which uses the the absolute value of the coefficient, or the \textit{Ridge} penalty, which uses the square of the estimate, this penalty derived from \textcite{TGP2020} is based on the $\log$ of the confluent hyper-geometric of the second kind introduced by \textcite{Tricomi1947}.
 Notably, this penalty term has three additional hyper-parameters: $c^\xi$, $a^\xi$ and $\kappa_B$ as $\phi^\xi = (2c^\xi)/(\kappa^2_B a^\xi)$.
 Here, the restrictions $a^\xi>0.5$ and $0 < c^\xi < \infty$ are necessary to ensure that the penalty for a $\beta_j$ being equal to zero remains finite and not diverges to negative infinity at zero.
-This results, which has already been presented and proven as part of Theorem 2 in \textcite[5--6]{TGP2020}, ensures that the negative $\log$ of the hypergeometric function remains finite and thus does not produce parameter estimates which are zero for every variables.
-(\textbf{BESSER SCHREIBEN?})\\
-\begin{lightbluebox}
-Write more to fill this page
-\end{lightbluebox}
+This results, which has already been presented and proven as part of Theorem 2 in \textcite[5--6]{TGP2020}, ensures that the negative $\log$ of the hypergeometric function remains finite and thus does not produce parameter estimates which are zero for every variables.\\
+
+In contrast to penalties like \textit{LASSO} and \textit{Ridge} which have a pre-defined structure, the hyperparameters of \textit{Triple-Gamma} penalty make it possible to adjust the structure of the penalty and thus its influence on the overall optimization problem.
+Of course, the other penalties have simpler mathematical structures, but are very limited in adapting to different settings.
+Thus, the \textit{Triple-Gamma} penalty trades some of the mathematical simplicity to gain more flexibility by introducing these hyperparameters.
+The next few pages will elaborate on the different effects that different values of these hyperparameters have on the overall structure of the penalty.
+
 \newpage
@@
 
-\begin{figure}[!h]
+\begin{figure}[h!]
 \centering
@@
 Again, starting from the baseline with $c^\xi = 0.1$, higher values for this hyper-parameter mainly change the behaviour of the penalty in the tails.
-A result that has already been shown by \textcite{TGP2020} in Table 1, where multiple different hyper-parameter settings are presented, is that with an increasing value for $c^\xi$ and with $a^\xi = 1$ \textbf{as well as kappaB = ??}, the Triple-Gamma-Prior converges to a \textit{LASSO} like shrinkage behaviour.
+A result that has already been shown by \textcite{TGP2020} in Table 1, where multiple different hyper-parameter settings are presented, is that with an increasing value for $c^\xi$ and with $a^\xi = 1$ as well as $\kappa_B = 2$, the Triple-Gamma-Prior converges to a \textit{LASSO} like shrinkage behaviour.
 A property which carries over to the proposed regularization setting when using the proposed hyper-parameter values, thus showing that the Triple-Gamma-Penalty can be used both as a non-convex penalty as well as a \textit{LASSO} penalty, creating increased flexibility in modelling approaches.
@@
 A plot with several different values for the absolute value of $\kappa_B$ can be found in figure \ref{fig:TGPenalty_ChangeInKappa}.
+It can be seen that $\kappa_B$ has a scaling effect on the strength of the penalty, thus playing a similar role as the generally multiplicatively added regularization parameter $\lambda$.
+For small values of $\kappa_B$, the penalty only has a weak singularity in small neighbourhoods around $0$, thus making it more likely for the parameters to be different from zero.
+As $\kappa_B$ increases, the spike becomes more pronounced and thus increases the added penalty for parameters different from zero.
+\\
 
-\begin{figure}[t]
+\begin{figure}[h!]
 \centering
@@
 
+Although it has a scaling effect like $\lambda$, it still has this structural effect as well.
+Allowing myself to use a Bayesian analogy in this setting, it can be viewed as follows: Increasing $\kappa_B$ corresponds to a way of putting more prior knowledge on zero and thus pulling coefficients stronger towards zero.\\
+
+A summary of all these effects can be found in table \ref{tab:VariationsInHyperparameters} below where the effects of positive and negative changes in the hyperparameters as well as defined ranges for these parameters are defined.
+
 \newpage
@@
 \begin{landscape}
-\begin{table}[!h]
-\begin{center}
+\hspace{3cm}
+\begin{table}[h!]
+\centering
 \begin{tabular}{lcccccc}\toprule
-		& \multicolumn{2}{l}{Change} & \multicolumn{3}{c}{Mathematical Properties}\\
+		& \multicolumn{2}{c}{Change} & \multicolumn{2}{c}{Mathematical Properties}\\
 		\cmidrule(r{4pt}){2-3} \cmidrule(l){4-5}
 Variable     	& \textbf{Positive} Change  & \textbf{Negative} Change & Defined Range & Misc.\\\midrule
-$a^\xi$  	& \makecell{Shifting towards\\ \textit{Gaussian}-like behaviour\\ at $\beta = 0$} & \makecell{Shifting towards singularity\\ at $\beta = 0$; Higher\\ immediate penalty for coefficients\\ $\beta \neq 0$} & $(0.5, \infty)$ & Expl.\\
+$a^\xi$  	& \makecell{Shifting towards\\ \textit{Gaussian}-like behaviour\\ at $\beta = 0$} & \makecell{Shifting towards singularity\\ at $\beta = 0$; Higher\\ immediate penalty\\ for coefficients\\ $\beta \neq 0$} & $(0.5, \infty)$ & -\\
 $c^\xi$ 		& \makecell{Generally, convergence towards \\ convexity and, given certain \\ settings for $a^\xi$ and\\ $\kappa_B$, LASSO.
-Higher values\\ increase the additional penalty\\ for higher absolute values of $\beta$.} &  \makecell{For values smaller \\ than $0.1$, similar effect\\ to increase in $a^\xi$} & $(0, \infty)$ & Expl.
-\\
-$\kappa_B$ 	& 15883 & 5.2e-8 & $(-\infty, \infty)/\{0\}$ & Expl. \\\bottomrule
+Higher values\\ increase the additional penalty\\ for higher absolute values of $\beta$.} &  \makecell{For values smaller \\ than $0.1$, similar effect\\ to increase in $a^\xi$} & $(0, \infty)$ & - \\
+$\kappa_B$ 	& \makecell{The singularity\\ at $\beta=0$ becomes more\\ pronounced, putting more\\ \textit{prior knowledge} on $\beta$\\ being zero.} & \makecell{The reverse effect\\ to the positive effect.} & $(-\infty, \infty)$ & \makecell{When $\kappa_B=0$, the\\ value of $\beta$ doesn't affect\\ the overall penalty anymore,\\ thus reverting the optimization\\ problem back to the\\ non-penalized one.} \\\bottomrule
 \end{tabular}
@@
 \label{tab:VariationsInHyperparameters}
-\end{center}
 \end{table}
 \end{landscape}
+
 \newpage
@@
 Seeing that, due to its flexibility, there is not \textit{one} \textit{Triple-Gamma} penalty, three distinct hyper-parameter setting have been chosen to represent the proposed penalty term.
+\begin{enumerate}
+\item Setting 1: \quad $a^\xi=0.75$, $c^\xi=0.1$, $\kappa_B = 2$
+\item Setting 2: \quad $a^\xi=5$, $c^\xi=0.01$, $\kappa_B = 2$
+\item Setting 3: \quad $a^\xi=0.51$, $c^\xi=0.001$, $\kappa_B = 1$
+\end{enumerate}
 
@@
 
-\subsection{Restricted Strong Convexity (RSC) of the Triple-Gamma-Regularization}
+%\subsection{Restricted Strong Convexity (RSC) of the Triple-Gamma-Regularization}
 
-\begin{lightbluebox}
-Weglassen?
-\end{lightbluebox}
+%\begin{lightbluebox}
+%Weglassen?
+%\end{lightbluebox}
 
@@
 \end{lightbluebox}
-\subsection{Approaches to Estimation}
 
 %----- Simulation Section
-\section{Simulation Section}
-Use the earlier derivation, code up the functions and simulate data to check behaviour for different datasets. Compare to base OLS, Ridge and Lasso Regression?
+\newpage
+\section{Simulation Study}
+To test the proposed method of section \ref{sec:modelderivation} a simulation study will now be conducted whether, and if so, in what scenarios, the \textit{Triple-Gamma} penalty might be valuable addition to the literature.
+Of course several previously introduced methods have also been tested using simulation studies, but the methodology behind these studies usually varies from paper to paper.
+However, before moving on to this section of the thesis, the question remains on how to solve the optimization problem in \ref{eq:tgr}.
 
-\begin{lightbluebox}
-Ganze Simulation
-\end{lightbluebox}
+\subsection{Approaches to Estimation}
+As already mentioned in chapter \ref{sec:litreview}, non-convex penalties like the \textit{Triple-Gamma} penalty are usually harder to solve than convex optimization problems.
+The reason being that convex functions have a unique global minimum, whereas non-convex functions can have multiple local minima, which are not necessarily a global minimum.
+\textbf{(SOURCE)}.
+In addition, unlike for example \textit{Ridge} regression, the \textit{Triple-Gamma} penalty like many other established penalties in the literature does not have a closed form solution for this optimization problem.
+Thus, it is necessary to apply an optimization algorithm which solves this problem iteratively.
+An algorithm which has established itself to solve these kinds of problems is called \textit{Gradient Descent} \parencite[229--248]{GrippoSciandrone2023}.
+In its essence, the algorithm tries to minimize a loss function by iteratively adjusting the model parameters in the direction that reduces the loss most.
+It calculates the gradient of the loss function with respect to the model parameters and then updates the parameters by a learning rate.
+This iterative process can either be repeated until a specified number of iterations is reached or a local (or global) minimum has been found.
+As already mentioned, this can lead to problems when dealing with non-convex optimization problems as multiple local minima might exist, which do not necessarily need to be global ones.
+Various approaches to deal with this have been proposed.
+One method uses random starting points to cover various areas of the optimization space to cover potential multiple local minima.
+Another method is called \textit{Stochastic Gradient Descent (SGD)} and uses different batches of the dataset to estimate the model parameters \parencite{Amari1993}.
+The \textit{Gradient Descent} method will be used for the simulation study in the following chapter.\\
+
+For the sake of completeness and as a stepping stone for further research, it is necessary to mention a different approach to solve the optimization problem which is called \textit{Local Linear Approximation (LLA)} algorithm and has been proposed by \textcite{ZouLi2008}.
+Their resulting \textit{one-step LLA estimates} have several computational advantages and "alleviate the computation burden in the iterative algorithm and overcome the potential local maxima problem in maximizing the nonconcave penalized likelihood" \parencite{ZouLi2008}.
+Still, to the best of my knowledge, no easily accessible programming packages exist for this algorithm.
+
+\subsection{Scenario Simulation}
+Various simulation studies comparing different regularization penalties have been published so far.
+\textcite{VettamJohn2022} for example have compared \textit{LASSO, Ridge, MCP, SCAD, Laplace} and \textit{Arctan} in the context of the estimation of neural networks.
+\textcite{WangEtAl2020} have tested a range of penalties in the context of linear models and analysed various the performance of penalties using levels of sparsity, dimensionality and data availability.
+The authors tested the performance based on three criteria: \textit{prediction}, \textit{variables selection} and \textit{variables ranking}.
+This simulation study will focus on the the first two metrics.\\
+
+\textit{Prediction} is usually measured by splitting a simulated dataset into a training dataset and a test dataset.
+The model is fitted on the training dataset and then tested on the test dataset using a metric like the \textit{mean squared error (MSE)}.
+\textit{Variable Selection} is measured in various ways.
+\textcite{WangEtAl2020} used \textit{true-positive} and \textit{false-positive} rates as their metric of choice.
+As several of the tested methods in this simulation study do not perform variable selection naturally due to its \textit{smooth-at-origin} property and thus report estimates larger than zero, a different metric will be chosen for this simulation study.
+To test whether models accurately predict the underlying data generating process and also result in estimates close to its true coefficients, the square of the absolute deviation between the true coefficient and the estimated coefficient of each variable will be computed and summed up.
+Using this metric, models whose estimates are close the true coefficients will perform than models whose estimates are far off.\\
+
+To evaluate the models in a wide range of contexts, every simulation scenario will vary in terms off three variables: \textit{sample size $N$} (ie $N=100$ meaning that for every run, a total of $100$ observations will be generated), \textit{dimensionality $p$} (ie $p=10$ meaning a total of ten covariates will included in the model) and \textit{sparsity $s$} (ie $s=0.1$ meaning that 10\% of the covariates have a true coefficients different from zero).
+The set of values chosen for each scenario variable can be found in table \ref{tab:Scenarios}.
+Using this values, all possible combinations of these variable settings will be formed, resulting in a total of $48$ possible scenarios.
+
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{lc}\toprule
+Variable & Values\\\midrule
+Sample Size $N$ & $50, 100, 500, 1000$\\
+Dimensionality $p$ & $3, 10, 40$\\
+Sparsity $s$ & $0.1, 0.3, 0.5, 0.9$\\\bottomrule
+\end{tabular}
+\caption{Scenarios Values}
+\label{tab:Scenarios}
+\end{center}
+\end{table}
+
+The remaining issue to cover deals with the weighting/regularization parameter $\lambda$ (see section \ref{sec:theorysuper}) and how it is set.
+This key parameter controlling the strength of the influence of the penalty on the overall optimization result is usually set by the user, however another \textit{hands-off} method is cross-validation, which will be used for this simulation \parencite[250--251]{ESL2009}.
+A grid of possible values for $\lambda$ is chosen, the model is being estimated for every possible value, and the best model will be chosen based on the chosen cross-validation metric.
+For this simulation study, all values between $0$ and $1$ based on $0.01$ steps will be tested.
+The simulations have been run with Python (Version 3.11.4) along with scikit-learn (Version 1.4.1.post1) and PyTorch (Version 2.2.2).\footnote{More information on the packages used and its installed version can be found in the accompanying GitHub repository.}
+
+\subsection{Simulation Study for Prediction}
+
+\subsection{Simulation Study for Variable Selection}
 
 \subsection{Implementation as Python Package}
+
+This section provides a brief overview of the Python script, which has been used to run the simulations of the previous section, along with input/output descriptions of the defined functions.
 \begin{lightbluebox}
@@
 
-%----- Small Applied Section
-%\section{Small Applied Section}
-%Here I am planning to apply the TGP using Peter's Bayesian Package and the self coded frequentist code on a small dataset.
 \section{Possible Extensions and Criticism}
 
-\subsection{Implementation as Python Package}
 \begin{lightbluebox}

### 2024-08-08 01_latex/MScThesis_Econ.tex
LOTS OF WORK commit - please no conflict

@@
 \usepackage{tikz}
+\usepackage{float}
 
@@
 \usepackage{adjustbox}
+\usepackage{longtable}
 
@@
 \begin{abstract}
-Lorem ipsum...
+\begin{lightbluebox}
+Add abstract as soon as the thesis is 100\% finished.
+\end{lightbluebox}
 \end{abstract}
@@
 
-I like to acknowledge ...
+This completion oft his thesis would not have been possible without so many amazing people in my life who supported me throughout the process of writing this master's thesis and the master program as a whole.
+I want to thank my mum, Daniela, and my dad, Werner, who always picked me up when I lost my motivation to continue and who convinced me to keep going time after time.
+I want to thank my brother, Tobias, who always readily listened to me complaining for hours and hours on end about things he probably barely understood and yet always agreed with me about my computational issues while doing the simulations.
+And most of all I want to thank my advisor, Peter, who always supported me from the day I randomly dropped an e-mail into his e-mail inbox about becoming his tutor in econometrics, although not having met once during the distance learning phase of the COVID pandemic, up until today.
+From working as a tutor in his team, writing a bachelor thesis, and to the support during this master thesis now.
+Even though sometimes living 12h time differences apart, one in Boston the other in Manila, he always answered any questions I had and supported me in whatever way he could and I want to sincerely thank him for that!
 
@@
 Since then nonetheless, the principle has long been used by statisticians and other researchers as a a scientific credo to capture the notion that "the simpler of two explanations is to be preferred" \parencite{Lazar2010}.
+Recent decades and its advancements in information technology have opened the gates to seemingly unlimited amounts of data and information.
+Whether it is data about the carbon dioxide levels near bus stations in a city, the intraday trading volume of a specific financial asset or the rhythm of a beating heart throughout a day, new techniques and approaches in measuring digital and natural phenomena have enables researchers all around the globe to study previously unknown effects, test novel hypotheses and find relationships between real world process that would have otherwise remained hidden from the eye of human civilization.\\
 
-\begin{lightbluebox}
-Finish Intro
-\end{lightbluebox}
+Yet, these advancements come at a cost.
+Conventional statistical models like the \textit{ordinary least squares (OLS)} have troubles handling statistical problem in higher dimensions.
+When the relative number of features to the number of data points in a statistical model is very high, the estimates of these models suffer from high variance and thus generalize poorly.
+Frequentist statisticians have developed penalized regression approaches to battle these issues by incorporating a penalty term into the optimization problems used to estimate the coefficients of linear models.
+In recent decades, various penalty terms have been published with each of its own advantages and disadvantages, yet to this day no a single method has emerged to triumph above them all \parencite{WangEtAl2020}.\\
+
+Bayesian statisticians have developed their own tools to handle high-dimensional statistical problems and commonly use specific probability distributions to battle model complexity by shrinking the estimates of less important variables towards zero (thus the name \textit{shrinkage prior}).
+Although these two fields of statistical thought use different approaches to tackle the same problem, a striking mathematical connection exists between those two methods.
+A bridge which allows mathematicians to derive a regularization penalty from specific prior distributions, which raises the question: "Does there exist a already known prior distribution in the Bayesian setting which can be used to derive a regularization penalty which might perform better than existing penalties?".\\
+
+A prior distribution which might have these suitable properties is the unifying shrinkage prior developed by \textcite{TGP2020} called \textit{Triple-Gamma-Prior}.
+Its unifying properties and the fact that a closed-form solution for the marginal prior exists might lead to favourable properties in the realm of frequentist statistics, but before that it is necessary to have a closer look at what the exact problem is that Bayesian shrinkage prior and regularization approaches are trying to solve.
+An overview of this along with a theoretical basis of the necessary concepts will be presented in section 2.\\
 
@@
 \textit{Prediction} on the other hand aims at forecasting the output variable $Y$ as accurately as possible and using every bit of information that is available, but disregards interpretability.
-\parencite{ESL,21} These goals can be summarized by viewing it as a decision between \textit{prediction accuracy} and \textit{model interpretability}, which has thoroughly been explained by \textcite{ESL}.\\
+\parencite[21]{ESL2009} These goals can be summarized by viewing it as a decision between \textit{prediction accuracy} and \textit{model interpretability}, which has thoroughly been explained by \textcite{ESL2009}.\\
 
@@
 where $L(.)$ refers to a loss function defined as some function of the true values and the predicted values and $J(f)$ is penalty based on the chosen functional from a space of functions $\mathcal{H}$.
-In the context of penalized linear regression, this is equivalent to finding the set of risk minimizing coefficients $\hat{\beta}$ from the set of all possible combinations of coefficients $\boldsymbol{\beta}$.
+In the context of penalized linear regression, this is equivalent to finding the set of risk minimizing coefficients $\hat{\beta}$ from the set of all possible combinations of coefficients $\beta$.
 \MC Thus, resulting in the general class of regularization problems of the form:
@@
 Non-Convex penalties, which are usually convergent in its limits towards $-\infty$ and $+\infty$, tend to yield unbiased results as the additional penalty becomes zero as soon as a certain threshold is crossed (Again, referring to the visualisation in figure \ref{fig:DifferentPenalties}).
+
+\begin{lightbluebox}
+Still have to figure out how to fit this table.
+\end{lightbluebox}
+
 \begin{table}[!h]
 \begin{center}
-\begin{tabular}{lcccc}\toprule
+\begin{tabular}{llccc}\toprule
  \multicolumn{2}{c}{Penalty} & \multicolumn{3}{c}{Classification}\\
@@
 
-Yet, before diving into the mathematical core of this thesis which derives said concept, it is necessary to have a look at the Triple-Gamma-Prior in depth to explain why this particular prior might prove itself to provide a useful building block for a novel regularization penalty.
+Yet, before diving into the mathematical core of this thesis which derives said concept, it is necessary to have a look at the Triple-Gamma-Prior in depth to explain why this particular prior might prove itself to provide a useful building block for a novel regularization penalty.\\
+
+As already mentioned above, BMA and shrinkage priors are two Bayesian approaches to deal with statistical problems in high-dimensional settings.
+The prior is generally constructed for variance selection in sparse state space and TVP models and is named the Triple-Gamma-Prior as it's representation is given by three Gamma distributions.
+A key advantage of this prior is its unifying property.
+As cam be seen in table 1 in \textcite{TGP2020}, special cases of the prior, depending on certain values in its hyperparameters, are the Normal-Exponential-Gamma, the Horseshoe and the double Gamma prior.
+In addition, it can also be seen as a special case of the LASSO prior.
+Another advantage is its function as a bridge between spike-and-slap and continuous shrinkage prior as the hyperparameters can be used both for steering the shrinkage effect on noise while also preventing overshrinking the signal.
+Computationally the shrinkage prior performs better than commonly used spike-and-slab priors as it is a continuous shrinkage prior which can more easily implemented using Markov-Chain-Monte-Carlo (MCMC) methods.\\
+
+Mathematically, the prior builds on the work by \textcite{BittoFS2019} in which the authors introduced the \textit{double gamma prior} with the following hierarchical representation:
+
+$$\theta_j|\xi^2_j \sim \mathcal{G}\left(\frac{1}{2}, \frac{1}{2\xi^2_j} \right), \quad \xi^2_j | a^\xi, \kappa^2_B \sim \mathcal{G}\left(a^\xi, \frac{a^\xi\kappa_B^2}{2}\right)$$
+
+It is important to note here, that the \textit{double gamma prior} is a global-local shrinkage prior, where the global hyperparameter $\kappa^2_B$ is the same for all parameters $\theta_j$ and the local hyperparameter $\xi^2_j$ is the local component.
+The \textit{Triple-Gamma-Prior} now adds a third Gamma prior into this framework by replacing $\kappa_B^2$ in the second-level prior with $\kappa_j^2$, which follows
+$$\kappa_j^2 | c^\xi, \kappa_B^2 \sim \mathcal{G}\left(c^\xi, \frac{c^\xi}{\kappa_B^2}\right)$$
+
+The core property which is relevant to this thesis can be found in \textit{Theorem 1 (b)} in \textcite{TGP2020} which shows that the \textit{Triple-Gamma-Prior} has a closed-form marginal prior distribution for the parameter $\theta_j$, or to stick with the terminology of this thesis $\beta_j$.
+The prior is given by
+$$p(\sqrt{\beta_j}|\phi^\xi, a^\xi, c^\xi) = \frac{\Gamma(c^\xi + \frac{1}{2})}{\sqrt{2\pi \phi^\xi}\cdot B(a^\xi, c^\xi)}\cdot U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right),$$
+where $\phi^\xi = \frac{2c^\xi}{\kappa^2_Ba^\xi}$ and $U(a,b,z)$ is the confluent hyper-geometric function of the second kind of \textcite{Tricomi1947} given by
+$$U(a,b,z) = \frac{1}{\Gamma(a)}\int_0^\infty e^{-zt}t^{a-1}(1+t)^{b-a-1}dt$$
+
+According to the mathematical connection described above, this prior can now be used to derive a novel regularization penalty.
 
 \begin{lightbluebox}
-Describe TRIPLE GAMMA PRIOR
+Should I talk more extensively about the TGP? Is there something important I forgot to mention?
 \end{lightbluebox}
@@
 Seeing that, due to its flexibility, there is not \textit{one} \textit{Triple-Gamma} penalty, three distinct hyper-parameter setting have been chosen to represent the proposed penalty term.
-\begin{enumerate}
-\item Setting 1: \quad $a^\xi=0.75$, $c^\xi=0.1$, $\kappa_B = 2$
-\item Setting 2: \quad $a^\xi=5$, $c^\xi=0.01$, $\kappa_B = 2$
-\item Setting 3: \quad $a^\xi=0.51$, $c^\xi=0.001$, $\kappa_B = 1$
-\end{enumerate}
 
-\begin{lightbluebox}
-Describe differences
-\end{lightbluebox}
+\begin{table}[h!]
+\centering
+\begin{tabular}{l|ccc}\toprule
+		& \multicolumn{3}{c}{Hyperparameter} \\\cmidrule(r{4pt}){2-4}
+     	& $a^\xi$  & $c^\xi$ & $\kappa_B$\\\midrule
+Setting 1&	$0.75$	&	$0.1$ &	$2$\\
+Setting 2&	$5$  &   $0.01$ & $2$\\
+Setting 3&  $0.51$  & $0.001$&$1$\\ \bottomrule
+\end{tabular}
+\caption{Three Example Settings of the \textit{Triple-Gamma} Penalty}
+\label{tab:TGSettings}
+\end{table}
 
-\begin{figure}[!h]
+A visualisation of these settings can be found in figure \ref{fig:DifferentTGPSettings}.
+It can be seen that all settings differ heavily in its structure and thus its influence on the optimization problem and in the end the resulting parameters.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_DifferentSettings.png}
+\caption{Different Settings of the Triple-Gamma-Penalty}
+\label{fig:DifferentTGPSettings}
+\end{figure}
+
+\textit{Setting 1} is a \textit{LASSO} like regularization penalty, but still keeps the non-convex shape of the Triple-Gamma penalty.
+\textit{Setting 2} introduces the smooth-at-origin property but keeps a similar shape than \textit{setting 1} in the tails.
+\textit{Setting 3} has the most distinct structure with a strong singularity at origin but tails which fall of very quickly and thus adds relatively little penalty for parameters that are above $1$ in absolute terms.\\
+
+\begin{figure}[h!]
 \centering
@@
 
-%\subsection{Restricted Strong Convexity (RSC) of the Triple-Gamma-Regularization}
+Additionally, a comparison of these \textit{Triple-Gamma} settings to a selection of other regularization penalties can be found in figure \ref{fig:DifferentPenalties}.
+As can be seen here, \textit{setting 1} of the \textit{Triple-Gamma} penalty imitates a \textit{LASSO} penalty with a slightly decreasing additional penalty, resulting in a weakened bias which is common to \textit{LASSO} estimates.
+\textit{Setting 3} has a similar structure than the non-convex penalties \textit{Gaussian} and \textit{Arctan}, but with a string singularity at zero.
+Here, it can clearly be seen that the \textit{Triple-Gamma} penalty is not a penalty which converges in the tails, as do \textit{Gaussian} and \textit{Arctan}, but still has a considerably weaker bias as convex methods like \textit{LASSO} and \textit{Ridge}.
+Overall, figure \ref{fig:DifferentPenalties} showcases the variety of possible penalties that can be implemented using the \textit{Triple-Gamma} penalty.
 
-%\begin{lightbluebox}
-%Weglassen?
-%\end{lightbluebox}
+%\subsection{Alternative Specification (with +1 to mimic artan)}
 
-\subsection{Alternative Specification (with +1 to mimic artan)}
-
+%Before moving on to the simulation study in section \ref{sec:simstudy_overall}, this might be the suitable place in this thesis to elaborate on a related concept.
 As previously mentioned, the \textit{Arctan} penalty developed by \textcite{WangZhu2016} has a similar structure as the \textit{Triple-Gamma-Penalty} in small neighbourhoods near $\beta = 0$ when using specific hyper-parameters (see section \ref{subsec:comparepenalties}).
@@
 
-\begin{lightbluebox}
-Propose different conecpts?
-\end{lightbluebox}
+%\begin{lightbluebox}
+%Propose different concepts?
+%\end{lightbluebox}
 
@@
 \newpage
-\section{Simulation Study}
+\section{Simulation Study}\label{sec:simstudy_overall}
 To test the proposed method of section \ref{sec:modelderivation} a simulation study will now be conducted whether, and if so, in what scenarios, the \textit{Triple-Gamma} penalty might be valuable addition to the literature.
@@
 The reason being that convex functions have a unique global minimum, whereas non-convex functions can have multiple local minima, which are not necessarily a global minimum.
-\textbf{(SOURCE)}.
-In addition, unlike for example \textit{Ridge} regression, the \textit{Triple-Gamma} penalty like many other established penalties in the literature does not have a closed form solution for this optimization problem.
+\MC In addition, unlike for example \textit{Ridge} regression, the \textit{Triple-Gamma} penalty like many other established penalties in the literature does not have a closed form solution for this optimization problem.
 Thus, it is necessary to apply an optimization algorithm which solves this problem iteratively.
@@
 The authors tested the performance based on three criteria: \textit{prediction}, \textit{variables selection} and \textit{variables ranking}.
-This simulation study will focus on the the first two metrics.\\
+This simulation study will focus on the the first of these metrics.\\
 
@@
 The model is fitted on the training dataset and then tested on the test dataset using a metric like the \textit{mean squared error (MSE)}.
-\textit{Variable Selection} is measured in various ways.
+\textit{\textit{Variable Selection} is measured in various ways.
 \textcite{WangEtAl2020} used \textit{true-positive} and \textit{false-positive} rates as their metric of choice.
@@
 To test whether models accurately predict the underlying data generating process and also result in estimates close to its true coefficients, the square of the absolute deviation between the true coefficient and the estimated coefficient of each variable will be computed and summed up.
-Using this metric, models whose estimates are close the true coefficients will perform than models whose estimates are far off.\\
+Using this metric, models whose estimates are close the true coefficients will perform than models whose estimates are far off.\\}
+\begin{lightbluebox}
+Some of the previous paragraph is in italic, because I initially planned on running a second simulation study on this metric as well, but implementation and runtime issues made it difficult.
+Will probably just mention it.
+\end{lightbluebox}
 
@@
 The set of values chosen for each scenario variable can be found in table \ref{tab:Scenarios}.
-Using this values, all possible combinations of these variable settings will be formed, resulting in a total of $48$ possible scenarios.
+Using this values, all possible combinations of these variable settings will be formed, resulting in a total of $36$ possible scenarios.
 
@@
 Sample Size $N$ & $50, 100, 500, 1000$\\
-Dimensionality $p$ & $3, 10, 40$\\
-Sparsity $s$ & $0.1, 0.3, 0.5, 0.9$\\\bottomrule
+Dimensionality $p$ & $3, 10, 25$\\
+Sparsity $s$ & $0.1, 0.5, 0.9$\\\bottomrule
 \end{tabular}
@@
 A grid of possible values for $\lambda$ is chosen, the model is being estimated for every possible value, and the best model will be chosen based on the chosen cross-validation metric.
-For this simulation study, all values between $0$ and $1$ based on $0.01$ steps will be tested.
-The simulations have been run with Python (Version 3.11.4) along with scikit-learn (Version 1.4.1.post1) and PyTorch (Version 2.2.2).\footnote{More information on the packages used and its installed version can be found in the accompanying GitHub repository.}
+For this simulation study, all values between $0$ and $1$ based on $0.01$ steps will be tested on the first generated dataset.
+To save time when it comes to computation, the search will be stopped if the chosen metric hasn't improved for more than 10 new values for $\lambda$.
+After his run, these optimal values will be used in the overall simulation.
+\textbf{For the application of the gradient descent algorithm a maximum number of 750 epochs has been set.} The simulations have been run with Python (Version 3.11.4) along with scikit-learn (Version 1.4.1.post1) and PyTorch (Version 2.2.2).\footnote{More information on the packages used and its installed version can be found in the accompanying GitHub repository.}
 
@@
 
-\subsection{Simulation Study for Variable Selection}
+For the simulation study testing the models prediction accuracy the key metric to test performance will be the \textit{mean-squared-error (MSE)}.
+The data is being generated the following way: Given a set of scenario parameters $N_i$, $p_i$ and $s_i$, the first $s_i*p_i$ coefficients, rounded to the next larger integer, will be generated from a normal distribution with mean $0$ and variance $1$, the remaining coefficients will be set to zero.
+Then, $N_i$ draws will be generated from a normal distribution with mean $0$ and variance $1$ for each of the $p_i$ features.
+Using these coefficients and the data from the features a response variable $y$ will be computed and noise drawn from a normal distribution with mean $0$ and variance $1$ multiplied with $0.5$ will be added as noise.
+First, the grid search for the optimal $\lambda$ will be performed by generating a sample dataset using the above generating process.
+Then, every method that is part of the simulation will be estimated on the dataset for every $\lambda_i$ in the set $\lambda_i \in \{0, 0.01, 0.02, \cdots, 1\}$.
+For every method separately, the $\lambda_i$ which generates the lowest validation loss on the testset will be used for the overall simulation.\\
+
+Using the set of scenario variables mentioned in table \ref{tab:Scenarios}, all possible combinations will be formed resulting in the overall $36$ scenarios.
+The code iterates through the list of scenarios, generates 25 datasets based on these scenarios variables and all tested methods will be estimated on every one the test part of these datasets.
+Afterwards, the validation loss will be computed for each method and stored.
+This procedure results in tables \ref{tab:PredSim}, which shows the mean and standard deviation of the distribution of the validation loss for every scenario and every methods.
+The values colored in \textcolor{red}{red} indicate the smallest means for every scenario.
+Before advancing to the overall results of this simulation study, it might be useful to have a look at a specific scenario to better understand the results in table \ref{tab:PredSim}, which will be the scenario with $N=100, p=25, s=0.1$.\\
+
+In this scenario, we are dealing with a dataset of $100$ observations, $25$ features and $3$ non-zero coefficients.\footnote{$25 \times 0.1 = 2.5$ and $ceil(2.5)=3$.} A figure with boxplots showcasing the distributions of the Mean-Squared-Error rates on the validation set for all methods can be found in figure \ref{fig:SpecificScenario}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.55]{../02_simulation/021_simulation_figures/Scenarion_100_25_3.png}
+\caption{Distribution of MSE on Validation Set in the Scenario with $100$ Observations, $25$ Features and $3$ non-zero Coefficients}
+\label{fig:SpecificScenario}
+\end{figure}
+
+This scenario, which is a good exmaple for a sparse scenario, where a lot of features are in the dataset but only a small part of it is different from zero, i.e.
+has an effect on the outcome.
+Here, \textit{LASSO} performs well which was to be expected, but it can also be seen that the first and second setting of the \textit{Triple-Gamma} Penalty can both produce similar results when it comes to predictive power.
+\textit{Setting 2} even has a lower mean in MSE ($0.25255$) than \textit{LASSO} regression ($0.2858$).
+\textit{OLS} manages to perform quite well, yet has a visible shift towards higher \textit{MSE} values.
+\textit{Arctan, Gaussian} and the third setting of the \textit{Triple-Gamma} penalty perform significantly worse in this scenario.\\
+
+Generally, it can be seen table \ref{tab:Scenarios} that the larger the sample size gets, the better OLS performs on the dataset as enough data is present for the OLS regression to work properly.
+However, in sparse data settings as well as when the sample size is low, regularization approaches regularly outperform the OLS method, which aligns with theory.
+Essentially, \textit{LASSO} and the \textit{first} and \textit{second} setting of the \textit{Triple-Gamma} penalty outperform most other methods in these scenarios.
+Especially, the two models estimated with these two settings of the \textit{Triple-Gamma} approach manage to work best in these scenarios in most cases, highlighting the potential benefit that the \textit{Triple-Gamma} regularization might have in these scenarios.\\
+
+\begin{lightbluebox}
+I will extend my discussion on the results and go a bit more into detail. But the general idea of the results should be there.
+\end{lightbluebox}
+
+\newpage
+\subsection{Computational Efficiency}
+At this point of the thesis it is necessary to quickly cover the topic of computational efficiency.
+As mentioned earlier, this simulation study has been implemented using Python along with PyTorch.
+As the \textit{Triple-Gamma} penalty is not a simple algebraic computation, as for example computing the absolute value of a real number in the case of \textit{LASSO} or computing the arcus tangens in the case of the \textit{Arctan} penalty, it is apparent that the computation of the loss function given a set of parameters is not very straight-forward and computationally expensive.
+In its current implementation, the Python function computing the \textit{Triple-Gamma-Loss} has to access a second function which approximates the logarithm of the confluent hyper-geometric  function of the second kind.
+More importantly, it does so for every parameter in the model.
+This is, to no surprise, very inefficient and makes computations in high dimensions unnecessarily complicated.
+In figure \ref{fig:ComputationTime} a plot can be found which shows the time to estimate all three settings of the \textit{Triple-Gamma-Regularization} on a dataset generated with parameters $N=100$ and $s=0.1$ with an increasing number of features $p$.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.55]{../02_simulation/021_simulation_figures/ComputationTime_Example.png}
+\caption{Time necessary to compute all three scenarios of the Triple-Gamma-Regularization with $N=100$ and $s=0.1$ dependent on the number of Features $p$}
+\label{fig:ComputationTime}
+\end{figure}
+
+As can be seen from figure \ref{fig:ComputationTime} above, the time to estimates these models increases drastically with an increased number of variables.
+Setting aside that it might even grow exponentially, it can be seen that the computation time also increasingly becomes more unstable.
+Several approaches might help in resolving these issues, like using \textit{Stochastic Gradient Descend (SDG)}, which splits up the training dataset stochastically into smaller batches, \MC or choosing a different estimation algorithm altogether (see section 6.1).
+Another approach could be to implement the underlying estimation in a more efficient programming language when it comes to runtime like C++.
+All in all, this definitely opens up a field for further research to make the overall method more suitable for application.
+
+\begin{landscape}
+\begin{longtable}{ccc|llllllll}
+\caption{Mean and Standard Deviations of MSE on the Validation Set for different Scenarios (25 runs per scenario)} \\
+\toprule
+\makecell{\textbf{Sample} \\ \textbf{Size}} & \makecell{\textbf{Features}} & \makecell{\textbf{Non-zero} \\ \textbf{Features}} & \makecell{\textbf{OLS}} & \makecell{\textbf{LASSO}} & \makecell{\textbf{Ridge}} & \makecell{\textbf{TGR} \\ \textbf{Setting 1}} & \makecell{\textbf{TGR} \\ \textbf{Setting 2}} & \makecell{\textbf{TGR} \\ \textbf{Setting 3}} & \makecell{\textbf{Arctan}} & \makecell{\textbf{Gaussian}} \\
+\midrule
+\endhead
+\midrule \multicolumn{11}{r}{{Continued on next page}} \\
+\endfoot
+
+\bottomrule
+\endlastfoot
+
+\multicolumn{11}{c}{{\tablename\ \thetable{} -- continued from previous page}} \\
+\toprule
+\makecell{\textbf{Sample} \\ \textbf{Size}} & \makecell{\textbf{Features}} & \makecell{\textbf{Non-zero} \\ \textbf{Features}} & \makecell{\textbf{OLS}} & \makecell{\textbf{LASSO}} & \makecell{\textbf{Ridge}} & \makecell{\textbf{TGR} \\ \textbf{Setting 1}} & \makecell{\textbf{TGR} \\ \textbf{Setting 2}} & \makecell{\textbf{TGR} \\ \textbf{Setting 3}} & \makecell{\textbf{Arctan}} & \makecell{\textbf{Gaussian}} \\
+\midrule
+\endfirsthead
+
+\makecell{50} & \makecell{3} & \makecell{1} & \makecell{0,25234 \\(0,16398)} & \makecell{0,2219 \\(0,16634)} & \makecell{0,27945 \\(0,30662)} & \makecell{0,22478 \\(0,15457)} & \makecell{\textcolor{red}{0,21905} \\(0,16378)} & \makecell{0,35557 \\(0,9856)} & \makecell{0,97859 \\(1,75094)} & \makecell{0,93073 \\(1,07439)}\\
+\makecell{50} & \makecell{3} & \makecell{2} & \makecell{0,22655 \\(0,11512)} & \makecell{0,23138 \\(0,11184)} & \makecell{0,39515 \\(0,51324)} & \makecell{0,23436 \\(0,10803)} & \makecell{\textcolor{red}{0,21497} \\(0,11079)} & \makecell{0,47195 \\(0,78161)} & \makecell{1,3962 \\(2,19764)} & \makecell{1,18809 \\(3,67118)}\\
+\makecell{50} & \makecell{3} & \makecell{3} & \makecell{0,20423 \\(0,13742)} & \makecell{0,21708 \\(0,15681)} & \makecell{0,53198 \\(0,60466)} & \makecell{\textcolor{red}{0,19216} \\(0,14344)} & \makecell{0,20721 \\(0,15232)} & \makecell{0,90621 \\(1,94347)} & \makecell{1,92277 \\(5,64658)} & \makecell{2,41364 \\(5,04711)}\\
+\makecell{50} & \makecell{10} & \makecell{1} & \makecell{0,28023 \\(0,17155)} & \makecell{0,22356 \\(0,13548)} & \makecell{0,29245 \\(0,54917)} & \makecell{0,21951 \\(0,14297)} & \makecell{\textcolor{red}{0,2116} \\(0,12048)} & \makecell{0,42564 \\(1,06699)} & \makecell{0,80753 \\(1,6802)} & \makecell{0,82095 \\(2,02455)}\\
+\makecell{50} & \makecell{10} & \makecell{5} & \makecell{0,28965 \\(0,1554)} & \makecell{0,28843 \\(0,15598)} & \makecell{0,93375 \\(0,7604)} & \makecell{\textcolor{red}{0,26844} \\(0,11256)} & \makecell{0,28782 \\(0,13445)} & \makecell{2,89328 \\(2,27582)} & \makecell{4,5195 \\(5,73895)} & \makecell{4,47004 \\(4,20082)} \\
+\makecell{50} & \makecell{10} & \makecell{9} & \makecell{\textcolor{red}{0,30136} \\(0,1306)} & \makecell{0,37676 \\(0,14906)} & \makecell{2,00818 \\(1,17919)} & \makecell{0,33526 \\(0,1349)} & \makecell{0,35175 \\(0,16711)} & \makecell{5,72024 \\(3,36261)} & \makecell{10,64451 \\(5,36156)} & \makecell{10,72909 \\(5,46578)}\\
+\makecell{50} & \makecell{25} & \makecell{3} & \makecell{0,51829 \\(0,36764)} & \makecell{0,36501 \\(0,21862)} & \makecell{0,62776 \\(0,65178)} & \makecell{0,3955 \\(0,29328)} & \makecell{\textcolor{red}{0,30886} \\(0,22148)} & \makecell{1,46023 \\(1,78356)} & \makecell{1,77643 \\(2,71921)} & \makecell{1,88994 \\(2,21)}\\
+\makecell{50} & \makecell{25} & \makecell{13} & \makecell{0,67486 \\(0,35518)} & \makecell{\textcolor{red}{0,54569} \\(0,36132)} & \makecell{2,9942 \\(2,02239)} & \makecell{0,91695 \\(0,77358)} & \makecell{0,80402 \\(0,50006)} & \makecell{9,23039 \\(5,06033)} & \makecell{11,46166 \\(6,86366)} & \makecell{12,24814 \\(6,86801)}\\
+\makecell{50} & \makecell{25} & \makecell{23} & \makecell{\textcolor{red}{0,77777} \\(0,47943)} & \makecell{1,31854 \\(0,74119)} & \makecell{4,98093 \\(3,66703)} & \makecell{2,14074 \\(1,62387)} & \makecell{2,11424 \\(1,4291)} & \makecell{14,84778 \\(9,21278)} & \makecell{21,84308 \\(11,33141)} & \makecell{21,33126 \\(12,44137)}\\
+\makecell{100} & \makecell{3} & \makecell{1} & \makecell{0,26113 \\(0,06292)} & \makecell{0,24148 \\(0,05724)} & \makecell{0,28637 \\(0,1803)} & \makecell{0,24006 \\(0,06026)} & \makecell{\textcolor{red}{0,23919} \\(0,06046)} & \makecell{0,33325 \\(0,35087)} & \makecell{0,80169 \\(1,85348)} & \makecell{0,62443 \\(1,84042)}\\
+\makecell{100} & \makecell{3} & \makecell{2} & \makecell{0,23982 \\(0,06316)} & \makecell{0,23845 \\(0,06489)} & \makecell{0,41608 \\(0,15747)} & \makecell{\textcolor{red}{0,2366} \\(0,06092)} & \makecell{0,24922 \\(0,06462)} & \makecell{0,53486 \\(0,6425)} & \makecell{1,56864 \\(1,05884)} & \makecell{1,62051 \\(1,20262)}\\
+\makecell{100} & \makecell{3} & \makecell{3} & \makecell{0,29648 \\(0,09054)} & \makecell{\textcolor{red}{0,27556} \\(0,08227)} & \makecell{0,44406 \\(0,48781)} & \makecell{0,27967 \\(0,08737)} & \makecell{0,29763 \\(0,08619)} & \makecell{0,81765 \\(1,02153)} & \makecell{2,19614 \\(3,74058)} & \makecell{1,87073 \\(3,38036)}\\
+\makecell{100} & \makecell{10} & \makecell{1} & \makecell{0,2734 \\(0,07944)} & \makecell{0,26898 \\(0,08039)} & \makecell{0,40486 \\(0,13091)} & \makecell{\textcolor{red}{0,26611} \\(0,07539)} & \makecell{0,26677 \\(0,07919)} & \makecell{0,55277 \\(0,78647)} & \makecell{1,05805 \\(0,81199)} & \makecell{1,13716 \\(0,95467)}\\
+\makecell{100} & \makecell{10} & \makecell{5} & \makecell{0,26237 \\(0,09054)} & \makecell{0,251 \\(0,09586)} & \makecell{1,06942 \\(0,5515)} & \makecell{\textcolor{red}{0,243} \\(0,08831)} & \makecell{0,25305 \\(0,0991)} & \makecell{2,7111 \\(1,97029)} & \makecell{5,93076 \\(3,65107)} & \makecell{5,18044 \\(3,10735)}\\
+\makecell{100} & \makecell{10} & \makecell{9} & \makecell{\textcolor{red}{0,25386} \\(0,10201)} & \makecell{0,32494 \\(0,12919)} & \makecell{1,72644 \\(0,9834)} & \makecell{0,2797 \\(0,1147)} & \makecell{0,30738 \\(0,11993)} & \makecell{5,6015 \\(4,00655)} & \makecell{9,87634 \\(5,05172)} & \makecell{9,13047 \\(5,53228)}\\
+\makecell{100} & \makecell{25} & \makecell{3} & \makecell{0,35328 \\(0,113)} & \makecell{0,2858 \\(0,07274)} & \makecell{0,87797 \\(0,56232)} & \makecell{0,28449 \\(0,07773)} & \makecell{\textcolor{red}{0,25255} \\(0,0729)} & \makecell{2,90378 \\(1,76077)} & \makecell{3,90851 \\(2,74017)} & \makecell{3,94007 \\(2,62225)}\\
+\makecell{100} & \makecell{25} & \makecell{13} & \makecell{0,39073 \\(0,1303)} & \makecell{0,43176 \\(0,12362)} & \makecell{2,56021 \\(1,25941)} & \makecell{0,5217 \\(0,31652)} & \makecell{\textcolor{red}{0,35142} \\(0,1927)} & \makecell{8,24937 \\(4,35583)} & \makecell{11,40495 \\(5,75347)} & \makecell{10,7303 \\(5,60251)}\\
+\makecell{100} & \makecell{25} & \makecell{23} & \makecell{\textcolor{red}{0,34696} \\(0,1123)} & \makecell{0,55041 \\(0,18314)} & \makecell{4,83633 \\(2,02043)} & \makecell{1,02786 \\(0,97606)} & \makecell{0,97566 \\(0,9903)} & \makecell{20,17376 \\(7,27886)} & \makecell{25,35184 \\(10,40436)} & \makecell{24,57685 \\(10,40762)}\\
+\makecell{500} & \makecell{3} & \makecell{1} & \makecell{\textcolor{red}{0,25492} \\(0,03172)} & \makecell{0,25986 \\(0,03346)} & \makecell{0,34586 \\(0,39479)} & \makecell{0,25577 \\(0,03298)} & \makecell{0,2552 \\(0,0348)} & \makecell{0,39464 \\(0,80202)} & \makecell{0,9333 \\(2,63126)} & \makecell{1,14691 \\(2,72861)}\\
+\makecell{500} & \makecell{3} & \makecell{2} & \makecell{\textcolor{red}{0,26374} \\(0,0221)} & \makecell{0,26873 \\(0,02096)} & \makecell{0,54005 \\(0,23233)} & \makecell{0,26467 \\(0,02099)} & \makecell{0,2691 \\(0,02182)} & \makecell{0,75057 \\(1,08099)} & \makecell{2,1697 \\(1,72071)} & \makecell{2,26932 \\(2,01686)}\\
+\makecell{500} & \makecell{3} & \makecell{3} & \makecell{\textcolor{red}{0,26158} \\(0,04296)} & \makecell{0,27067 \\(0,04119)} & \makecell{0,61755 \\(0,27379)} & \makecell{0,26586 \\(0,04229)} & \makecell{0,26434 \\(0,03968)} & \makecell{1,05504 \\(0,79724)} & \makecell{2,96089 \\(2,38658)} & \makecell{3,16231 \\(2,07472)}\\
+\makecell{500} & \makecell{10} & \makecell{1} & \makecell{0,24745 \\(0,04425)} & \makecell{0,25079 \\(0,03818)} & \makecell{0,33238 \\(0,1129)} & \makecell{\textcolor{red}{0,244} \\(0,03922)} & \makecell{0,2541 \\(0,03966)} & \makecell{0,64 \\(0,43651)} & \makecell{1,06196 \\(0,93851)} & \makecell{1,20499 \\(1,01908)}\\
+\makecell{500} & \makecell{10} & \makecell{5} & \makecell{\textcolor{red}{0,24921} \\(0,04205)} & \makecell{0,26579 \\(0,04301)} & \makecell{0,81008 \\(0,57001)} & \makecell{0,25288 \\(0,04222)} & \makecell{0,26072 \\(0,03949)} & \makecell{2,6974 \\(2,56921)} & \makecell{3,61381 \\(4,61234)} & \makecell{3,85227 \\(4,56494)}\\
+\makecell{500} & \makecell{10} & \makecell{9} & \makecell{\textcolor{red}{0,24397} \\(0,03147)} & \makecell{0,28519 \\(0,043)} & \makecell{1,44095 \\(0,7961)} & \makecell{0,25363 \\(0,07933)} & \makecell{0,28111 \\(0,10408)} & \makecell{5,84618 \\(3,07682)} & \makecell{8,56159 \\(6,16018)} & \makecell{9,97515 \\(5,99551)}\\
+\makecell{500} & \makecell{25} & \makecell{3} & \makecell{0,26085 \\(0,03684)} & \makecell{0,25511 \\(0,03815)} & \makecell{0,57272 \\(0,29767)} & \makecell{\textcolor{red}{0,2472} \\(0,03757)} & \makecell{0,24907 \\(0,04021)} & \makecell{2,09905 \\(1,77082)} & \makecell{2,7201 \\(2,04823)} & \makecell{2,72876 \\(2,27602)}\\
+\makecell{500} & \makecell{25} & \makecell{13} & \makecell{\textcolor{red}{0,27144} \\(0,02889)} & \makecell{0,32268 \\(0,04375)} & \makecell{1,86148 \\(0,69901)} & \makecell{0,29349 \\(0,11735)} & \makecell{0,30065 \\(0,05267)} & \makecell{9,38381 \\(3,4034)} & \makecell{12,09481 \\(4,82712)} & \makecell{12,38708 \\(4,64426)}\\
+\makecell{500} & \makecell{25} & \makecell{23} & \makecell{\textcolor{red}{0,2755} \\(0,03552)} & \makecell{0,39447 \\(0,06411)} & \makecell{3,1937 \\(1,276)} & \makecell{0,41115 \\(1,11575)} & \makecell{0,45642 \\(1,0544)} & \makecell{16,75672 \\(6,37604)} & \makecell{21,00113 \\(9,35346)} & \makecell{20,08944 \\(9,5086)}\\
+\makecell{1000} & \makecell{3} & \makecell{1} & \makecell{\textcolor{red}{0,25053} \\(0,02649)} & \makecell{0,25757 \\(0,0281)} & \makecell{0,34022 \\(0,20817)} & \makecell{0,25349 \\(0,02671)} & \makecell{0,25861 \\(0,02731)} & \makecell{0,41004 \\(0,69077)} & \makecell{1,07548 \\(1,89567)} & \makecell{1,1043 \\(1,5998)}\\
+\makecell{1000} & \makecell{3} & \makecell{2} & \makecell{0,25114 \\(0,02077)} & \makecell{0,25515 \\(0,02314)} & \makecell{0,46823 \\(0,17607)} & \makecell{\textcolor{red}{0,24898} \\(0,02115)} & \makecell{0,24944 \\(0,02262)} & \makecell{1,07539 \\(0,93913)} & \makecell{2,16733 \\(1,47574)} & \makecell{1,7779 \\(1,61607)}\\
+\makecell{1000} & \makecell{3} & \makecell{3} & \makecell{0,25034 \\(0,0289)} & \makecell{0,25653 \\(0,031)} & \makecell{0,53652 \\(0,28536)} & \makecell{0,25239 \\(0,02764)} & \makecell{\textcolor{red}{0,24992} \\(0,02859)} & \makecell{0,78222 \\(0,9846)} & \makecell{3,06023 \\(1,5519)} & \makecell{2,33984 \\(2,22089)}\\
+\makecell{1000} & \makecell{10} & \makecell{1} & \makecell{0,25044 \\(0,01971)} & \makecell{0,25084 \\(0,02246)} & \makecell{0,33524 \\(0,27203)} & \makecell{0,25095 \\(0,02019)} & \makecell{\textcolor{red}{0,24915} \\(0,02237)} & \makecell{0,7077 \\(1,02835)} & \makecell{1,27558 \\(1,87087)} & \makecell{1,51029 \\(1,54743)}\\
+\makecell{1000} & \makecell{10} & \makecell{5} & \makecell{\textcolor{red}{0,24012} \\(0,02191)} & \makecell{0,26252 \\(0,02371)} & \makecell{0,68128 \\(0,39154)} & \makecell{0,24393 \\(0,02244)} & \makecell{0,25507 \\(0,02319)} & \makecell{2,60964 \\(1,90423)} & \makecell{4,16242 \\(3,10798)} & \makecell{4,29199 \\(2,78838)}\\
+\makecell{1000} & \makecell{10} & \makecell{9} & \makecell{\textcolor{red}{0,2563} \\(0,02596)} & \makecell{0,28626 \\(0,02975)} & \makecell{1,32663 \\(0,38829)} & \makecell{0,25664 \\(0,02786)} & \makecell{0,26883 \\(0,03265)} & \makecell{4,90589 \\(1,77821)} & \makecell{8,38851 \\(3,19513)} & \makecell{8,28297 \\(3,29618)}\\
+\makecell{1000} & \makecell{25} & \makecell{3} & \makecell{0,25279 \\(0,02674)} & \makecell{0,25831 \\(0,02874)} & \makecell{0,78625 \\(0,34754)} & \makecell{0,26149 \\(0,03574)} & \makecell{\textcolor{red}{0,25134} \\(0,02827)} & \makecell{3,05865 \\(1,72991)} & \makecell{3,65552 \\(2,50772)} & \makecell{3,84833 \\(2,32238)}\\
+\makecell{1000} & \makecell{25} & \makecell{13} & \makecell{\textcolor{red}{0,2587} \\(0,02206)} & \makecell{0,31177 \\(0,03114)} & \makecell{2,03451 \\(0,70594)} & \makecell{0,30109 \\(0,07099)} & \makecell{0,28809 \\(0,02876)} & \makecell{9,19749 \\(3,68473)} & \makecell{12,10087 \\(5,07376)} & \makecell{12,51176 \\(5,42773)}\\
+\makecell{1000} & \makecell{25} & \makecell{23} & \makecell{\textcolor{red}{0,26145} \\(0,02966)} & \makecell{0,35083 \\(0,03516)} & \makecell{3,77492 \\(1,0891)} & \makecell{0,41261 \\(0,36625)} & \makecell{0,4022 \\(0,33202)} & \makecell{19,54978 \\(5,65596)} & \makecell{26,04359 \\(6,87056)} & \makecell{25,08614 \\(7,12848)}\\
+\bottomrule
+\label{tab:PredSim}
+\end{longtable}
+\end{landscape}
+
+%\subsection{Simulation Study for Variable Selection}
+
+%As described in the introductory part of this section, the variable selection part of the simulation study will explore how accurately specific models can estimate the underlying data generating process without worrying about predictive power on a test dataset.
+Thus, no validation set will be used to measure performance, but rather the deviation of the estimated coefficients to the true data generating coefficients.
+To showcase this overall procedure, the scenario
 
 \subsection{Implementation as Python Package}
+As mentioned before, this simulation study has been run using Python (Version 3.11.4) along with scikit-learn (Version 1.4.1.post1) and PyTorch (Version 2.2.2).
+The accompanying code, a list of packages used and its version and other material can be found on \href{https://github.com/therealLucasPaul/MScThesis_Econ}{GitHub}.
+The script \textit{tgr.py} can be used as a script to apply \textit{Triple-Gamma-Regularization} on a dataset of choice.
+To make its application easier, the following subsections provides important information on how to use it.
 
-This section provides a brief overview of the Python script, which has been used to run the simulations of the previous section, along with input/output descriptions of the defined functions.
-\begin{lightbluebox}
-How to use it. 
-Explanation of Functions. Input - Output Tables
-\end{lightbluebox}
+\subsubsection*{General Functions}
 
-\subsection{Computational Performance}
-Talking about Gradient Descent Methods in more depth. Why Gradient Clipping. Maybe more modern estimation techniques?
+\begin{longtable}{|p{4cm}|p{9cm}|}
+\hline
+\textbf{Function Name} & \textbf{Description} \\
+\hline
+\endfirsthead
 
-See how computation times change when increasing the size of the data set or when the number of parameter changes. => Use Stochastic Gradient Descent (SGD)
+\hline
+\textbf{Function Name} & \textbf{Description} \\
+\hline
+\endhead
 
-\begin{lightbluebox}
-Kurzes Ansprechen von Computations Efficieny
-\end{lightbluebox}
+\hline
+\endfoot
+
+\hline
+\endlastfoot
+
+\makecell{\texttt{TripleGamma-}\\\texttt{Regularization}} & Here a class is defining a simple neural network.
+It uses the \texttt{nn.Module} and initializes a linear model with 10 input features and 1 output feature without an intercept.
+\\
+\hline
+	\texttt{TripleGammaReg\_Loss} & This function computes the loss for the Triple Gamma Regularization.
+It takes the predicted values (\texttt{Y\_HAT}), the true values (\texttt{Y}), the coefficients of the model (\texttt{coefficients}), the regularization parameter (\texttt{lamda}), and the regularization parameters \texttt{a}, \texttt{c} and \texttt{kappa} as input.
+The loss is computed according to the theoretical formulation by using the script \texttt{log\_hyperu.py}, which approximates the log of the confluent hyper-geometric function of the second kind.
+\\
+\hline
+\texttt{TripleGammaModel} & This function trains the \textit{Triple-Gamma} Regularization model.
+It takes the feature matrix (\texttt{X}), the target values (\texttt{y}), the regularization parameter (\texttt{penalty}), regularization hyper-parameters \texttt{a}, \texttt{c}, \texttt{kappa}, the number of epochs (\texttt{num\_epochs}), and the learning rate (\texttt{lr}) as input.
+It initializes the \texttt{PyTorch} model and optimizer, uses Gradient Descent to train the model for the specified number of epochs, and returns the trained model, a list of model coefficients for each epoch, and a list of loss values for each epoch.\\
+\hline
+\end{longtable}
+
+\subsubsection*{Dependencies}
+To successfully run the script, the following dependencies are required:
+\begin{itemize}
+    \item \texttt{torch}: PyTorch library including sub modules \texttt{torch.nn} and \texttt{torch.optim} for building and training neural networks with at least version 2.2.2
+    \item \texttt{log\_hyperu as hyperu}: The custom module for computing the logarithm of the hypergeometric function, which can be found on GitHub.
+\end{itemize}
+
+\subsubsection*{Data Types of Inputs and Outputs of the Functions}
+\begin{itemize}
+  	\item \texttt{TripleGammaModel}
+    \begin{itemize}
+        \item \textbf{Input:} \texttt{X} (Tensor), \texttt{y} (Tensor), \texttt{penalty} (float), \texttt{a} (float), \texttt{c} (float), \texttt{kappa} (float), \texttt{num\_epochs} (int, default=1000), \texttt{lr} (float, default=0.01)
+        \item \textbf{Output:} \texttt{model} (Initialization of the class TripleGammaRegularization), \texttt{coef\_list} (list of Tensors), \texttt{loss\_list} (list of Tensors)
+    \end{itemize}
+\end{itemize}
 
@@
 \begin{lightbluebox}
-Interessante unifying properties, aber langsam implementiert. 
+I will write the last two paragraphs as soon as the rest of the thesis is 100\% air tight to avoid having to rewrite the conclusions multiple times. It should take long though.
 \end{lightbluebox}
 \section{Conclusion}
-\subsection{Implementation as Python Package}
 \begin{lightbluebox}
@@
 \clearpage
-\appendix
 \end{document}

### 2024-08-08 02_simulation/log_hyperu.py

@@ -84,7 +84,7 @@ class log_hyperu_shift(torch.autograd.Function):
     def forward(ctx, a, b, x):
 
         u_res = robust_hyperu(a, b, x)
-        result = torch.log(u_res+1)
+        result = torch.log(u_res)
 
         ctx.mark_non_differentiable(a)
         ctx.mark_non_differentiable(b)

### 2024-08-08 02_simulation/log_hyperu_conv.py

@@ -1,0 +1,86 @@
+import torch
+import numpy as np
+import scipy.special as sp
+
+"""This script is implementing the alternative, convergin version of the log-hyperu penalty."""
+"""Unfortunately, it appears that not all approximations of the hyperu function as x -> 0 
+are implemented in the scipy library. As such, this is an implementation of those 
+appearing in the DLMF (https://dlmf.nist.gov/13.2#iii).
+a, b, and z are all tensors of the same shape. The function returns a tensor of the same shape.
+"""
+def robust_hyperu_conv(a, b, z):
+    res = torch.zeros_like(z)
+    res.fill_(np.nan)
+    small_z = torch.abs(z) < 1e-9
+
+    # Approximation for small z and b > 2
+    res = torch.where(torch.logical_and(small_z, b > 2), 
+                        torch.exp(torch.lgamma(b - 1) - torch.lgamma(a) + (1 - b) * torch.log(z)),
+                        res)
+
+    # Approximation for small z and b = 2
+    res = torch.where(torch.logical_and(small_z, b == 2),
+                        torch.exp(-torch.lgamma(a) - torch.log(z)),
+                        res)
+
+    # Approximation for small z and 1 < b < 2
+    res = torch.where(torch.logical_and(torch.logical_and(small_z, b < 2), b > 1),
+                        torch.exp(torch.lgamma(b - 1) - torch.lgamma(a) + (1 - b) * torch.log(z)) +
+                        torch.exp(-torch.lgamma(1 - b) - torch.lgamma(a - b +1)),
+                        res)
+
+    # Approximation for small z and b = 1
+    res = torch.where(torch.logical_and(small_z, b == 1),
+                        -torch.exp(-torch.lgamma(a) - torch.log(z + torch.digamma(a) + 0.57721566490153286060651209008240243)),
+                        res)
+
+    # Approximation for small z and 0 < b < 1
+    res = torch.where(torch.logical_and(torch.logical_and(small_z, b < 1), b > 0),
+                        torch.exp(torch.lgamma(1 - b) - torch.lgamma(a - b + 1)),
+                        res)
+
+    # Approximation for small z and b = 0
+    res = torch.where(torch.logical_and(small_z, b == 0),
+                        torch.exp(-torch.lgamma(a + 1)),
+                        res)
+
+    # Approximation for small z and b < 0
+    res = torch.where(torch.logical_and(small_z, b < 0),
[…]

### 2024-08-08 06_general_code/log_hyperu.py

@@ -84,7 +84,7 @@ class log_hyperu_shift(torch.autograd.Function):
     def forward(ctx, a, b, x):
 
         u_res = robust_hyperu(a, b, x)
-        result = torch.log(u_res) # TODO: Add +1 for shift version
+        result = torch.log(u_res)
 
         ctx.mark_non_differentiable(a)
         ctx.mark_non_differentiable(b)

### 2024-09-06 01_latex/MScThesis_Econ.tex
New Code - Final Simulation

@@
 
-\begin{lightbluebox}
-- BIAS VARIANCE TRADE-OFF
-- DIMENSIONALITY PROBLEM
-
-General problem: Fit vs. Complexity. What to choose and where is the optimal balance?
-\end{lightbluebox}
+In supervised learning, a model is fitted on an observed dataset where both inputs and outputs are given in pairs.
+Using this data a statistical model aims to find a functional form which maps these inputs into the output space and thus describes a relationship between those two spaces.
+Naturally, one would assume to find a functional form which manages to describe the relationship as closely as possible by minimizing a chosen loss function.
+Yet, this often ignores a problem called "overfitting" which can loosely be described as using "too much information" from the training dataset.
+As described by \textcite{Ying2019}, this problem arises from the fact "that over-fitted model has difficulty coping with pieces of the information in the testing set, which may be different from those in the training set".
+A more formal definition of overfitting has been defined by \textcite{Mitchell1997}:\\
+
+\textbf{Definition 2:}Given a hypothesis space $\mathcal{H}$, a hypothesis $h \in \mathcal{H}$ is said to overfit the training data if there exists some alternative hypothesis $h' \in \mathcal{H}$ such that $h$ has smaller error than $h'$ over the training examples, but $h'$ has a smaller error than $h$ over the entire distribution of instances.\\
+
+Theoretically, this problem can emerge from a multitude of reasons.
+One of which being that learning every piece of information in the training dataset can lead to fitting the noise rather than fitting the underlying pattern.
+Another reason can be ill-chosen degrees of model complexity, because "having many hypotheses intuitively increase the risk of randomly finding a solution that learn the training set “by heart”, with limited generalization ability." \parencite{ParisRobilliardFonlupt2003}.\\
 
@@
 
-\textbf{Defintion 1. Regularization} is any supplementary technique that aims at making the model generalize better, i.e. produce better results on the test set.\\
+\textbf{Defintion 2: Regularization} is any supplementary technique that aims at making the model generalize better, i.e. produce better results on the test set.\\
 
@@
 Variable & Values\\\midrule
-Sample Size $N$ & $50, 100, 500, 1000$\\
-Dimensionality $p$ & $3, 10, 25$\\
+Sample Size $N$ & $10, 100, 250$\\
+Dimensionality $p$ & $10, 50, 200$\\
 Sparsity $s$ & $0.1, 0.5, 0.9$\\\bottomrule
@@
 
-\subsection{Simulation Study for Prediction}
+\subsection{Simulation Study}
 
 For the simulation study testing the models prediction accuracy the key metric to test performance will be the \textit{mean-squared-error (MSE)}.
-The data is being generated the following way: Given a set of scenario parameters $N_i$, $p_i$ and $s_i$, the first $s_i*p_i$ coefficients, rounded to the next larger integer, will be generated from a normal distribution with mean $0$ and variance $1$, the remaining coefficients will be set to zero.
+The data is being generated the following way: Given a set of scenario parameters $N_i$, $p_i$ and $sd_i$, the first $s_i*p_i$ coefficients, rounded to the next larger integer, will be set to $3$ and the remaining will be set to $0$.
 Then, $N_i$ draws will be generated from a normal distribution with mean $0$ and variance $1$ for each of the $p_i$ features.
-Using these coefficients and the data from the features a response variable $y$ will be computed and noise drawn from a normal distribution with mean $0$ and variance $1$ multiplied with $0.5$ will be added as noise.
-First, the grid search for the optimal $\lambda$ will be performed by generating a sample dataset using the above generating process.
-Then, every method that is part of the simulation will be estimated on the dataset for every $\lambda_i$ in the set $\lambda_i \in \{0, 0.01, 0.02, \cdots, 1\}$.
-For every method separately, the $\lambda_i$ which generates the lowest validation loss on the testset will be used for the overall simulation.\\
-
-Using the set of scenario variables mentioned in table \ref{tab:Scenarios}, all possible combinations will be formed resulting in the overall $36$ scenarios.
-The code iterates through the list of scenarios, generates 25 datasets based on these scenarios variables and all tested methods will be estimated on every one the test part of these datasets.
+Using these coefficients and the data from the features a response variable $y$ will be computed and noise generated from a normal distribution with mean $0$ and variance $\sigma_i$.
+According to \textcite{WangEtAl2020}, the respective $\sigma_i$ will be computed based on the \textit{Signal-To-Noise Ration (SNR)}.
+The \textit{SNR} is given by $SNR = \sqrt{\beta^TX^TX\beta/(N_i\sigma_i^2)}$ and by setting the \textit{SNR} to a specific value, one can adjust how string the noise in the data is relative to the sound of the actual data generating process.
+For the purpose of this study, and similar to \textcite{WangEtAl2020}, a \textit{SNR} equal to one will be used.
+In terms of the regularization parameter $\lambda$, the search for the optimal $\lambda$ will be performed by using five-fold-cross-validation on the a set of possible $\lambda$ values.
+For every method and every run in every scenario separately, the optimal $\lambda^*_i$ will be chosen which generates the lowest validation loss on the testset.
+This grid-serach procedure will be performed for every $\lambda_i \in \{0.001, 0.01, 0.1, 0.25, 0.4, 0.5, 0.6, 0.75, 0.9, 0.95\}$.\\
+
+Using the set of scenario variables mentioned in table \ref{tab:Scenarios}, all possible combinations will be formed resulting in the overall $27$ scenarios.
+The code iterates through the list of scenarios, generates 15 datasets based on these scenarios variables and all tested methods will be estimated on every one the test part of these datasets.
 Afterwards, the validation loss will be computed for each method and stored.
-This procedure results in tables \ref{tab:PredSim}, which shows the mean and standard deviation of the distribution of the validation loss for every scenario and every methods.
+This procedure results in tables \ref{tab:PredSim}, which shows the mean and standard deviation of the distribution of the validation loss for every scenario and every method.
 The values colored in \textcolor{red}{red} indicate the smallest means for every scenario.
-Before advancing to the overall results of this simulation study, it might be useful to have a look at a specific scenario to better understand the results in table \ref{tab:PredSim}, which will be the scenario with $N=100, p=25, s=0.1$.\\
-
-In this scenario, we are dealing with a dataset of $100$ observations, $25$ features and $3$ non-zero coefficients.\footnote{$25 \times 0.1 = 2.5$ and $ceil(2.5)=3$.} A figure with boxplots showcasing the distributions of the Mean-Squared-Error rates on the validation set for all methods can be found in figure \ref{fig:SpecificScenario}
+Before advancing to the overall results of this simulation study, it might be useful to have a look at a specific scenario to better understand the results in table \ref{tab:PredSim}, which will be the scenario with $N=100, p=200, s=0.1$.\\
+
+In this scenario, we are dealing with a dataset of $100$ observations, $200$ features and $20$ non-zero coefficients.\footnote{$200 \times 0.1 = 20$.} A figure with boxplots showcasing the distributions of the Mean-Squared-Error rates on the validation set for all methods can be found in figure \ref{fig:SpecificScenario}.
 
@@
 \centering
-\includegraphics[scale=0.55]{../02_simulation/021_simulation_figures/Scenarion_100_25_3.png}
+\includegraphics[scale=0.5]{../02_simulation/021_simulation_figures/Scenarion_100_200_20.png}
 \caption{Distribution of MSE on Validation Set in the Scenario with $100$ Observations, $25$ Features and $3$ non-zero Coefficients}
@@
 has an effect on the outcome.
-Here, \textit{LASSO} performs well which was to be expected, but it can also be seen that the first and second setting of the \textit{Triple-Gamma} Penalty can both produce similar results when it comes to predictive power.
-\textit{Setting 2} even has a lower mean in MSE ($0.25255$) than \textit{LASSO} regression ($0.2858$).
-\textit{OLS} manages to perform quite well, yet has a visible shift towards higher \textit{MSE} values.
-\textit{Arctan, Gaussian} and the third setting of the \textit{Triple-Gamma} penalty perform significantly worse in this scenario.\\
-
-Generally, it can be seen table \ref{tab:Scenarios} that the larger the sample size gets, the better OLS performs on the dataset as enough data is present for the OLS regression to work properly.
-However, in sparse data settings as well as when the sample size is low, regularization approaches regularly outperform the OLS method, which aligns with theory.
-Essentially, \textit{LASSO} and the \textit{first} and \textit{second} setting of the \textit{Triple-Gamma} penalty outperform most other methods in these scenarios.
-Especially, the two models estimated with these two settings of the \textit{Triple-Gamma} approach manage to work best in these scenarios in most cases, highlighting the potential benefit that the \textit{Triple-Gamma} regularization might have in these scenarios.\\
+Here, \textit{Ridge} performs best by far in manages to produce the smallest mean in loss with about $300$.
+Except for \textit{Gaussian}, every method produces a right-skewed distribution indicating that most methods produce average losses of around $400$ most of the time with common outliers up to $750$.
+
+An overview of the results for each of the $27$ scenarios can be found in table \ref{tab:bestmethod}.
+In the left half of the table the scenario parameters are presented and in the right half the best method based on the method having the lowest mean as well as median validation loss.
+In general, the results confirm the results from \textcite{WangEtAl2020} that no go-to method in regularization have been found.
+In terms of the mean loss, \textit{LASSO}, \textit{Ridge}, \textit{Gaussian} and \textit{Arctan} have managed to perform best in one or more scenarios.
+When it comes to the median, \textit{LASSO}, \textit{Setting 1 and 2 of the TGR}, \textit{Ridge}, \textit{Arctan} and \textit{Gaussian} have managed to perform best in one or more scenarios.
+Clearly, no one single method stands out as an overall winner in this simulation.
+However, these results have to be taken with care as will be discussed in section \ref{sec:crit} later on.
 
@@
 \end{lightbluebox}
+
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{ccc|l|l}
+\toprule
+\multicolumn{3}{c}{Scenario Parameters} & \multicolumn{2}{c}{Moment}\\
+\midrule
+Samples & Features & Non-Zero Features & Best Method (Mean) & Best Method (Median) \\
+\midrule
+10 & 10 & 1 & LASSO & LASSO \\
+10 & 10 & 5 & Ridge & TGR Setting 1 \\
+10 & 10 & 9 & Ridge & Ridge \\
+10 & 50 & 5 & Ridge & Ridge \\
+10 & 50 & 25 & Gaussian & Gaussian \\
+10 & 50 & 45 & Ridge & Ridge \\
+10 & 200 & 20 & Gaussian & Arctan \\
+10 & 200 & 100 & Arctan & LASSO \\
+10 & 200 & 180 & Gaussian & Gaussian \\
+100 & 10 & 1 & Arctan & Arctan \\
+100 & 10 & 5 & Gaussian & Gaussian \\
+100 & 10 & 9 & Gaussian & Ridge \\
+100 & 50 & 5 & Gaussian & Gaussian \\
+100 & 50 & 25 & Ridge & Ridge \\
+100 & 50 & 45 & Ridge & Ridge \\
+100 & 200 & 20 & Ridge & Ridge \\
+100 & 200 & 100 & Gaussian & Ridge \\
+100 & 200 & 180 & Ridge & Ridge \\
+250 & 10 & 1 & Gaussian & Gaussian \\
+250 & 10 & 5 & Gaussian & Gaussian \\
+250 & 10 & 9 & Gaussian & TGR Setting 2 \\
+250 & 50 & 5 & Gaussian & Gaussian \\
+250 & 50 & 25 & Ridge & Ridge \\
+250 & 50 & 45 & Ridge & Ridge \\
+250 & 200 & 20 & Ridge & Ridge \\
+250 & 200 & 100 & Ridge & Ridge \\
+250 & 200 & 180 & Ridge & Ridge \\
+\bottomrule
+\end{tabular}
+\caption{Table showing the best performing methods according to smallest Mean and Median Loss accordingly}
+\end{center}
+\label{tab:bestmethod}
+\end{table}
 
@@
 This is, to no surprise, very inefficient and makes computations in high dimensions unnecessarily complicated.
-In figure \ref{fig:ComputationTime} a plot can be found which shows the time to estimate all three settings of the \textit{Triple-Gamma-Regularization} on a dataset generated with parameters $N=100$ and $s=0.1$ with an increasing number of features $p$.
+In figure \ref{fig:ComputationTime} a plot can be found which shows the time to estimate all three settings of the \textit{Triple-Gamma-Regularization} on a dataset generated with parameters $N=100$ and $s=0.1$ with an increasing number of features $p$.\\
+
+It is also worth noting that the compuational efficiency of the \textit{Triple-Gamma-Penalty} still relies on the specification of the penalty.
+\textit{Setting 2} for example with its very \textit{smooth-at-origin} behaviour takes significantly longer to compute compared to its \textit{singular-at-origin} specifications in \textit{setting 1} and \textit{setting 3}.
 
@@
 Setting aside that it might even grow exponentially, it can be seen that the computation time also increasingly becomes more unstable.
-Several approaches might help in resolving these issues, like using \textit{Stochastic Gradient Descend (SDG)}, which splits up the training dataset stochastically into smaller batches, \MC or choosing a different estimation algorithm altogether (see section 6.1).
+Several approaches might help in resolving these issues, like optimizing the underlying approximation of the confluent hypergeometric funciton or choosing a different estimation algorithm altogether (see section 6.1).
 Another approach could be to implement the underlying estimation in a more efficient programming language when it comes to runtime like C++.
@@
 \begin{landscape}
-\begin{longtable}{ccc|llllllll}
-\caption{Mean and Standard Deviations of MSE on the Validation Set for different Scenarios (25 runs per scenario)} \\
+\begin{longtable}{lllllllllllrrrrrrrr}
+\toprule
+\caption{Mean and Standard Deviations of MSE on the Validation Set for different Scenarios (15 runs per scenario)} \\
 \toprule
@@
 
-\makecell{50} & \makecell{3} & \makecell{1} & \makecell{0,25234 \\(0,16398)} & \makecell{0,2219 \\(0,16634)} & \makecell{0,27945 \\(0,30662)} & \makecell{0,22478 \\(0,15457)} & \makecell{\textcolor{red}{0,21905} \\(0,16378)} & \makecell{0,35557 \\(0,9856)} & \makecell{0,97859 \\(1,75094)} & \makecell{0,93073 \\(1,07439)}\\
-\makecell{50} & \makecell{3} & \makecell{2} & \makecell{0,22655 \\(0,11512)} & \makecell{0,23138 \\(0,11184)} & \makecell{0,39515 \\(0,51324)} & \makecell{0,23436 \\(0,10803)} & \makecell{\textcolor{red}{0,21497} \\(0,11079)} & \makecell{0,47195 \\(0,78161)} & \makecell{1,3962 \\(2,19764)} & \makecell{1,18809 \\(3,67118)}\\
-\makecell{50} & \makecell{3} & \makecell{3} & \makecell{0,20423 \\(0,13742)} & \makecell{0,21708 \\(0,15681)} & \makecell{0,53198 \\(0,60466)} & \makecell{\textcolor{red}{0,19216} \\(0,14344)} & \makecell{0,20721 \\(0,15232)} & \makecell{0,90621 \\(1,94347)} & \makecell{1,92277 \\(5,64658)} & \makecell{2,41364 \\(5,04711)}\\
-\makecell{50} & \makecell{10} & \makecell{1} & \makecell{0,28023 \\(0,17155)} & \makecell{0,22356 \\(0,13548)} & \makecell{0,29245 \\(0,54917)} & \makecell{0,21951 \\(0,14297)} & \makecell{\textcolor{red}{0,2116} \\(0,12048)} & \makecell{0,42564 \\(1,06699)} & \makecell{0,80753 \\(1,6802)} & \makecell{0,82095 \\(2,02455)}\\
-\makecell{50} & \makecell{10} & \makecell{5} & \makecell{0,28965 \\(0,1554)} & \makecell{0,28843 \\(0,15598)} & \makecell{0,93375 \\(0,7604)} & \makecell{\textcolor{red}{0,26844} \\(0,11256)} & \makecell{0,28782 \\(0,13445)} & \makecell{2,89328 \\(2,27582)} & \makecell{4,5195 \\(5,73895)} & \makecell{4,47004 \\(4,20082)} \\
-\makecell{50} & \makecell{10} & \makecell{9} & \makecell{\textcolor{red}{0,30136} \\(0,1306)} & \makecell{0,37676 \\(0,14906)} & \makecell{2,00818 \\(1,17919)} & \makecell{0,33526 \\(0,1349)} & \makecell{0,35175 \\(0,16711)} & \makecell{5,72024 \\(3,36261)} & \makecell{10,64451 \\(5,36156)} & \makecell{10,72909 \\(5,46578)}\\
-\makecell{50} & \makecell{25} & \makecell{3} & \makecell{0,51829 \\(0,36764)} & \makecell{0,36501 \\(0,21862)} & \makecell{0,62776 \\(0,65178)} & \makecell{0,3955 \\(0,29328)} & \makecell{\textcolor{red}{0,30886} \\(0,22148)} & \makecell{1,46023 \\(1,78356)} & \makecell{1,77643 \\(2,71921)} & \makecell{1,88994 \\(2,21)}\\
-\makecell{50} & \makecell{25} & \makecell{13} & \makecell{0,67486 \\(0,35518)} & \makecell{\textcolor{red}{0,54569} \\(0,36132)} & \makecell{2,9942 \\(2,02239)} & \makecell{0,91695 \\(0,77358)} & \makecell{0,80402 \\(0,50006)} & \makecell{9,23039 \\(5,06033)} & \makecell{11,46166 \\(6,86366)} & \makecell{12,24814 \\(6,86801)}\\
-\makecell{50} & \makecell{25} & \makecell{23} & \makecell{\textcolor{red}{0,77777} \\(0,47943)} & \makecell{1,31854 \\(0,74119)} & \makecell{4,98093 \\(3,66703)} & \makecell{2,14074 \\(1,62387)} & \makecell{2,11424 \\(1,4291)} & \makecell{14,84778 \\(9,21278)} & \makecell{21,84308 \\(11,33141)} & \makecell{21,33126 \\(12,44137)}\\
-\makecell{100} & \makecell{3} & \makecell{1} & \makecell{0,26113 \\(0,06292)} & \makecell{0,24148 \\(0,05724)} & \makecell{0,28637 \\(0,1803)} & \makecell{0,24006 \\(0,06026)} & \makecell{\textcolor{red}{0,23919} \\(0,06046)} & \makecell{0,33325 \\(0,35087)} & \makecell{0,80169 \\(1,85348)} & \makecell{0,62443 \\(1,84042)}\\
-\makecell{100} & \makecell{3} & \makecell{2} & \makecell{0,23982 \\(0,06316)} & \makecell{0,23845 \\(0,06489)} & \makecell{0,41608 \\(0,15747)} & \makecell{\textcolor{red}{0,2366} \\(0,06092)} & \makecell{0,24922 \\(0,06462)} & \makecell{0,53486 \\(0,6425)} & \makecell{1,56864 \\(1,05884)} & \makecell{1,62051 \\(1,20262)}\\
-\makecell{100} & \makecell{3} & \makecell{3} & \makecell{0,29648 \\(0,09054)} & \makecell{\textcolor{red}{0,27556} \\(0,08227)} & \makecell{0,44406 \\(0,48781)} & \makecell{0,27967 \\(0,08737)} & \makecell{0,29763 \\(0,08619)} & \makecell{0,81765 \\(1,02153)} & \makecell{2,19614 \\(3,74058)} & \makecell{1,87073 \\(3,38036)}\\
-\makecell{100} & \makecell{10} & \makecell{1} & \makecell{0,2734 \\(0,07944)} & \makecell{0,26898 \\(0,08039)} & \makecell{0,40486 \\(0,13091)} & \makecell{\textcolor{red}{0,26611} \\(0,07539)} & \makecell{0,26677 \\(0,07919)} & \makecell{0,55277 \\(0,78647)} & \makecell{1,05805 \\(0,81199)} & \makecell{1,13716 \\(0,95467)}\\
-\makecell{100} & \makecell{10} & \makecell{5} & \makecell{0,26237 \\(0,09054)} & \makecell{0,251 \\(0,09586)} & \makecell{1,06942 \\(0,5515)} & \makecell{\textcolor{red}{0,243} \\(0,08831)} & \makecell{0,25305 \\(0,0991)} & \makecell{2,7111 \\(1,97029)} & \makecell{5,93076 \\(3,65107)} & \makecell{5,18044 \\(3,10735)}\\
-\makecell{100} & \makecell{10} & \makecell{9} & \makecell{\textcolor{red}{0,25386} \\(0,10201)} & \makecell{0,32494 \\(0,12919)} & \makecell{1,72644 \\(0,9834)} & \makecell{0,2797 \\(0,1147)} & \makecell{0,30738 \\(0,11993)} & \makecell{5,6015 \\(4,00655)} & \makecell{9,87634 \\(5,05172)} & \makecell{9,13047 \\(5,53228)}\\
-\makecell{100} & \makecell{25} & \makecell{3} & \makecell{0,35328 \\(0,113)} & \makecell{0,2858 \\(0,07274)} & \makecell{0,87797 \\(0,56232)} & \makecell{0,28449 \\(0,07773)} & \makecell{\textcolor{red}{0,25255} \\(0,0729)} & \makecell{2,90378 \\(1,76077)} & \makecell{3,90851 \\(2,74017)} & \makecell{3,94007 \\(2,62225)}\\
-\makecell{100} & \makecell{25} & \makecell{13} & \makecell{0,39073 \\(0,1303)} & \makecell{0,43176 \\(0,12362)} & \makecell{2,56021 \\(1,25941)} & \makecell{0,5217 \\(0,31652)} & \makecell{\textcolor{red}{0,35142} \\(0,1927)} & \makecell{8,24937 \\(4,35583)} & \makecell{11,40495 \\(5,75347)} & \makecell{10,7303 \\(5,60251)}\\
-\makecell{100} & \makecell{25} & \makecell{23} & \makecell{\textcolor{red}{0,34696} \\(0,1123)} & \makecell{0,55041 \\(0,18314)} & \makecell{4,83633 \\(2,02043)} & \makecell{1,02786 \\(0,97606)} & \makecell{0,97566 \\(0,9903)} & \makecell{20,17376 \\(7,27886)} & \makecell{25,35184 \\(10,40436)} & \makecell{24,57685 \\(10,40762)}\\
-\makecell{500} & \makecell{3} & \makecell{1} & \makecell{\textcolor{red}{0,25492} \\(0,03172)} & \makecell{0,25986 \\(0,03346)} & \makecell{0,34586 \\(0,39479)} & \makecell{0,25577 \\(0,03298)} & \makecell{0,2552 \\(0,0348)} & \makecell{0,39464 \\(0,80202)} & \makecell{0,9333 \\(2,63126)} & \makecell{1,14691 \\(2,72861)}\\
-\makecell{500} & \makecell{3} & \makecell{2} & \makecell{\textcolor{red}{0,26374} \\(0,0221)} & \makecell{0,26873 \\(0,02096)} & \makecell{0,54005 \\(0,23233)} & \makecell{0,26467 \\(0,02099)} & \makecell{0,2691 \\(0,02182)} & \makecell{0,75057 \\(1,08099)} & \makecell{2,1697 \\(1,72071)} & \makecell{2,26932 \\(2,01686)}\\
-\makecell{500} & \makecell{3} & \makecell{3} & \makecell{\textcolor{red}{0,26158} \\(0,04296)} & \makecell{0,27067 \\(0,04119)} & \makecell{0,61755 \\(0,27379)} & \makecell{0,26586 \\(0,04229)} & \makecell{0,26434 \\(0,03968)} & \makecell{1,05504 \\(0,79724)} & \makecell{2,96089 \\(2,38658)} & \makecell{3,16231 \\(2,07472)}\\
-\makecell{500} & \makecell{10} & \makecell{1} & \makecell{0,24745 \\(0,04425)} & \makecell{0,25079 \\(0,03818)} & \makecell{0,33238 \\(0,1129)} & \makecell{\textcolor{red}{0,244} \\(0,03922)} & \makecell{0,2541 \\(0,03966)} & \makecell{0,64 \\(0,43651)} & \makecell{1,06196 \\(0,93851)} & \makecell{1,20499 \\(1,01908)}\\
-\makecell{500} & \makecell{10} & \makecell{5} & \makecell{\textcolor{red}{0,24921} \\(0,04205)} & \makecell{0,26579 \\(0,04301)} & \makecell{0,81008 \\(0,57001)} & \makecell{0,25288 \\(0,04222)} & \makecell{0,26072 \\(0,03949)} & \makecell{2,6974 \\(2,56921)} & \makecell{3,61381 \\(4,61234)} & \makecell{3,85227 \\(4,56494)}\\
-\makecell{500} & \makecell{10} & \makecell{9} & \makecell{\textcolor{red}{0,24397} \\(0,03147)} & \makecell{0,28519 \\(0,043)} & \makecell{1,44095 \\(0,7961)} & \makecell{0,25363 \\(0,07933)} & \makecell{0,28111 \\(0,10408)} & \makecell{5,84618 \\(3,07682)} & \makecell{8,56159 \\(6,16018)} & \makecell{9,97515 \\(5,99551)}\\
-\makecell{500} & \makecell{25} & \makecell{3} & \makecell{0,26085 \\(0,03684)} & \makecell{0,25511 \\(0,03815)} & \makecell{0,57272 \\(0,29767)} & \makecell{\textcolor{red}{0,2472} \\(0,03757)} & \makecell{0,24907 \\(0,04021)} & \makecell{2,09905 \\(1,77082)} & \makecell{2,7201 \\(2,04823)} & \makecell{2,72876 \\(2,27602)}\\
-\makecell{500} & \makecell{25} & \makecell{13} & \makecell{\textcolor{red}{0,27144} \\(0,02889)} & \makecell{0,32268 \\(0,04375)} & \makecell{1,86148 \\(0,69901)} & \makecell{0,29349 \\(0,11735)} & \makecell{0,30065 \\(0,05267)} & \makecell{9,38381 \\(3,4034)} & \makecell{12,09481 \\(4,82712)} & \makecell{12,38708 \\(4,64426)}\\
-\makecell{500} & \makecell{25} & \makecell{23} & \makecell{\textcolor{red}{0,2755} \\(0,03552)} & \makecell{0,39447 \\(0,06411)} & \makecell{3,1937 \\(1,276)} & \makecell{0,41115 \\(1,11575)} & \makecell{0,45642 \\(1,0544)} & \makecell{16,75672 \\(6,37604)} & \makecell{21,00113 \\(9,35346)} & \makecell{20,08944 \\(9,5086)}\\
-\makecell{1000} & \makecell{3} & \makecell{1} & \makecell{\textcolor{red}{0,25053} \\(0,02649)} & \makecell{0,25757 \\(0,0281)} & \makecell{0,34022 \\(0,20817)} & \makecell{0,25349 \\(0,02671)} & \makecell{0,25861 \\(0,02731)} & \makecell{0,41004 \\(0,69077)} & \makecell{1,07548 \\(1,89567)} & \makecell{1,1043 \\(1,5998)}\\
-\makecell{1000} & \makecell{3} & \makecell{2} & \makecell{0,25114 \\(0,02077)} & \makecell{0,25515 \\(0,02314)} & \makecell{0,46823 \\(0,17607)} & \makecell{\textcolor{red}{0,24898} \\(0,02115)} & \makecell{0,24944 \\(0,02262)} & \makecell{1,07539 \\(0,93913)} & \makecell{2,16733 \\(1,47574)} & \makecell{1,7779 \\(1,61607)}\\
-\makecell{1000} & \makecell{3} & \makecell{3} & \makecell{0,25034 \\(0,0289)} & \makecell{0,25653 \\(0,031)} & \makecell{0,53652 \\(0,28536)} & \makecell{0,25239 \\(0,02764)} & \makecell{\textcolor{red}{0,24992} \\(0,02859)} & \makecell{0,78222 \\(0,9846)} & \makecell{3,06023 \\(1,5519)} & \makecell{2,33984 \\(2,22089)}\\
-\makecell{1000} & \makecell{10} & \makecell{1} & \makecell{0,25044 \\(0,01971)} & \makecell{0,25084 \\(0,02246)} & \makecell{0,33524 \\(0,27203)} & \makecell{0,25095 \\(0,02019)} & \makecell{\textcolor{red}{0,24915} \\(0,02237)} & \makecell{0,7077 \\(1,02835)} & \makecell{1,27558 \\(1,87087)} & \makecell{1,51029 \\(1,54743)}\\
-\makecell{1000} & \makecell{10} & \makecell{5} & \makecell{\textcolor{red}{0,24012} \\(0,02191)} & \makecell{0,26252 \\(0,02371)} & \makecell{0,68128 \\(0,39154)} & \makecell{0,24393 \\(0,02244)} & \makecell{0,25507 \\(0,02319)} & \makecell{2,60964 \\(1,90423)} & \makecell{4,16242 \\(3,10798)} & \makecell{4,29199 \\(2,78838)}\\
-\makecell{1000} & \makecell{10} & \makecell{9} & \makecell{\textcolor{red}{0,2563} \\(0,02596)} & \makecell{0,28626 \\(0,02975)} & \makecell{1,32663 \\(0,38829)} & \makecell{0,25664 \\(0,02786)} & \makecell{0,26883 \\(0,03265)} & \makecell{4,90589 \\(1,77821)} & \makecell{8,38851 \\(3,19513)} & \makecell{8,28297 \\(3,29618)}\\
-\makecell{1000} & \makecell{25} & \makecell{3} & \makecell{0,25279 \\(0,02674)} & \makecell{0,25831 \\(0,02874)} & \makecell{0,78625 \\(0,34754)} & \makecell{0,26149 \\(0,03574)} & \makecell{\textcolor{red}{0,25134} \\(0,02827)} & \makecell{3,05865 \\(1,72991)} & \makecell{3,65552 \\(2,50772)} & \makecell{3,84833 \\(2,32238)}\\
-\makecell{1000} & \makecell{25} & \makecell{13} & \makecell{\textcolor{red}{0,2587} \\(0,02206)} & \makecell{0,31177 \\(0,03114)} & \makecell{2,03451 \\(0,70594)} & \makecell{0,30109 \\(0,07099)} & \makecell{0,28809 \\(0,02876)} & \makecell{9,19749 \\(3,68473)} & \makecell{12,10087 \\(5,07376)} & \makecell{12,51176 \\(5,42773)}\\
-\makecell{1000} & \makecell{25} & \makecell{23} & \makecell{\textcolor{red}{0,26145} \\(0,02966)} & \makecell{0,35083 \\(0,03516)} & \makecell{3,77492 \\(1,0891)} & \makecell{0,41261 \\(0,36625)} & \makecell{0,4022 \\(0,33202)} & \makecell{19,54978 \\(5,65596)} & \makecell{26,04359 \\(6,87056)} & \makecell{25,08614 \\(7,12848)}\\
+% &  &  &  Arctan &  Gaussian &  LASSO &  OLS &  Ridge &  TGR Setting 1 &  TGR Setting 2 &  TGR Setting 3 & median Arctan & median Gaussian & median LASSO & median OLS & median Ridge & median TGR Setting 1 & median TGR Setting 2 & median TGR Setting 3 \\
+%Samples & Features & Non-Zero Features &  &  &  &  &  &  &  &  &  &  &  &  %&  &  &  &  \\
+\midrule
+\multirow[t]{9}{*}{100} & \multirow[t]{3}{*}{10} & 1 & \makecell{8.143 \\ (2.511)} & \makecell{10.027 \\ (3.428)} & \makecell{8.516 \\ (2.645)} & \makecell{8.761 \\ (2.474)} & \makecell{9.398 \\ (2.78)} & \makecell{8.76 \\ (2.475)} & \makecell{8.76 \\ (2.474)} & \makecell{8.762 \\ (2.475)} \\
+ &  & 5 & \makecell{55.223 \\ (20.503)} & \makecell{50.321 \\ (17.244)} & \makecell{55.148 \\ (19.635)} & \makecell{55.609 \\ (20.961)} & \makecell{56.055 \\ (19.489)} & \makecell{55.609 \\ (20.964)} & \makecell{55.61 \\ (20.962)} & \makecell{55.609 \\ (20.965)}  \\
+ &  & 9 & \makecell{94.411 \\ (20.534)} & \makecell{91.228 \\ (33.291)} & \makecell{94.499 \\ (21.804)} & \makecell{94.328 \\ (20.518)} & \makecell{91.867 \\ (22.567)} & \makecell{94.327 \\ (20.518)} & \makecell{94.323 \\ (20.517)} & \makecell{94.331 \\ (20.516)} \\
+\cline{2-19}
+ & \multirow[t]{3}{*}{200} & 100 & \makecell{2226.539 \\ (739.514)} & \makecell{1827.873 \\ (444.322)} & \makecell{2208.412 \\ (787.768)} & \makecell{2216.253 \\ (723.275)} & \makecell{1830.305 \\ (737.83)} & \makecell{2216.27 \\ (728.55)} & \makecell{2212.339 \\ (723.82)} & \makecell{2219.283 \\ (725.999)}  \\
+ &  & 180 & \makecell{3646.99 \\ (772.852)} & \makecell{3715.863 \\ (938.21)} & \makecell{3636.415 \\ (839.114)} & \makecell{3599.837 \\ (815.794)} & \makecell{2946.407 \\ (597.781)} & \makecell{3606.205 \\ (814.385)} & \makecell{3601.481 \\ (818.954)} & \makecell{3597.845 \\ (812.657)}  \\
+ &  & 20 & \makecell{445.823 \\ (159.82)} & \makecell{416.379 \\ (171.003)} & \makecell{431.558 \\ (169.15)} & \makecell{442.394 \\ (155.412)} & \makecell{348.24 \\ (139.308)} & \makecell{438.987 \\ (151.256)} & \makecell{440.075 \\ (151.842)} & \makecell{441.839 \\ (153.669)}  \\
+\cline{2-19}
+ & \multirow[t]{3}{*}{50} & 25 & \makecell{432.699 \\ (197.61)} & \makecell{481.517 \\ (180.227)} & \makecell{368.908 \\ (162.292)} & \makecell{443.575 \\ (194.823)} & \makecell{339.177 \\ (125.94)} & \makecell{444.025 \\ (194.793)} & \makecell{443.355 \\ (194.348)} & \makecell{443.488 \\ (194.801)} \\
+ &  & 45 & \makecell{836.618 \\ (324.041)} & \makecell{814.207 \\ (342.009)} & \makecell{721.727 \\ (251.258)} & \makecell{846.918 \\ (337.334)} & \makecell{614.541 \\ (170.535)} & \makecell{846.84 \\ (337.454)} & \makecell{846.12 \\ (337.28)} & \makecell{846.476 \\ (336.935)}  \\
+ &  & 5 & \makecell{93.694 \\ (47.708)} & \makecell{67.294 \\ (34.223)} & \makecell{71.908 \\ (25.233)} & \makecell{121.977 \\ (59.6)} & \makecell{79.943 \\ (23.445)} & \makecell{121.636 \\ (59.986)} & \makecell{121.991 \\ (59.878)} & \makecell{121.864 \\ (60.022)} \\
+\cline{1-19} \cline{2-19}
+\multirow[t]{9}{*}{10} & \multirow[t]{3}{*}{10} & 1 & \makecell{11.91 \\ (17.701)} & \makecell{28.907 \\ (43.717)} & \makecell{8.635 \\ (10.314)} & \makecell{15.504 \\ (18.187)} & \makecell{9.851 \\ (10.121)} & \makecell{16.438 \\ (16.91)} & \makecell{16.028 \\ (17.231)} & \makecell{16.369 \\ (17.874)}\\
+ &  & 5 & \makecell{143.56 \\ (167.634)} & \makecell{177.867 \\ (209.043)} & \makecell{94.755 \\ (76.06)} & \makecell{141.116 \\ (171.209)} & \makecell{75.967 \\ (54.791)} & \makecell{138.544 \\ (160.823)} & \makecell{140.159 \\ (163.716)} & \makecell{138.335 \\ (165.406)} \\
+ &  & 9 & \makecell{262.25 \\ (426.742)} & \makecell{201.942 \\ (170.517)} & \makecell{226.472 \\ (407.698)} & \makecell{267.779 \\ (417.718)} & \makecell{200.697 \\ (357.116)} & \makecell{264.61 \\ (412.264)} & \makecell{266.555 \\ (410.478)} & \makecell{267.376 \\ (415.85)} \\
+\cline{2-19}
+ & \multirow[t]{3}{*}{200} & 100 & \makecell{1808.579 \\ (2076.395)} & \makecell{2980.261 \\ (2754.132)} & \makecell{1808.738 \\ (2060.886)} & \makecell{1838.216 \\ (2040.237)} & \makecell{1834.696 \\ (2044.349)} & \makecell{1835.863 \\ (2057.228)} & \makecell{1834.512 \\ (2033.185)} & \makecell{1837.199 \\ (2046.792)} \\
+ &  & 180 & \makecell{4330.096 \\ (4779.502)} & \makecell{2342.614 \\ (2243.02)} & \makecell{4156.453 \\ (4253.531)} & \makecell{4340.759 \\ (4767.094)} & \makecell{4325.067 \\ (4751.866)} & \makecell{4356.129 \\ (4776.532)} & \makecell{4355.088 \\ (4763.186)} & \makecell{4365.29 \\ (4769.61)} \\
+ &  & 20 & \makecell{593.649 \\ (857.827)} & \makecell{244.895 \\ (281.378)} & \makecell{590.32 \\ (849.003)} & \makecell{599.976 \\ (833.877)} & \makecell{597.436 \\ (838.781)} & \makecell{590.162 \\ (821.858)} & \makecell{600.672 \\ (838.178)} & \makecell{594.873 \\ (848.782)} \\
+\cline{2-19}
+ & \multirow[t]{3}{*}{50} & 25 & \makecell{388.054 \\ (321.434)} & \makecell{324.916 \\ (308.065)} & \makecell{364.883 \\ (312.231)} & \makecell{360.303 \\ (306.296)} & \makecell{354.606 \\ (301.023)} & \makecell{362.582 \\ (309.18)} & \makecell{360.177 \\ (305.899)} & \makecell{359.78 \\ (306.077)} \\
+ &  & 45 & \makecell{895.964 \\ (794.069)} & \makecell{993.069 \\ (979.897)} & \makecell{898.587 \\ (810.784)} & \makecell{898.939 \\ (794.377)} & \makecell{885.455 \\ (745.737)} & \makecell{908.628 \\ (782.478)} & \makecell{906.609 \\ (780.218)} & \makecell{908.734 \\ (788.112)} \\
+ &  & 5 & \makecell{77.59 \\ (72.053)} & \makecell{120.175 \\ (149.159)} & \makecell{74.652 \\ (76.395)} & \makecell{72.223 \\ (70.693)} & \makecell{72.033 \\ (72.748)} & \makecell{74.309 \\ (72.165)} & \makecell{75.892 \\ (73.834)} & \makecell{74.12 \\ (70.883)} \\
+\cline{1-19} \cline{2-19}
+\multirow[t]{9}{*}{250} & \multirow[t]{3}{*}{10} & 1 & \makecell{9.285 \\ (2.219)} & \makecell{8.203 \\ (1.954)} & \makecell{9.376 \\ (2.179)} & \makecell{9.701 \\ (2.323)} & \makecell{9.704 \\ (2.302)} & \makecell{9.701 \\ (2.323)} & \makecell{9.701 \\ (2.323)} & \makecell{9.701 \\ (2.323)} \\
+ &  & 5 & \makecell{50.568 \\ (8.659)} & \makecell{44.651 \\ (7.361)} & \makecell{50.586 \\ (9.112)} & \makecell{51.251 \\ (8.933)} & \makecell{51.128 \\ (9.263)} & \makecell{51.251 \\ (8.933)} & \makecell{51.251 \\ (8.933)} & \makecell{51.251 \\ (8.933)} \\
+ &  & 9 & \makecell{92.956 \\ (26.567)} & \makecell{87.92 \\ (20.76)} & \makecell{92.847 \\ (26.272)} & \makecell{92.857 \\ (26.528)} & \makecell{93.317 \\ (25.737)} & \makecell{92.857 \\ (26.528)} & \makecell{92.856 \\ (26.529)} & \makecell{92.857 \\ (26.529)} \\
+\cline{2-19}
+ & \multirow[t]{3}{*}{200} & 100 & \makecell{2191.822 \\ (464.342)} & \makecell{2207.572 \\ (460.284)} & \makecell{1783.244 \\ (466.102)} & \makecell{2256.102 \\ (467.37)} & \makecell{1397.03 \\ (284.985)} & \makecell{2255.161 \\ (465.895)} & \makecell{2256.095 \\ (466.639)} & \makecell{2256.174 \\ (465.94)} \\
+ &  & 180 & \makecell{4037.567 \\ (847.844)} & \makecell{4017.374 \\ (704.43)} & \makecell{3477.884 \\ (714.527)} & \makecell{4083.589 \\ (859.518)} & \makecell{2554.422 \\ (614.084)} & \makecell{4081.027 \\ (859.12)} & \makecell{4082.227 \\ (861.805)} & \makecell{4080.481 \\ (860.907)} \\
+ &  & 20 & \makecell{374.787 \\ (102.866)} & \makecell{292.05 \\ (66.283)} & \makecell{282.808 \\ (73.489)} & \makecell{479.24 \\ (121.248)} & \makecell{281.375 \\ (56.671)} & \makecell{479.953 \\ (121.219)} & \makecell{479.651 \\ (120.956)} & \makecell{479.596 \\ (121.574)} & \\
+\cline{2-19}
+ & \multirow[t]{3}{*}{50} & 25 & \makecell{303.069 \\ (66.83)} & \makecell{304.353 \\ (83.207)} & \makecell{296.789 \\ (68.898)} & \makecell{303.902 \\ (61.62)} & \makecell{289.719 \\ (63.05)} & \makecell{303.919 \\ (61.637)} & \makecell{303.9 \\ (61.61)} & \makecell{303.923 \\ (61.631)} \\
+ &  & 45 & \makecell{538.998 \\ (127.705)} & \makecell{565.719 \\ (125.848)} & \makecell{532.489 \\ (129.833)} & \makecell{534.825 \\ (125.456)} & \makecell{502.432 \\ (130.652)} & \makecell{534.794 \\ (125.417)} & \makecell{534.832 \\ (125.462)} & \makecell{534.779 \\ (125.407)}  \\
+ &  & 5 & \makecell{55.19 \\ (12.429)} & \makecell{43.153 \\ (10.311)} & \makecell{53.335 \\ (12.516)} & \makecell{66.509 \\ (10.663)} & \makecell{63.255 \\ (13.669)} & \makecell{66.512 \\ (10.667)} & \makecell{66.512 \\ (10.664)} & \makecell{66.516 \\ (10.66)} \\
+\cline{1-19} \cline{2-19}
 \bottomrule
+\end{longtable}
 \label{tab:PredSim}
-\end{longtable}
 \end{landscape}
@@
 
-\section{Possible Extensions and Criticism}
+\section{Possible Extensions and Criticism}\label{sec:crit}
 

### 2024-09-06 02_simulation/tgr.py

@@ -1,4 +1,5 @@
 # this is the base package for triple gamma regularizazion
+
 import torch
 import torch.nn as nn
 import torch.optim as optim

### 2024-09-24 01_latex/MScThesis_Econ.tex
v0.9 of tex

--- 2024-08-06 01_latex/MScThesis_Econ.tex
@@
 \usepackage{tikz}
+\usepackage{float}
+\usepackage{csquotes}
+\MakeOuterQuote{"}
 
 % Packages for Tables -----
+\usepackage{pdfpages}
 \usepackage{multirow}
@@
 \usepackage[style=apa, backend=biber]{biblatex}
-\addbibresource[]{ref.bib}
+\addbibresource[]{corrected_ref.bib}
 \renewcommand{\baselinestretch}{1.25}
@@
 \pagestyle{fancy}
-\lhead{\slshape Unterweger}
+\lhead{\slshape L. P. Unterweger}
 \chead{}
@@
 
+\includepdf[pages=1]{cover_signed.pdf}
+
 \begin{titlepage}
@@
 Examiner: & Peter Knaus, PhD \\
-Submission date: & TBA \\
+			& \textit{Vienna University of Economics and Business} \\
+			& \textit{Harvard University} \\
+			& \\
+Submission date: & 25.09.2024 \\
 \end{tabular}
@@
 by\\ \vspace{3mm}
-{\Large Lucas Unterweger \href{https://github.com/therealLucasPaul}{\includegraphics[scale=0.01]{GitHub.png}}}\\
+{\Large Lucas Paul Unterweger, B.Sc. (WU) \href{https://github.com/therealLucasPaul}{\includegraphics[scale=0.01]{GitHub.png}}}\\
 (Student-ID: 11913169)\\
@@
 \begin{abstract}
-Lorem ipsum...
+This thesis introduces the Triple-Gamma Regularization (TGR), a novel non-convex penalty term inspired by the Triple-Gamma prior, which provides increased flexibility in handling under- and overfitting in high-dimensional regression problems.
+The proposed method offers a unifying framework that bridges convex penalties like LASSO and non-convex penalties such as Gaussian and Arctan, allowing for fine-tuning of the regularization process through adjustable hyperparameters.
+First, a detailed theoretical derivation of the TGR is provided, highlighting its properties and advantages over existing regularization methods.
+Then, a comprehensive simulation study is conducted to evaluate the performance of TGR under various high-dimensional scenarios.
+The results indicate that TGR can outperform traditional regularization techniques in several settings, particularly in terms of minimizing mean squared error.
+This thesis also addresses the computational challenges associated with non-convex optimization problems and explores potential solutions through gradient-based optimization techniques.
+These findings contribute to the growing body of literature on regularization methods and offer practical insights for future applications in sparse modeling and high-dimensional data analysis.
 \end{abstract}
@@
 
-I like to acknowledge ...
+This completion oft this thesis would not have been possible without so many amazing people in my life who supported me throughout the process of writing this master's thesis and the master program as a whole.
+I want to thank my mum, Daniela, and my dad, Werner, who always picked me up when I lost my motivation to continue and who convinced me to keep going time after time.
+I want to thank my brother, Tobias, who always readily listened to me complaining for hours and hours on end about things he probably barely understood and yet always agreed with me about my computational issues while doing the simulations.
+And most of all I want to thank my advisor, Peter, who always supported me from the day I randomly dropped an e-mail into his e-mail inbox about becoming his tutor in econometrics, although not having met once during the distance learning phase of the COVID pandemic, up until today.
+From working as a tutor in his team, writing a bachelor thesis, and to the support during this master thesis now.
+Even though sometimes living 12h time differences apart, one in Boston the other in Manila, he always answered any questions I had and supported me in whatever way he could and I want to sincerely thank him for that!
 
@@
 Willam of Ockham, born in Ockham, Surrey, probably lived between 1287 and 1348 and is nowadays recognized as a pre-eminent philosopher of the middle ages.
-Although     his name itself is no common knowledge, a principle carrying his name is: \textit{Ockham's Razor}.
+While his name may not be widely known, the principle that bears his name is well recognized: \textit{Ockham's Razor}.
 Interestingly, the main formulation of the principle (\textit{Entia non sunt multiplicanda praeter necessitatem} [plurality should not be posited without necessity]) can not be traced back to Ockham directly, but variations of it can be found in Ockham's writings.
-Since then nonetheless, the principle has long been used by statisticians and other researchers as a a scientific credo to capture the notion that "the simpler of two explanations is to be preferred" \parencite{Lazar2010}.
+Nonetheless, since then, the principle has long been used by statisticians and other researchers as a scientific credo to capture the notion that "the simpler of two explanations is to be preferred" \parencite{Lazar2010}.
+Recent decades and their advancements in information technology have opened the gates to seemingly unlimited amounts of data and information.
+Whether it is data about the carbon dioxide levels near bus stations in a city, the intraday trading volume of a specific financial asset or the rhythm of a beating heart throughout a day, new techniques and approaches in measuring digital and natural phenomena have enabled researchers all around the globe to study previously unknown effects, test novel hypotheses and find relationships between real world process that would have otherwise remained hidden from the eye of human civilization.\\
 
-\begin{lightbluebox}
-Finish Intro
-\end{lightbluebox}
+Yet, these advancements come at a cost.
+Conventional statistical models like the \textit{ordinary least squares (OLS)} have trouble handling statistical problem in higher dimensions.
+When the relative number of features to the number of data points in a statistical model is very high, the estimates of these models suffer from high variance and thus generalize poorly.
+Frequentist statisticians have developed penalized regression approaches to battle these issues, which incorporate a penalty term into the optimization problems used to estimate the coefficients of linear models.
+In recent decades, various penalty terms have been published each with its own advantages and disadvantages, yet to this day no single method has emerged to triumph above them all \parencite{WangEtAl2020}.\\
 
-The remaining thesis is structure as follows: Section 3 will provide a literature review about the history of regularization and advancements in the field along with an overview of established concepts and their respective advantages and disadvantages.
-Section 4 will quickly discuss the mathematical building block for this thesis by showcasing the bridge between regularization and Bayesian shrinkage prior as well as introduce the Triple-Gamma-Prior by \textcite{TGP2020} as the shrinkage prior of choice.
+Bayesian statisticians have developed their own tools to handle high-dimensional statistical problems and commonly use specific probability distributions to battle model complexity by shrinking the estimates of less important variables towards zero (thus the name \textit{shrinkage prior}).
+Although these two fields of statistical thought use different approaches to tackle the same problem, a striking mathematical connection exists between those two methods.
+A bridge which allows mathematicians to derive a regularization penalty from specific prior distributions, which raises the question: "Does there exist a already known prior distribution in the Bayesian setting which can be used to derive a regularization penalty which might perform better than existing penalties?".\\
+
+A prior distribution which might have these suitable properties is the unifying shrinkage prior developed by \textcite{TGP2020} called \textit{Triple-Gamma-Prior}.
+Its unifying properties and the fact that a closed-form solution for the marginal prior exists might lead to favourable properties in the realm of frequentist statistics.
+Before that it is necessary to have a closer look at what the exact problem is that Bayesian shrinkage priors and regularization approaches are trying to solve.
+An overview of this along with a theoretical basis of the necessary concepts will be presented in section 2.\\
+
+The remaining thesis is structured as follows: Section 3 will provide a literature review about the history of regularization and advancements in the field along with an overview of established concepts and their respective advantages and disadvantages.
+Section 4 will quickly discuss the mathematical building block for this thesis, by showcasing the bridge between regularization and Bayesian shrinkage prior as well as introduce the Triple-Gamma-Prior by \textcite{TGP2020} as the shrinkage prior of choice.
 Section 5 will then derive the proposed penalty by utilizing the bridge explained in section 4.
@@
 \section{Theoretical Section}\label{sec:theorysuper}
-Generally speaking, a major part of statistical learning deals with trying to describe a certain output variable $Y$ with a set of input variables $X_1, \cdots, X_p$ by trying to find a functional form $f$ which uses the given information in the inputs and - ideally - describes the hidden relationship between $Y$ and the inputs $X_i$ as accurately as possible.
+Generally speaking, a major part of statistical learning deals with trying to describe a certain output variable $\mathbf{Y}$ with a set of input variables $\mathbf{X_1}, \cdots, \mathbf{X_p}$ by trying to find a functional form $f$ which uses the given information in the inputs and - ideally - describes the hidden relationship between $\mathbf{Y}$ and the inputs $\mathbf{X_p}$ as accurately as possible.
 However, it comes as no surprise that the functional form $f$ depends on the statistical problem at hand.
@@
 
-The first of these two goals - \textit{inference} - aims at understanding the relationship that may or may not exist between the input variables $X_i$ and the output $Y$.
+The first of these two goals - \textit{inference} - aims at understanding the relationship that may or may not exist between the input variables $\mathbf{X_i}$ and the output $\mathbf{Y}$.
 Especially applied sciences like Economics, Psychology and Medicine often try to find a (causal) relationship within their theoretical framework to evaluate a policy, a medication or a new form of therapy.
 Linear models for example often provide a simple and straightforward framework which provide the scientist with interpretable effects.
-\textit{Prediction} on the other hand aims at forecasting the output variable $Y$ as accurately as possible and using every bit of information that is available, but disregards interpretability.
-\parencite{ESL,21} These goals can be summarized by viewing it as a decision between \textit{prediction accuracy} and \textit{model interpretability}, which has thoroughly been explained by \textcite{ESL}.\\
+\textit{Prediction} on the other hand aims at forecasting the output variable $Y$ as accurately as possible and using every bit of information that is available, but disregards interpretability \parencite[21]{ESL2009}.
+These goals can be summarized by viewing it as a decision between \textit{prediction accuracy} and \textit{model interpretability}, which has thoroughly been explained by \textcite{ESL2009}.\\
 
-For the purpose of this thesis, the following chapters will restrict itself to the case of linear models, hence where assume that the functional form $f$ is linear in its inputs.
+For the purpose of this thesis, the following chapters will restrict itself to the case of linear models, hence we assume that the functional form $f$ is linear in its inputs.
 The commonly known \textit{least squares estimator} is one way of estimating such a functional form and due to its many desirable properties has gained popularity in various  scientific fields.
@@
 
-\begin{lightbluebox}
-- BIAS VARIANCE TRADE-OFF
-- DIMENSIONALITY PROBLEM
+In supervised learning, a model is fitted on an observed dataset where both inputs and outputs are given in pairs.
+Using this data a statistical model aims to find a functional form which maps these inputs into the output space and thus describes a relationship between those two spaces.
+Naturally, one would assume to find a functional form which manages to describe the relationship as closely as possible by minimizing a chosen loss function.
+Yet, this often ignores a problem called "overfitting" which can loosely be described as using "too much information" from the training dataset.
+As described by \textcite{Ying2019}, this problem arises from the fact "that [an] over-fitted model has difficulty coping with pieces of the information in the testing set, which may be different from those in the training set".
+A more formal definition of overfitting has been defined by \textcite{Mitchell1997}:\\
 
-General problem: Fit vs. Complexity. What to choose and where is the optimal balance?
-\end{lightbluebox}
+\textbf{Definition 1:} Given a hypothesis space $\mathcal{H}$, a hypothesis $h \in \mathcal{H}$ is said to overfit the training data if there exists some alternative hypothesis $h' \in \mathcal{H}$ such that $h$ has smaller error than $h'$ over the training examples, but $h'$ has a smaller error than $h$ over the entire distribution of instances.\\
+
+Theoretically, this problem can emerge from a multitude of reasons.
+One of which being that learning every piece of information in the training dataset can lead to fitting the noise rather than fitting the underlying pattern.
+Another reason can be ill-chosen degrees of model complexity, because "having many hypotheses intuitively increase the risk of randomly finding a solution that learns the training set “by heart”, with limited generalization ability." \parencite{ParisRobilliardFonlupt2003}.\\
 
@@
 For example, a first order polynomial has two coefficients to estimate: the intercept $\beta_0$ and the slope $\beta_1$.
-A polynomial of order of order eight has nine coefficients to estimate.
+A polynomial of order eight has nine coefficients to estimate.
 What can now be seen in figure \ref{fig:polyfit} is the change in estimates if we include/exclude the additional red data point.
@@
 In the case of the eighth-order polynomial, we need at least nine data points to create a fit as we have nine predictors (one intercept and one coefficient for each of the eight powers).
-In this case $n=p$ and adding another data point drastically changes the estimates coefficients, which means that the model won't perform well in out-of-sample scenarios.
+In this case $n=p$ and adding another data point drastically changes the estimated coefficients, which means that the model won't perform well in out-of-sample scenarios.
 This emphasizes the importance a sufficient sample size when fitting linear models.
-And this leads us to the core field of study of this thesis: What are ways to improve the generalization of a linear model in scenarios where the sample size is not sufficiently large enough or high-dimensionality becomes a problem?\\
+And this leads us to the core field of study of this thesis: What are ways to improve the generalization of a linear model in scenarios where the sample size is not sufficiently large or high-dimensionality becomes a problem?\\
 
@@
 The main problem to solve is how to accurately approach the problem of feature selection and make models generalize better.
-A first approach could be to increase the sample size to re-establish the unbiasedness of methods like OLS, however either the problem at hand involves a scenario with only few data points to begin with, or due to an extensive number of features, the collection of a sufficient amount of data points is practically not feasible.
-Another approach could be to use common variable selection methods like \textit{AIC} and \textit{BIC}, but as \textcite{FanLi2006} point out, "[t]raditional variable selection such as $C_p$, AIC and BIC involves a combinatorial optimization problem, which is NP-hard, with computational time increasing exponentially with the dimensionality." A third and computationally more feasible approach involves a concept called \textit{penalized regression}, more commonly known as \textit{Regularization}.
+A first approach could be to increase the sample size to re-establish the unbiasedness of methods like \textit{OLS}, however either the problem at hand involves a scenario with only few data points to begin with, or due to an extensive number of features, the collection of a sufficient amount of data points is practically not feasible.
+Another approach could be to use common variable selection methods like \textit{AIC} and \textit{BIC}, but as \textcite{FanLi2006} point out, "[t]raditional variable selection such as $C_p$, AIC and BIC involves a combinatorial optimization problem, which is NP-hard, with computational time increasing exponentially with the dimensionality." A third and computationally more feasible approach involves a concept called \textit{penalized regression}, more commonly known as \textit{regularization}.
 
@@
 \[
-\underset{f \in \mathcal{H}}{\min}\left\{\sum_{i=1}^N L(y_i, f(x_i)) + \lambda{J}(f)\right\}
+\underset{f \in \mathcal{H}}{\min}\left\{\sum_{i=1}^N L(y_i, f(x_i)) + \lambda{J}(f)\right\},
 \]
 where $L(.)$ refers to a loss function defined as some function of the true values and the predicted values and $J(f)$ is penalty based on the chosen functional from a space of functions $\mathcal{H}$.
-In the context of penalized linear regression, this is equivalent to finding the set of risk minimizing coefficients $\hat{\beta}$ from the set of all possible combinations of coefficients $\boldsymbol{\beta}$.
-\MC Thus, resulting in the general class of regularization problems of the form:
+In the context of penalized linear regression, this is equivalent to finding the set of risk minimizing coefficients $\hat{\beta}$ from the set of all possible combinations of coefficients $\mathbf{\beta}$ \parencite{ESL2009}.
+Thus, resulting in the general class of regularization problems of the form:
 \[
-\underset{\beta \in \boldsymbol{\beta}}{\min}\left\{\sum_{i=1}^N L(y_i, f_\beta(x_i)) + \lambda{J}(\beta)\right\}
+\underset{\beta \in \boldsymbol{\beta}}{\min}\left\{\sum_{i=1}^N L(y_i, f_\beta(x_i)) + \lambda{J}(\mathbf{\beta})\right\},
 \]
-where $f_\beta(x_i)$ is a linear function of the inputs $x_i$ parametrized by the coefficients $\beta$.
+where $f_\beta(x_i)$ is a linear function of the inputs $x_i$ parametrized by the coefficients $\mathbf{\beta}$.
 Hence, in this setting, regularization deals with penalizing the risk function based on the value of the chosen set of coefficients.
-\\
-However, this only describes a subset of \textit{regularization} methods as stated by \textcite{Taxonomy2017}. The authors use a more general definition of regularization:\\
+However, this only describes a subset of \textit{regularization} methods as stated by \textcite{Taxonomy2017}.
+The authors use a more general definition of regularization:\\
 
-\textbf{Defintion 1. Regularization} is any supplementary technique that aims at making the model generalize better, i.e. produce better results on the test set.\\
+\textbf{Defintion 2: Regularization} is any supplementary technique that aims at making the model generalize better, i.e. produce better results on the test set.\\
 
-Building on that, they split up the majority of \textit{regularization} methods into  (1) methods applied to the data set like transformations or modifications of the inputs, (2) methods altering the selected model family , (3) methods applied to the error/loss function $L(y_i, f_\beta(x_i))$ , (4) methods applied to regularization/penalty term as described above and (5) alterations of the optimization procedure itself.
-
-Unsurprisingly, this thesis is concerned with the fourth group of regularization methods, which add a penalty/regularization term $J(\beta)$ into the risk function, but before advancing to literature that deals with this kind of problem, it is necessary to establish a terminology which will be used throughout this thesis.
+Building on that, they split up the majority of \textit{regularization} methods into  (1) methods applied to the data set like transformations or modifications of the inputs, (2) methods altering the selected model family, (3) methods applied to the error/loss function $L(y_i, f_\beta(x_i))$, (4) methods applied to regularization/penalty term as described above and (5) alterations of the optimization procedure itself.
+Unsurprisingly, this thesis is concerned with the fourth group of regularization methods, which add a penalty/regularization term $J(\beta)$ into the risk function.
+Before advancing to literature that deals with this kind of problem, it is necessary to establish terminology which will be used throughout this thesis.
 This terminology will be the following:
 
-Let $\mathcal{D}$ be a training data set with $n \in \mathbb{N}$ observations, where every  consists of a target variable $y_i \in \mathbb{R}$ along with a number of corresponding inputs $x_i \in \mathbb{R}$.
-Given a linear function $f_\beta(x_i)$ of the inputs parametrized by coefficients $\beta \in \boldsymbol{\beta}$, $L(y_i f_\beta(x_i))$ is the \textbf{Loss} function measuring the discrepancy between the actual target $y_i$ and the output of the linear function $f_\beta(x_i)$.
-According to \textcite{Vapnik1991}, the \textbf{Empirical Risk Functional} is then
+Let $\mathcal{D}$ be a training data set with $n \in \mathbb{N}$ observations, where every data point consists of a target variable $y_i \in \mathbb{R}$ along with a number of corresponding inputs $x_i \in \mathbb{R}^p$.
+Given a linear function $f_\beta(x_i)$ of the inputs parametrized by coefficients $\beta \in \boldsymbol{\beta}$, $L(y_i f_\beta(x_i))$ is the \textit{Loss} function measuring the discrepancy between the actual target $y_i$ and the output of the linear function $f_\beta(x_i)$.
+According to \textcite{Vapnik1991}, the \textit{Empirical Risk Functional} is then
 \[
@@
 \]
-\textbf{Regularization} in this thesis' context refers then to adding some penalty function $J(\beta)$ dependent on the set of parameters $\beta$, multiplied by some weighting parameter $\lambda$, to the empirical risk functional $R_{emp}(\beta)$.
+\textit{Regularization} in this thesis' context refers then to adding some penalty function $J(\beta)$ dependent on the set of parameters $\beta$, multiplied by some weighting parameter $\lambda$, to the empirical risk functional $R_{emp}(\beta)$.
 Thus, $R_{reg} = R_{emp}(\beta) + \lambda\cdot J(\beta)$.
@@
 &=\underset{\beta \in \boldsymbol{\beta}}{\argmin}\left\{R_{emp}(\beta) + \lambda\cdot J(\beta)\right\}\nonumber\\
-&=\underset{\beta \in \boldsymbol{\beta}}{\argmin}\left\{\sum_{i=1}^n L(y_i, f_\beta(x_i)) + \lambda\cdot J(\beta)\right\}\label{eq:genreg}
+&=\underset{\beta \in \boldsymbol{\beta}}{\argmin}\left\{\sum_{i=1}^n L(y_i, f_\beta(x_i)) + \lambda\cdot J(\beta)\right\}.\label{eq:genreg}
 \end{align}
 
-It is important to note here that as $J(\beta)$ is only a function of the coefficients $\beta$ and neither the targets $y_i$ nor the inputs $x_i$.
-It only affects the generalization error of the model, not the training error given by the empirical risk functional $R_{emp}(\beta)$.
+It is important to note here that $J(\beta)$ is only a function of the coefficients $\beta$ and neither the targets $y_i$ nor the inputs $x_i$.
+Therefore, it only affects the generalization error of the model, not the training error given by the empirical risk functional $R_{emp}(\beta)$.
 
@@
 To build on the mathematical connection between the Bayesian and Frequentist approach to battle model complexity, which will be used as the building block of this thesis later on, it is necessary to make a quick detour and quickly recap on how Bayesian statisticians tackle model complexity.
-
-\begin{lightbluebox}
-Explain Shrinkage Prior
-\end{lightbluebox}
-
+Shrinkage priors, such as the \textit{horseshoe} prior \parencite{Carvalho2010} or the \textit{Triple-Gamma} prior \parencite{TGP2020}, place a large amount of probability mass near zero while allowing for heavier tails, meaning that most parameter estimates are small, but the prior still allows for larger values when strongly supported by the data.
+This behavior structure of a probability distribution reduces the influence of irrelevant variables while retaining the effect of significant variables, thus improving both the predictive performance of the model in high-dimensional data settings, where often only a few variables are relevant in a set of multiple irrelevant variables.
+Unlike standard normal prior distributions, shrinkage priors actively encourage sparsity, making them particularly effective for feature selection and regularization in high-dimensional models \parencite{PiironenVehtari2017}.
 \newpage
@@
 Arguably, this methodological approach to penalized regression started with the publication of two pieces of literature published by Arthur Hoerl and Robert Kennard in 1970 \parencite{HoerlKennard1970a, HoerlKennard1970b}.
-With these two papers the authors introduced the widely known \textit{Ridge Regression}, which has been developed from the previously known concept of Ridge analysis.
-In its core, the authors were trying to tackle the problem of high variances of the regression coefficients in high-dimensional problem settings.
+With these two papers, the authors introduced the widely known \textit{Ridge Regression}, which was derived from the previously known concept of Ridge analysis.
+At its core, the authors were trying to tackle the problem of high variances of the regression coefficients in high-dimensional problem settings.
 This shrinkage estimator, which uses the squared coefficient as a penalty term, "attempt[s] to shrink the coefficients to
@@
 The closed from solution of the Ridge estimator is given by
-$$\hat{\beta}_{Ridge} = \left(X^TX+\lambda I\right)^{-1}X^Ty$$,
+$$\hat{\beta}_{Ridge} = \left(X^TX+\lambda I\right)^{-1}X^Ty,$$
 which adjusts the OLS estimator by shifting the main diagonal entries of the design matrix by $\lambda$ ($\lambda \geq 0$).
 It can be shown that this closed form estimator is equivalent to a Lagrangian problem of the following form \parencite{VanWieringen2015}:
-$$\hat{\beta}_{Ridge}(\lambda) = \underset{\beta}{\argmin}\left\{\norm{y-X\beta}_2^2 + \lambda\norm{\beta}_2^2\right\}$$
+$$\hat{\beta}_{Ridge}(\lambda) = \underset{\beta}{\argmin}\left\{\norm{y-X\beta}_2^2 + \lambda\norm{\beta}_2^2\right\}.$$
 This resembles an example of the above defined regularization framework with squared residual loss and a penalty term of the form $\norm{\beta}_2^2$, which only depends on the parameter $\beta$.
@@
 One concept which is almost as famous \textit{Ridge Regression} is the \textit{Least Absolute Shrinkage and Selection Operator}, more commonly know as \textit{LASSO}, developed by \textcite{Tibishirani1996}.
-He argues that the two at the time most prominent shrinkage methods - Ridge and Subset Selection - both have their drawbacks.
+He argues that the two most prominent shrinkage methods at the time - Ridge and Subset Selection - both have their drawbacks.
 Ridge regression on the one hand is an optimization problem which continuously shrinks coefficients towards zero, but doesn't select them in a discrete sense, which makes it hard to interpret these models.
@@
 
-\textit{LASSO} and to some extend \textit{Ridge} can be viewed as a special case of a $l_p$-norm regularization with corresponding values for $p$ ($p = 1$ for LASSO and $p=2$ for Ridge) \parencite{FrankFriedman1993}.
+\textit{LASSO} and to some extend \textit{Ridge} can be viewed as a special case of a $l_p$-norm regularization with corresponding values for $p$ ($p = 1$ for LASSO and $p=2$ for Ridge) \parencite{FrankFriedman1993}
 
-$$\norm{\beta}_p =  \left(\sum_{i=1}^p|\beta_i|^p\right)^{1/p}$$
+$$\norm{\beta}_p =  \left(\sum_{i=1}^p|\beta_i|^p\right)^{1/p}.$$
 
@@
 Due to this particular situation in the literature, several other methods have been proposed in the recent years and decades.
-An approach combining \textit{Ridge} and \textit{LASSO} two methods is called \textit{Elastic Net} regularization and has been developed by \textcite{ZouHastie2005}.
+An approach combining the \textit{Ridge} and \textit{LASSO} methods is called \textit{Elastic Net} regularization and has been developed by \textcite{ZouHastie2005}.
 The authors there elaborate on some of the shortcomings of the LASSO method.
@@
 In its core, \textit{Elastic Net Regularization} linearly combines the penalty terms of \textit{Ridge} and \textit{LASSO} regularization, yielding a loss function of the form:\\
-$$J(\beta) = \lambda_1 \norm{\beta}_2^2 + \lambda_2 \norm{\beta}_1$$
+$$J(\beta) = \lambda_1 \norm{\beta}_2^2 + \lambda_2 \norm{\beta}_1.$$
 The authors have	 shown that, especially when it comes to encouraging the aforementioned grouping effects, \textit{Elastic Net} tends to perform better than the \textit{LASSO}.\\
@@
 To better incorporate the proposed concept of this thesis into this body of literature, I am proposing a third property to distinguish penalty terms: (3) How does the function behave in the limits?
-(Does it converge or diverge?) \\
+(Does it converge or diverge?) Such a classification tree can be found in figure \ref{fig:Classification}.
+\\
 
+\begin{figure}
 \begin{center}
@@
 \end{center}
-
+\caption{A possible classification of regularization methods based on the mathematical properties of the penalty function} \label{fig:Classification}
+\end{figure}
 As already mentioned earlier in section \ref{sec:theorysuper}, a penalty function is a function dependent on the parameter of the model and it does not depend on the data at hand.
 Thus, changes in your data set does not effect the penalty directly, but only the overall optimization problem through the empirical risk functional $R_{emp}$.
-The following table classifies some of the existing concepts based on the three criteria mentioned earlier.
+The following table \ref{tab:ClassificationOfPenalties} classifies some of the existing concepts based on the three criteria mentioned earlier.
 A visualisation of them can be found in figure \ref{fig:DifferentPenalties} in chapter \ref{subsec:comparepenalties}.\\
@@
 As thoroughly described by \parencite{JohnVettamWu2022}, penalties with a singularity at origin tend to be suitable when the goal of the statistical analysis is variable selection but "could pose theoretical and computational challenges when the focus is on regularization alone without variable selection." In addition, it has been shown in the literature that "objective functions which are a sum of a nonconvex, singular-at-origin penalty function coupled with either a smooth nonconvex loss function or a nonsmooth convex loss function, often fails to satisfy a theoretical condition known as ‘Clarke regularity’." (A result presented in \textcite{QiCuiLiuPang2021})
-Convex penalties are generally easier to implement using common optimization algorithms than non-convex penalties and, more importantly, penalties which are divergent and its limits, which most convex penalties are, yield biased results.
+Convex penalties are generally easier to implement using common optimization algorithms than non-convex penalties but, more importantly, penalties which are divergent in its limits, which most convex penalties are, yield biased results.
 Due to the fact that, when using divergent and convex penalties like LASSO and Ridge, the additional penalty for larger estimates keeps rising with estimates which deviate from zero, estimates are getting artificially pulled towards zero and are thus biased.
 Non-Convex penalties, which are usually convergent in its limits towards $-\infty$ and $+\infty$, tend to yield unbiased results as the additional penalty becomes zero as soon as a certain threshold is crossed (Again, referring to the visualisation in figure \ref{fig:DifferentPenalties}).
+
 \begin{table}[!h]
 \begin{center}
-\begin{tabular}{lcccc}\toprule
+\begin{tabular}{llccc}\toprule
  \multicolumn{2}{c}{Penalty} & \multicolumn{3}{c}{Classification}\\
 		\cmidrule(r{4pt}){1-2} \cmidrule(l){3-5}
-Penalty     	& Reference  & \makecell{Behaviour\\ at Origin} & (Non-)Convexity & Limits\\\midrule
+Penalty     	& Reference  & \makecell{Behaviour\\ at Origin} & \makecell{(Non-)\\Convexity} & Limits\\\midrule
 
-LASSO 	& \textcite{Tibishirani1996}	& Singular	&	Convex 	& Divergent\\
-Ridge 	& \textcite{HoerlKennard1970a}	& Smooth		& Convex			& Divergent\\
-Gaussian & \textcite{JohnVettamWu2022}	& Smooth		& Non-Convex 	& Convergent\\
-Ar(c)tan 	& \textcite{WangZhu2016}	& Singular 	& Non-Convex 	& Convergent\\
-Elastic-Net & \textcite{ZouHastie2005} & Singular & Convex &\\
+LASSO 	& \textcite{Tibishirani1996}	& Singular	&	C 	& Div.\\
+Ridge 	& \textcite{HoerlKennard1970a}	& Smooth		& C			& Div.\\
+Gaussian & \textcite{JohnVettamWu2022}	& Smooth		& NC 	& Conv.\\
+Ar(c)tan 	& \textcite{WangZhu2016}	& Singular 	& NC 	& Conv. \\
+Elastic-Net & \textcite{ZouHastie2005} & Singular & C &\\
 Bridge & \textcite{FrankFriedman1993}& Both &&\\
-MCAP & \textcite{Zhang2010}& Singular & Non-Convex &\\
-SCAD & \textcite{FanLi2001} & Singular & Non-Convex &\\
-Laplace & \textcite{TrzaskoManduca2009} & Non-Convex &&\\
-Triple-Gamma & - & \makecell{Depending\\ on parameters} & Non-Convex & Divergent \\
+MCAP & \textcite{Zhang2010}& Singular & NC &\\
+SCAD & \textcite{FanLi2001} & Singular & NC &\\
+Laplace & \textcite{TrzaskoManduca2009} & NC &&\\
+Triple-Gamma & - & \makecell{Depending\\ on \\ parameters} & NC & Div. \\
 
@@
 
-In a Bayesian setting, one usually assumes that the parameter vector $\mathbb{\beta}$ has a prior distribution $p(\mathbb{\beta}$.
+In a Bayesian setting, one usually assumes that the parameter vector $\mathbb{\beta}$ has a prior distribution $p(\mathbb{\beta})$.
 By multiplying it with the likelihood of the data $f(y|X,\beta)$ and by utilizing Bayes' rule, one retrieves the posterior distribution of the parameter distribution, up to a proportionality constant:
 
-$$p(\beta|y,X) \propto f(y|X, \beta) \times p(\beta)$$
+$$p(\beta|y,X) \propto f(y|X, \beta) \times p(\beta).$$
 
-It turns out, as can be seen in \textcite[248--250]{ESL2009} and \textcite{VanWieringen2015} among others, that when choosing certain prior distributions and using standard assumptions in Bayesian modelling (ie the individual parameters of the parameter vector are independent a prior and the errors of the standard linear model are drawn from a normal distribution), that the moments of the posterior distributions correspond to the point estimates of a regularization approach in a frequentist setting.
+It turns out, as can be seen in \textcite[248--250]{ESL2009} and \textcite{VanWieringen2015} among others, that when choosing certain prior distributions and using standard assumptions in Bayesian modelling (ie the individual parameters of the parameter vector are independent a priori and the errors of the standard linear model are drawn from a normal distribution), that the mode of the posterior distributions correspond to the point estimates of a regularization approach in a frequentist setting.
 As this idea is essential to the entire thesis, a shortened derivation of this duality for the case of \textit{Ridge} regression will now be shown.\\
 
-Assuming that a response variable $y_i$ follows a linear model with $k$ variables and errors $\epsilon_i \sim \mathcal{N}(0, \sigma^2)$, then the likelihood of the data is given by
-$$\mathcal{L}(y|X,\beta)=\frac{1}{(2\pi\sigma^2)^{n/2}}\exp\left(-\frac{1}{2\sigma^2}\sum_{i=1}^n\epsilon_i^2\right).$$
+Assuming that a response variable $y_i$ follows a linear model with $p$ variables and errors $\epsilon_i \sim \mathcal{N}(0, \sigma^2)$, then the likelihood of the data is given by
+$$\mathcal{L}(y|X,\beta)=\frac{1}{(2\pi\sigma^2)^{n/2}}\exp\left(-\frac{1}{2\sigma^2}\sum_{i=1}^n(y_i-x_i^T\beta)^2\right).$$
 
-Under the previously mentioned assumption that $p(\beta) = \prod_{i=1}^k$ and by choosing a Gaussian distribution with mean zero and variance $\tau^2$, we gain the prior distribution
+Under the previously mentioned assumption that $p(\beta) = \prod_{i=1}^k \beta_i$ and by choosing a Gaussian distribution with mean zero and variance $\tau^2$, we gain the prior distribution
 $$p(\beta) = \frac{1}{(2\pi\tau^2)^{p/2}}\exp\left(-\frac{1}{2\tau^2}\norm{\beta}_2^2\right).$$
 
-Putting both together using Bayes' theorem yields and taking the $\log$ of the distribution yields
-$$\log(p(\beta|y,X)) \propto -\frac{1}{2\sigma^2}\sum_{i=1}^n \epsilon_i^2  - \frac{1}{2\tau^2}\norm{\beta}_2^2.$$
+Putting both together using Bayes' theorem and taking the $\log$ of the distribution yields
+$$\log(p(\beta|y,X)) \propto -\frac{1}{2\sigma^2}\sum_{i=1}^n (y_i-x_i^T\beta)^2  - \frac{1}{2\tau^2}\norm{\beta}_2^2.$$
 
@@
 
-$$\hat{\beta}_{MAP} = \underset{\beta}{\argmin}\left\{\frac{1}{2\sigma^2}\sum_{i=1}^n \epsilon_i^2  + \frac{1}{2\tau^2}\norm{\beta}_2^2\right\}$$
+$$\hat{\beta}_{MAP} = \underset{\beta}{\argmin}\left\{\frac{1}{2\sigma^2}\sum_{i=1}^n \epsilon_i^2  + \frac{1}{2\tau^2}\norm{\beta}_2^2\right\}.$$
 
@@
 
-Yet, before diving into the mathematical core of this thesis which derives said concept, it is necessary to have a look at the Triple-Gamma-Prior in depth to explain why this particular prior might prove itself to provide a useful building block for a novel regularization penalty.
+Yet, before diving into the mathematical core of this thesis which derives said concept, it is necessary to have a look at the Triple-Gamma-Prior in depth to explain why this particular prior might prove itself to provide a useful building block for a novel regularization penalty.\\
 
-\begin{lightbluebox}
-Describe TRIPLE GAMMA PRIOR
-\end{lightbluebox}
+As already mentioned above, shrinkage priors are a Bayesian approach to dealing with statistical problems in high-dimensional settings.
+The prior is generally constructed for variance selection in sparse state space and TVP models and is named the Triple-Gamma-Prior as its representation is given by three gamma distributions.
+A key advantage of this prior is its unifying property.
+As can be seen in table 1 in \textcite{TGP2020}, special cases of the prior, depending on certain values in its hyperparameters, are the normal-exponential-Gamma, the horseshoe and the double gamma prior.
+In addition, the Bayesian LASSO can be seen as a special case of the triple-gamma-prior.
+Another advantage is its function as a bridge between spike-and-slab and continuous shrinkage prior as the hyperparameters can be used both for steering the shrinkage effect on noise while also preventing overshrinking the signal.
+Computationally the shrinkage prior performs better than commonly used spike-and-slab priors as it is a continuous shrinkage prior which can more easily be implemented using Markov-Chain-Monte-Carlo (MCMC) methods.\\
+
+Mathematically, the prior builds on the work by \textcite{BittoFS2019} in which the authors introduced the \textit{double gamma prior} with the following hierarchical representation:
+
+$$\theta_j|\xi^2_j \sim \mathcal{G}\left(\frac{1}{2}, \frac{1}{2\xi^2_j} \right), \quad \xi^2_j | a^\xi, \kappa^2_B \sim \mathcal{G}\left(a^\xi, \frac{a^\xi\kappa_B^2}{2}\right).$$
+
+It is important to note here, that the \textit{double gamma prior} is a global-local shrinkage prior, where the global hyperparameter $\kappa^2_B$ is the same for all parameters $\theta_j$ and the local hyperparameter $\xi^2_j$ is the local component.
+The \textit{Triple-Gamma-Prior} now adds a third Gamma prior into this framework by replacing $\kappa_B^2$ in the second-level prior with $\kappa_j^2$, which follows
+$$\kappa_j^2 | c^\xi, \kappa_B^2 \sim \mathcal{G}\left(c^\xi, \frac{c^\xi}{\kappa_B^2}\right).$$
+
+The core property which is relevant to this thesis can be found in \textit{Theorem 1 (b)} in \textcite{TGP2020} which shows that the \textit{Triple-Gamma-Prior} has a closed-form marginal prior distribution for the parameter $\theta_j$, or to stick with the terminology of this thesis, $\beta_j$.
+The prior is given by
+$$p(\sqrt{\beta_j}|\phi^\xi, a^\xi, c^\xi) = \frac{\Gamma(c^\xi + \frac{1}{2})}{\sqrt{2\pi \phi^\xi}\cdot B(a^\xi, c^\xi)}\cdot U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right),$$
+where $\phi^\xi = \frac{2c^\xi}{\kappa^2_Ba^\xi}$ and $U(a,b,z)$ is the confluent hyper-geometric function of the second kind of \textcite{Tricomi1947} given by
+$$U(a,b,z) = \frac{1}{\Gamma(a)}\int_0^\infty e^{-zt}t^{a-1}(1+t)^{b-a-1}dt.$$
+
+According to the mathematical connection described above, this prior can now be used to derive a novel regularization penalty.
 
@@
 Coming to the theoretical framework of the \textit{triple-gamma-regularization}, let's assume we have a response variable $y$ and $p$ predictors along with $n$ data points.
-More formally, let $y=[y_1  \quad y_2 \cdots y_n]^T$ and $x_i = [x_{i1} \quad x_{i2} \cdots x_{in}]^T$ with $\forall i\in \{1,...,n\}: y_i, x_i \in \mathbb{R}$.
+More formally, let $y=[y_1  \quad y_2 \cdots y_n]^T$ and $x_i = [x_{i1} \quad x_{i2} \cdots x_{ip}]^T$ with $\forall i\in \{1,...,n\}: y_i, x_{ij} \in \mathbb{R}$.
 Here, $x_i$ is the $i$-th predictor, thus resulting in the design matrix $X = [x_1 \quad x_2 \cdots x_p]$.\\
@@
 \[
-y_i = x_i^T\cdot \beta + \varepsilon_i \quad i\in \{1,...,n\}. 
+y_i = x_i^T\cdot \beta + \varepsilon_i, \quad i\in \{1,...,n\}, 
 \]
@@
 
-As stated above, each data point $y_i$ is assumed to be identically and independently drawn from a normal distribution with mean $X\beta$ and variance $\sigma_i^2$, thus:
+As stated above, each data point $y_i$ is assumed to be independently drawn from a normal distribution with mean $X\beta$ and variance $\sigma^2$, thus:
 \begin{align}
-\mathcal{L}(\mathbf{y}|\beta, \sigma^2, X) 	&= \prod_i^n p(y_i|\beta, \sigma^2, X_i) \nonumber\\
+\mathcal{L}(\mathbf{y}|\beta, \sigma^2, X) 	&= \prod_i^n p(y_i|\beta, \sigma^2, x_i) \nonumber\\
 						&= \prod_i^n \frac{1}{\sqrt{2\pi\sigma^2}} \exp\left(-\frac{1}{2}\left(\frac{x_i-\mu}{\sigma}\right)^2\right) \nonumber\\
@@
 \begin{align*}
-\log \mathcal{L}( \mathbf{y} |\beta, \sigma^2 , \mathbf{X}) &= \log \left( \frac{1}{(2\pi\sigma^2)^{n/2}} \exp\left(-\frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^\top (\mathbf{y} - \mathbf{X}\beta)\right) \right) \\
-&= \log \left( \frac{1}{(2\pi\sigma^2)^{n/2}} \right) + \log \exp\left(-\frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^\top (\mathbf{y} - \mathbf{X}\beta)\right) \\
-&= -\frac{n}{2} \log(2\pi\sigma^2) - \frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^\top (\mathbf{y} - \mathbf{X}\beta)\\
-&\propto - \frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^\top (\mathbf{y} - \mathbf{X}\beta) = - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2.\\
+\log \mathcal{L}( \mathbf{y} |\beta, \sigma^2 , \mathbf{X}) &= \log \left( \frac{1}{(2\pi\sigma^2)^{n/2}} \exp\left(-\frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^T (\mathbf{y} - \mathbf{X}\beta)\right) \right) \\
+&= \log \left( \frac{1}{(2\pi\sigma^2)^{n/2}} \right) + \log \exp\left(-\frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^T (\mathbf{y} - \mathbf{X}\beta)\right) \\
+&= -\frac{n}{2} \log(2\pi\sigma^2) - \frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^T (\mathbf{y} - \mathbf{X}\beta)\\
+&\propto - \frac{1}{2\sigma^2} (\mathbf{y} - \mathbf{X}\beta)^T (\mathbf{y} - \mathbf{X}\beta) = - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2.\\
 \end{align*}
@@
 
-Making use of the monotonicity of the logarithmic function and seeing that it is easier to optimize the log-posterior, Taking the log of the posterior probability distribution, we take the log of result \ref{eq:posterior}.
+Making use of the monotonicity of the logarithmic function and seeing that it is easier to optimize the log-posterior, we take the log of result \ref{eq:posterior}. 
 \begin{align}
@@
 \begin{equation}\label{eq:tgr}
-\hat{\beta}_{MAP} = \underset{\beta \in \mathbb{R}^p}{\argmin} \left(\frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \lambda \sum_j^p -\log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right)\right)
+\hat{\beta}_{MAP} = \underset{\beta \in \mathbb{R}^p}{\argmin} \left(\frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \lambda \sum_j^p -\log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right)\right).
 \end{equation}
@@
 \[
-R(\beta)=\frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2
+R(\beta)=\frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2.
 \] 
@@
 \[
-J_{TG}(\beta) = \sum_j^p -\log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right)
+J_{TG}(\beta) = \sum_j^p -\log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right).
 \]
@@
 Here, the restrictions $a^\xi>0.5$ and $0 < c^\xi < \infty$ are necessary to ensure that the penalty for a $\beta_j$ being equal to zero remains finite and not diverges to negative infinity at zero.
-This results, which has already been presented and proven as part of Theorem 2 in \textcite[5--6]{TGP2020}, ensures that the negative $\log$ of the hypergeometric function remains finite and thus does not produce parameter estimates which are zero for every variables.\\
+This result, which has already been presented and proven as part of Theorem 2 in \textcite[5--6]{TGP2020}, ensures that the negative $\log$ of the hypergeometric function remains finite and thus does not produce parameter estimates which are zero for every variables.\\
 
@@
 Here, it can be seen that as the values for $c^\xi$ become smaller, a shifting effect takes place which generally does not influence the overall structure of the penalty, but increases the amount of penalty which is added to the risk function for $\beta$-values which are different from zero (In a sense, this has a similar effect to changes in $\kappa_B$, which will be explained later).
-Or, to put it differently, with values of $c^\xi$ closer to zero, the data has be become even more convincing that the value is significantly different from zero.\\
+Or, to put it differently, with values of $c^\xi$ closer to zero, the data has be even more convincing that the value is significantly different from zero.\\
 
@@
 \includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInC_Part1.png}
-\caption{Triple-Gamma-Penalty using different values of $c^\xi$ with $c^\xi \geq 0.1$}
+\caption{Triple-Gamma-Penalty using different values of $c^\xi$, with $c^\xi \geq 0.1$}
 \label{fig:ChangeInC_LargeValues}
@@
 
-The third and final hyper-parameter $\kappa_B$ enters the Triple-Gamma-Penalty $J_{TG}(\beta)$ as part of $\phi^\xi = \frac{2c^\xi}{\kappa_B^2 a^\xi}$ as can be seen from equation \ref{eq:tgr}.
+The third and final hyper-parameter $\kappa_B^2$ enters the Triple-Gamma-Penalty $J_{TG}(\beta)$ as part of $\phi^\xi = \frac{2c^\xi}{\kappa_B^2 a^\xi}$ as can be seen from equation \ref{eq:tgr}.
 Notably, $\kappa_B$ is squared and thus only the absolute value of $\kappa_B$, $|\kappa_B|$, influences the structure of the penalty.
@@
 As already mentioned in section \ref{sec:litreview}, several other penalty terms have already been widely studied in the literature.
-Convex penalties like \textit{Ridge} \parencite{HoerlKennard1970a} or non-convex penalties like the \textit{Ar(c)tan} \parencite{WangZhu2016} and \textit{Gaussian} \parencite{JohnVettamWu2022} have managed to establish itself as prominent approaches to regularization.
+Convex penalties like \textit{Ridge} \parencite{HoerlKennard1970a} or non-convex penalties like the \textit{Ar(c)tan} \parencite{WangZhu2016} and \textit{Gaussian} \parencite{JohnVettamWu2022} have managed to establish themselves as prominent approaches to regularization.
 It is now certainly of interest to see how the \textit{Triple-Gamma} penalty compares to the established methods.
 Seeing that, due to its flexibility, there is not \textit{one} \textit{Triple-Gamma} penalty, three distinct hyper-parameter setting have been chosen to represent the proposed penalty term.
-\begin{enumerate}
-\item Setting 1: \quad $a^\xi=0.75$, $c^\xi=0.1$, $\kappa_B = 2$
-\item Setting 2: \quad $a^\xi=5$, $c^\xi=0.01$, $\kappa_B = 2$
-\item Setting 3: \quad $a^\xi=0.51$, $c^\xi=0.001$, $\kappa_B = 1$
-\end{enumerate}
 
-\begin{lightbluebox}
-Describe differences
-\end{lightbluebox}
+\begin{table}[h!]
+\centering
+\begin{tabular}{l|ccc}\toprule
+		& \multicolumn{3}{c}{Hyperparameter} \\\cmidrule(r{4pt}){2-4}
+     	& $a^\xi$  & $c^\xi$ & $\kappa_B$\\\midrule
+Setting 1&	$0.75$	&	$0.1$ &	$2$\\
+Setting 2&	$5$  &   $0.01$ & $2$\\
+Setting 3&  $0.51$  & $0.001$&$1$\\ \bottomrule
+\end{tabular}
+\caption{Three example settings of the \textit{triple-gamma-penalty}}
+\label{tab:TGSettings}
+\end{table}
 
-\begin{figure}[!h]
+A visualisation of these settings can be found in figure \ref{fig:DifferentTGPSettings}.
+It can be seen that all settings differ heavily in its structure and thus its influence on the optimization problem and in the end the resulting parameters.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_DifferentSettings.png}
+\caption{Different settings of the triple-gamma-penalty}
+\label{fig:DifferentTGPSettings}
+\end{figure}
+
+\textit{Setting 1} is a \textit{LASSO} like regularization penalty, but still keeps the non-convex shape of the Triple-Gamma penalty.
+\textit{Setting 2} introduces the smooth-at-origin property but keeps a similar shape than \textit{setting 1} in the tails.
+\textit{Setting 3} has the most distinct structure with a strong singularity at origin but tails which fall of very quickly and thus adds relatively little penalty for parameters that are above $1$ in absolute terms.\\
+
+\begin{figure}[h!]
 \centering
 \includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_Comparison.png}
-\caption{Basic Representation of the Triple-Gamma-Penalty using Hyperparameters $c^\xi = 0.1, \kappa_B = 2, a^\xi = 0.75$ compared to \textit{LASSO} and \textit{Ridge} Penalties}
+\caption{Basic representation of the triple-gamma-penalty using hyperparameters $c^\xi = 0.1, \kappa_B = 2, a^\xi = 0.75$ compared to \textit{LASSO} and \textit{ridge} penalties}
 \label{fig:DifferentPenalties}
@@
 \newpage
-\section{Simulation Study}
+\section{Simulation Study}\label{sec:simstudy_overall}
 To test the proposed method of section \ref{sec:modelderivation} a simulation study will now be conducted whether, and if so, in what scenarios, the \textit{Triple-Gamma} penalty might be valuable addition to the literature.
 Of course several previously introduced methods have also been tested using simulation studies, but the methodology behind these studies usually varies from paper to paper.
-However, before moving on to this section of the thesis, the question remains on how to solve the optimization problem in \ref{eq:tgr}.
+However, before moving on to this section of the thesis, the question remains on how to solve the optimization problem in equation \ref{eq:tgr}.
 
@@
 As already mentioned in chapter \ref{sec:litreview}, non-convex penalties like the \textit{Triple-Gamma} penalty are usually harder to solve than convex optimization problems.
-The reason being that convex functions have a unique global minimum, whereas non-convex functions can have multiple local minima, which are not necessarily a global minimum.
-\textbf{(SOURCE)}.
+The reason being that convex functions have a unique global minimum, whereas non-convex functions can have multiple local minima, which are not necessarily a global minimum \parencite{GrippoSciandrone2023}.
 In addition, unlike for example \textit{Ridge} regression, the \textit{Triple-Gamma} penalty like many other established penalties in the literature does not have a closed form solution for this optimization problem.
@@
 Another method is called \textit{Stochastic Gradient Descent (SGD)} and uses different batches of the dataset to estimate the model parameters \parencite{Amari1993}.
-The \textit{Gradient Descent} method will be used for the simulation study in the following chapter.\\
+The \textit{Stochastic Gradient Descent} method will be used for the simulation study in the following chapter.\\
 
@@
 The model is fitted on the training dataset and then tested on the test dataset using a metric like the \textit{mean squared error (MSE)}.
-\textit{Variable Selection} is measured in various ways.
-\textcite{WangEtAl2020} used \textit{true-positive} and \textit{false-positive} rates as their metric of choice.
-As several of the tested methods in this simulation study do not perform variable selection naturally due to its \textit{smooth-at-origin} property and thus report estimates larger than zero, a different metric will be chosen for this simulation study.
-To test whether models accurately predict the underlying data generating process and also result in estimates close to its true coefficients, the square of the absolute deviation between the true coefficient and the estimated coefficient of each variable will be computed and summed up.
-Using this metric, models whose estimates are close the true coefficients will perform than models whose estimates are far off.\\
-
 To evaluate the models in a wide range of contexts, every simulation scenario will vary in terms off three variables: \textit{sample size $N$} (ie $N=100$ meaning that for every run, a total of $100$ observations will be generated), \textit{dimensionality $p$} (ie $p=10$ meaning a total of ten covariates will included in the model) and \textit{sparsity $s$} (ie $s=0.1$ meaning that 10\% of the covariates have a true coefficients different from zero).
 The set of values chosen for each scenario variable can be found in table \ref{tab:Scenarios}.
-Using this values, all possible combinations of these variable settings will be formed, resulting in a total of $48$ possible scenarios.
+Using these values, all possible combinations of these variable settings will be formed, resulting in a total of $27$ possible scenarios.
 
@@
 Variable & Values\\\midrule
-Sample Size $N$ & $50, 100, 500, 1000$\\
-Dimensionality $p$ & $3, 10, 40$\\
-Sparsity $s$ & $0.1, 0.3, 0.5, 0.9$\\\bottomrule
+Sample Size $N$ & $10, 100, 250$\\
+Dimensionality $p$ & $10, 25, 50$\\
+Sparsity $s$ & $0.1, 0.5, 0.9$\\\bottomrule
 \end{tabular}
@@
 A grid of possible values for $\lambda$ is chosen, the model is being estimated for every possible value, and the best model will be chosen based on the chosen cross-validation metric.
-For this simulation study, all values between $0$ and $1$ based on $0.01$ steps will be tested.
+After this run, these optimal values will be used in the overall simulation.
+For the application of the gradient descent algorithm a maximum number of 500 epochs has been set.
 The simulations have been run with Python (Version 3.11.4) along with scikit-learn (Version 1.4.1.post1) and PyTorch (Version 2.2.2).\footnote{More information on the packages used and its installed version can be found in the accompanying GitHub repository.}
 
-\subsection{Simulation Study for Prediction}
+\subsection{Simulation Results}
 
-\subsection{Simulation Study for Variable Selection}
+For the simulation study testing the models prediction accuracy the key metric to test performance will be the \textit{mean-squared-error (MSE)}.
+The data is being generated the following way: Given a set of scenario parameters $N_i$, $p_i$ and $sd_i$, the first $s_i*p_i$ coefficients, rounded to the next larger integer, will be set to $3$ and the remaining will be set to $0$.
+Then, $N_i$ draws will be generated from a normal distribution with mean $0$ and variance $1$ for each of the $p_i$ features.
+Using these coefficients and the data from the features a response variable $y$ will be computed and noise generated from a normal distribution with mean $0$ and variance $\sigma_i$.
+According to \textcite{WangEtAl2020}, the respective $\sigma_i$ will be computed based on the \textit{Signal-To-Noise Ration (SNR)}.
+The \textit{SNR} is given by $SNR = \sqrt{\beta^TX^TX\beta/(N_i\sigma_i^2)}$ and by setting the \textit{SNR} to a specific value, one can adjust how strong the noise in the data is relative to the sound of the actual data generating process.
+For the purpose of this study, and similar to \textcite{WangEtAl2020}, a \textit{SNR} equal to one will be used.
+In terms of the regularization parameter $\lambda$, the search for the optimal $\lambda$ will be performed by using five-fold-cross-validation on the a set of possible $\lambda$ values.
+For every method and every run in every scenario separately, the optimal $\lambda^*_i$ will be chosen which generates the lowest validation loss on the testset.
+This grid-serach procedure will be performed for every $\lambda_i \in \{0.001, 0.01, 0.1, 0.25, 0.4, 0.5, 0.6, 0.75, 0.9, 0.95\}$.\\
+
+Using the set of scenario variables mentioned in table \ref{tab:Scenarios}, all possible combinations will be formed resulting in the overall $27$ scenarios.\footnote{Note: Due to the computational constraints of hardware used for this simulation  and several other issues, not all 27 scenarios were estimated in one run, but rather in several separate runs.
+More information on the exact procedure to ensure reproducibility can be found in the relevant script on \href{https://github.com/therealLucasPaul/MScThesis_Econ}{GitHub}.} The code iterates through the list of scenarios, generates 15 datasets based on these scenarios variables and all methods will be estimated on the test part of these datasets.
+Afterwards, the validation loss will be computed for each method and stored.
+This procedure results in table \ref{tab:PredSim}, which shows the mean and standard deviation of the distribution of the validation loss for every scenario and every method.
+Before advancing to the overall results of this simulation study and its interpretation, it might be useful to have a look at a specific scenario to better understand the results in table \ref{tab:PredSim}, which will be the scenario with $N=250, p=25, s=0.9$.\\
+
+In this scenario, we are dealing with a dataset of $250$ observations, $25$ features and $23$ non-zero coefficients.\footnote{$25 \times 0.9 = 22.5$, which is then rounded up to $23$.} A figure with boxplots showcasing the distributions of the Mean-Squared-Error rates on the validation set for all methods can be found in figure \ref{fig:SpecificScenario1}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.6]{../02_simulation/021_simulation_figures/Boxplot_Scenario_250_25_23.png}
+\caption{Distribution of MSE on validation set in the scenario with $250$ observations, $25$ features and $23$ non-zero coefficients}
+\label{fig:SpecificScenario1}
+\end{figure}
+
+This scenario, which is a good example for a dense scenario, where a lot of features are in the dataset and a major part of it is different from zero, i.e.
+has an effect on the outcome.
+Here, setting 1 of the \textit{Triple-Gamma-Penalty} performs best as it manages to produce the smallest mean in loss with about $291.426$.
+All other methods perform as good as or slightly better than the regular \textit{OLS} approach.
+A second scenario can be found in figure \ref{fig:SpecificScenario2}, where the scenario with $100$ observations, $50$ features and $25$ non-zero features is shown.
+Here, again the setting 1 of the \textit{Triple-Gamma-Penalty} seems to do best when it comes to the lowest mean \textit{MSE}.\\
+\vfill
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.6]{../02_simulation/021_simulation_figures/Boxplot_Scenario_100_50_25.png}
+\caption{Distribution of MSE on Validation Set in the Scenario with $100$ Observations, $50$ Features and $25$ non-zero Coefficients}
+\label{fig:SpecificScenario2}
+\end{figure}
+
+An overview of the basic results for each of the $27$ scenarios can be found in table \ref{tab:bestmethod}.
+In the left half of the table the scenario parameters are presented and in the right half the best method based on the method having the lowest mean as well as median validation loss.
+In general, the results confirm the results from \textcite{WangEtAl2020} that no go-to method in regularization has been found.
+In terms of the mean loss, Setting 1 and 2 of the \textit{Triple-Gamma-Penalty} as well as the \textit{Gaussian} approach seem to work well.
+Setting 3 of the \textit{Triple-Gamma-Penalty} only comes out on top in two scenarios.
+\textit{LASSO} only manages to perform best in one scenario when using the median loss as the method of comparison.
+\textit{Arctan} interestingly never performs best when it comes to the lowest mean loss, but shows up a few times in the median column.
+The \textit{OLS} approach, hence a regularization parameter of $\lambda = 0$ performs best in a few of the scenarios with sample size $10$, however seeing that these scenarios are trying to estimate $25$ and $50$ parameters based on ten samples, these results are suffering from high variance and thus should not be taken too serious.
+As previously mentioned, a table with the means and standard deviations of all methods in all scenarios can be found in table \ref{tab:PredSim}.
+
+\begin{table}[h!]
+\begin{tabular}{ccc|l|l}
+\toprule
+\multicolumn{3}{c}{Scenario Parameters} & \multicolumn{2}{c}{Moment}\\
+\midrule
+Samples & Features & Non-Zero Features & Best Method (Mean) & Best Method (Median) \\
+\midrule
+10 & 10 & 1 & TGR Setting 2 & TGR Setting 2 \\
+10 & 10 & 5 & TGR Setting 2 & TGR Setting 2 \\
+10 & 10 & 9 & Gaussian & Arctan \\
+10 & 25 & 3 & TGR Setting 1 & Arctan \\
+10 & 25 & 13 & TGR Setting 2 & Gaussian \\
+10 & 25 & 23 & OLS & TGR Setting 3 \\
+10 & 50 & 5 & TGR Setting 1 & Arctan \\
+10 & 50 & 25 & OLS & Gaussian \\
+10 & 50 & 45 & OLS & TGR Setting 2 \\
+100 & 10 & 1 & Gaussian & LASSO \\
+100 & 10 & 5 & TGR Setting 1 & TGR Setting 1 \\
+100 & 10 & 9 & OLS & Arctan \\
+100 & 25 & 3 & Gaussian & Gaussian \\
+100 & 25 & 13 & Ridge & TGR Setting 1 \\
+100 & 25 & 23 & TGR Setting 1 & TGR Setting 1 \\
+100 & 50 & 5 & Gaussian & Arctan \\
+100 & 50 & 25 & TGR Setting 1 & TGR Setting 1 \\
+100 & 50 & 45 & Ridge & Arctan \\
+250 & 10 & 1 & Gaussian & LASSO \\
+250 & 10 & 5 & TGR Setting 2 & OLS \\
+250 & 10 & 9 & TGR Setting 1 & TGR Setting 2 \\
+250 & 25 & 3 & Gaussian & Arctan \\
+250 & 25 & 13 & TGR Setting 1 & TGR Setting 2 \\
+250 & 25 & 23 & TGR Setting 1 & TGR Setting 1 \\
+250 & 50 & 5 & TGR Setting 2 & Gaussian \\
+250 & 50 & 25 & TGR Setting 3 & OLS \\
+250 & 50 & 45 & TGR Setting 3 & Ridge \\
+\bottomrule
+\end{tabular}
+\caption{Table showing the best performing methods according to smallest Mean and Median Loss accordingly}
+\label{tab:bestmethod}
+\end{table}
+
+Generally, it can be said that certain settings of the \textit{Triple-Gamma-Penalty} can indeed perform better than the existing methods in this specific scenarios.
+However, not a single setting seems to outperform the other settings over a broad range of scenarios.
+
+\newpage
+\subsection{Computational Efficiency}
+At this point of the thesis it is necessary to quickly cover the topic of computational efficiency.
+As mentioned earlier, this simulation study has been implemented using Python along with PyTorch on a local system.\footnote{The technical specifications of this system can be found in the Appendix.} As the \textit{Triple-Gamma} penalty is not a simple algebraic computation, as for example computing the absolute value of a real number in the case of \textit{LASSO} or computing the arctangent in the case of the \textit{Arctan} penalty, it is apparent that the computation of the loss function given a set of parameters is not very straight-forward and computationally expensive.
+In its current implementation, the Python function computing the \textit{Triple-Gamma-Loss} has to access a second function which approximates the logarithm of the confluent hyper-geometric  function of the second kind.
+More importantly, it does so for every parameter in the model.
+This is, to no surprise, very inefficient and makes computations in high dimensions unnecessarily complicated and time-intensive.
+In figure \ref{fig:ComputationTime} a plot can be found which shows the time to estimate all three settings of the \textit{Triple-Gamma-Regularization} on a dataset generated with parameters $N=100$ and $s=0.1$ and an increasing number of features $p$.\\
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.6]{../02_simulation/021_simulation_figures/ComputationTime_Example.png}
+\caption{Time necessary to compute all three scenarios of the Triple-Gamma-Regularization with $N=100$ and $s=0.1$ dependent on the number of Features $p$}
+\label{fig:ComputationTime}
+\end{figure}
+
+As can be seen from figure \ref{fig:ComputationTime} above, the time to estimates these models increases drastically with an increased number of variables.
+Setting aside that it might even grow exponentially, it can be seen that the computation time also increasingly becomes more unstable.
+Several approaches might help in resolving these issues, like optimizing the underlying approximation of the confluent hypergeometric funciton or choosing a different estimation algorithm altogether (see section 6.1).
+Another approach could be to implement the underlying estimation in a more efficient programming language when it comes to runtime like C++.
+All in all, this definitely opens up a field for further research to make the overall method more suitable for application.
+\\
+
+It is also worth noting that the computational efficiency of the \textit{Triple-Gamma-Penalty} still relies on the specification of the penalty itself.
+\textit{Setting 2} for example with its very \textit{smooth-at-origin} behaviour takes significantly longer to compute compared to its \textit{singular-at-origin} specifications in \textit{setting 1} and \textit{setting 3}.
+A plot showcasing these differences can be found in figure \ref{fig:ComputationTimeSettings} below.
+For an specific scenario, in this case with 100 samples, 10 features and one non-zero feature, 25 runs have been computed and timed.
+It can clearly be seen that settings 1 and 2 usually take about 2.5 seconds to estimate, whereas the \textit{smooth-at-origin} specification takes about 6 seconds on average.
+This disparity increases with an increasing number of features.
+All in all, this is an open issues which needs to be studied further to increase practicability in real-world applications.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.6]{../02_simulation/021_simulation_figures/ComputationTime_Different_Settings.png}
+\caption{Distribution of computation time for different settings of the TGR (Samples: 100, Features: 10, Non-zero Features: 1, 500 runs)}
+\label{fig:ComputationTimeSettings}
+\end{figure}
+
+\begin{landscape}
+\begin{longtable}{lllllllllllrrrrrrrr}
+
+\caption{Mean and Standard Deviations of MSE on the Validation Set for different Scenarios (15 runs per scenario)} \\
+\toprule
+\makecell{\textbf{Sample} \\ \textbf{Size}} & \makecell{\textbf{Features}} & \makecell{\textbf{Non-zero} \\ \textbf{Features}} & \makecell{\textbf{OLS}} & \makecell{\textbf{LASSO}} & \makecell{\textbf{Ridge}} &  \makecell{\textbf{Arctan}} & \makecell{\textbf{Gaussian}} & \makecell{\textbf{TGR} \\ \textbf{Setting 1}} & \makecell{\textbf{TGR} \\ \textbf{Setting 2}} & \makecell{\textbf{TGR} \\ \textbf{Setting 3}}\\
+\midrule
+\endfirsthead
+
+\midrule \multicolumn{11}{r}{{Continued on next page}} \\
+\endfoot
+
+\endlastfoot
+
+\multicolumn{11}{c}{{\tablename\ \thetable{} -- continued from previous page}} \\
+\toprule
+\makecell{\textbf{Sample} \\ \textbf{Size}} & \makecell{\textbf{Features}} & \makecell{\textbf{Non-zero} \\ \textbf{Features}} & \makecell{\textbf{OLS}} & \makecell{\textbf{LASSO}} & \makecell{\textbf{Ridge}}  & \makecell{\textbf{Arctan}} & \makecell{\textbf{Gaussian}} & \makecell{\textbf{TGR} \\ \textbf{Setting 1}} & \makecell{\textbf{TGR} \\ \textbf{Setting 2}} & \makecell{\textbf{TGR} \\ \textbf{Setting 3}}\\
+\midrule
+\endhead
+
+\midrule
+\multirow[t]{9}{*}{10} & \multirow[t]{3}{*}{10} & 1 & \makecell{12.746 \\ (14.993)} & \makecell{7.163 \\ (5.372)} & \makecell{8.589 \\ (5.595)} & \makecell{9.551 \\ (13.523)} & \makecell{6.751 \\ (6.217)} & \makecell{7.722 \\ (4.92)} & \makecell{5.348 \\ (3.151)} & \makecell{6.663 \\ (4.127)} \\
+ &  & 5 & \makecell{83.12 \\ (59.984)} & \makecell{84.273 \\ (62.912)} & \makecell{81.288 \\ (53.656)} & \makecell{85.04 \\ (61.694)} & \makecell{84.585 \\ (66.75)} & \makecell{80.645 \\ (51.107)} & \makecell{79.03 \\ (50.777)} & \makecell{89.188 \\ (57.828)} \\
+ &  & 9 & \makecell{220.161 \\ (360.491)} & \makecell{224.464 \\ (365.323)} & \makecell{221.269 \\ (354.385)} & \makecell{219.74 \\ (356.702)} & \makecell{219.399 \\ (354.232)} & \makecell{228.631 \\ (356.692)} & \makecell{219.837 \\ (355.328)} & \makecell{239.05 \\ (335.249)} \\
+\cline{2-11}
+ & \multirow[t]{3}{*}{25} & 3 & \makecell{50.664 \\ (49.508)} & \makecell{44.771 \\ (34.833)} & \makecell{44.945 \\ (40.545)} & \makecell{48.249 \\ (40.413)} & \makecell{53.057 \\ (40.557)} & \makecell{37.565 \\ (31.623)} & \makecell{37.675 \\ (29.551)} & \makecell{38.136 \\ (32.025)} \\
+ &  & 13 & \makecell{235.981 \\ (256.182)} & \makecell{234.756 \\ (260.716)} & \makecell{238.259 \\ (261.011)} & \makecell{235.193 \\ (259.992)} & \makecell{237.285 \\ (267.622)} & \makecell{233.065 \\ (251.616)} & \makecell{231.373 \\ (249.771)} & \makecell{261.546 \\ (311.695)} \\
+ &  & 23 & \makecell{657.683 \\ (927.439)} & \makecell{663.27 \\ (948.327)} & \makecell{682.629 \\ (969.617)} & \makecell{663.035 \\ (950.083)} & \makecell{665.583 \\ (950.939)} & \makecell{684.95 \\ (986.148)} & \makecell{661.124 \\ (931.974)} & \makecell{707.196 \\ (1055.199)} \\
+\cline{2-11}
+ & \multirow[t]{3}{*}{50} & 5 & \makecell{85.213 \\ (65.938)} & \makecell{86.522 \\ (63.037)} & \makecell{87.626 \\ (64.062)} & \makecell{82.807 \\ (61.584)} & \makecell{92.967 \\ (67.136)} & \makecell{72.882 \\ (52.811)} & \makecell{86.194 \\ (62.525)} & \makecell{73.482 \\ (55.999)} \\
+ &  & 25 & \makecell{380.704 \\ (348.464)} & \makecell{393.886 \\ (369.79)} & \makecell{383.191 \\ (358.369)} & \makecell{387.278 \\ (362.043)} & \makecell{385.417 \\ (362.873)} & \makecell{385.333 \\ (347.936)} & \makecell{400.293 \\ (356.349)} & \makecell{407.237 \\ (380.271)} \\
+ &  & 45 & \makecell{586.161 \\ (509.473)} & \makecell{595.584 \\ (502.119)} & \makecell{587.042 \\ (503.356)} & \makecell{589.93 \\ (516.23)} & \makecell{595.248 \\ (517.682)} & \makecell{628.681 \\ (532.073)} & \makecell{599.853 \\ (516.79)} & \makecell{625.393 \\ (567.819)} \\
+\cline{1-11} \cline{2-11}
+\multirow[t]{9}{*}{100} & \multirow[t]{3}{*}{10} & 1 & \makecell{9.424 \\ (3.128)} & \makecell{9.053 \\ (3.351)} & \makecell{9.395 \\ (3.177)} & \makecell{8.864 \\ (3.296)} & \makecell{8.679 \\ (2.888)} & \makecell{9.503 \\ (3.212)} & \makecell{8.691 \\ (3.022)} & \makecell{9.393 \\ (3.125)} \\
+ &  & 5 & \makecell{57.358 \\ (18.573)} & \makecell{56.949 \\ (18.757)} & \makecell{57.351 \\ (18.811)} & \makecell{56.565 \\ (18.628)} & \makecell{57.245 \\ (18.709)} & \makecell{55.015 \\ (18.942)} & \makecell{57.423 \\ (19.208)} & \makecell{56.856 \\ (18.704)} \\
+ &  & 9 & \makecell{116.117 \\ (44.899)} & \makecell{117.717 \\ (46.085)} & \makecell{116.924 \\ (45.616)} & \makecell{116.152 \\ (45.468)} & \makecell{116.713 \\ (47.097)} & \makecell{118.196 \\ (46.824)} & \makecell{117.065 \\ (45.264)} & \makecell{117.579 \\ (45.929)} \\
+\cline{2-11}
+ & \multirow[t]{3}{*}{25} & 3 & \makecell{32.254 \\ (13.184)} & \makecell{30.553 \\ (11.05)} & \makecell{33.468 \\ (13.544)} & \makecell{30.841 \\ (12.644)} & \makecell{29.089 \\ (12.183)} & \makecell{32.741 \\ (12.647)} & \makecell{29.98 \\ (12.085)} & \makecell{33.19 \\ (13.086)} \\
+ &  & 13 & \makecell{174.105 \\ (74.371)} & \makecell{174.086 \\ (71.812)} & \makecell{172.684 \\ (72.5)} & \makecell{174.514 \\ (75.149)} & \makecell{173.975 \\ (72.858)} & \makecell{173.319 \\ (71.67)} & \makecell{175.257 \\ (72.028)} & \makecell{174.474 \\ (73.942)} \\
+ &  & 23 & \makecell{372.536 \\ (119.118)} & \makecell{375.219 \\ (122.728)} & \makecell{372.548 \\ (119.272)} & \makecell{374.19 \\ (121.703)} & \makecell{374.707 \\ (121.828)} & \makecell{370.122 \\ (124.796)} & \makecell{375.738 \\ (122.027)} & \makecell{371.922 \\ (119.823)} \\
+\cline{2-11}
+ & \multirow[t]{3}{*}{50} & 5 & \makecell{74.46 \\ (21.745)} & \makecell{71.822 \\ (21.782)} & \makecell{73.924 \\ (20.749)} & \makecell{72.343 \\ (21.084)} & \makecell{68.12 \\ (22.565)} & \makecell{73.804 \\ (20.536)} & \makecell{69.25 \\ (23.649)} & \makecell{75.756 \\ (20.395)} \\
+ &  & 25 & \makecell{419.029 \\ (150.3)} & \makecell{420.748 \\ (149.616)} & \makecell{420.585 \\ (151.05)} & \makecell{418.464 \\ (150.909)} & \makecell{422.38 \\ (149.169)} & \makecell{414.026 \\ (162.605)} & \makecell{419.259 \\ (150.257)} & \makecell{430.39 \\ (174.063)} \\
+ &  & 45 & \makecell{660.425 \\ (219.371)} & \makecell{658.744 \\ (221.85)} & \makecell{657.582 \\ (220.248)} & \makecell{659.611 \\ (220.094)} & \makecell{661.732 \\ (220.315)} & \makecell{661.103 \\ (225.032)} & \makecell{662.506 \\ (222.481)} & \makecell{661.674 \\ (217.426)} \\
+\cline{1-11} \cline{2-11}
+\multirow[t]{9}{*}{250} & \multirow[t]{3}{*}{10} & 1 & \makecell{8.797 \\ (1.74)} & \makecell{8.692 \\ (1.599)} & \makecell{8.825 \\ (1.708)} & \makecell{8.673 \\ (1.656)} & \makecell{8.661 \\ (1.674)} & \makecell{8.77 \\ (1.741)} & \makecell{8.669 \\ (1.667)} & \makecell{8.773 \\ (1.726)} \\
+ &  & 5 & \makecell{48.357 \\ (7.664)} & \makecell{48.502 \\ (7.806)} & \makecell{49.367 \\ (7.531)} & \makecell{48.327 \\ (7.523)} & \makecell{47.985 \\ (7.308)} & \makecell{47.944 \\ (7.69)} & \makecell{47.939 \\ (7.505)} & \makecell{48.215 \\ (7.747)} \\
+ &  & 9 & \makecell{95.877 \\ (23.697)} & \makecell{96.414 \\ (24.141)} & \makecell{95.621 \\ (23.726)} & \makecell{96.268 \\ (23.569)} & \makecell{97.287 \\ (23.637)} & \makecell{95.458 \\ (23.909)} & \makecell{96.026 \\ (23.563)} & \makecell{96.794 \\ (22.755)} \\
+\cline{2-11}
+ & \multirow[t]{3}{*}{25} & 3 & \makecell{30.641 \\ (7.932)} & \makecell{29.895 \\ (6.621)} & \makecell{31.892 \\ (7.391)} & \makecell{29.45 \\ (7.185)} & \makecell{28.34 \\ (5.67)} & \makecell{29.621 \\ (7.539)} & \makecell{28.742 \\ (6.161)} & \makecell{30.599 \\ (7.725)} \\
+ &  & 13 & \makecell{157.836 \\ (45.342)} & \makecell{158.001 \\ (44.129)} & \makecell{157.34 \\ (44.617)} & \makecell{156.739 \\ (44.256)} & \makecell{157.788 \\ (44.235)} & \makecell{154.68 \\ (46.043)} & \makecell{157.53 \\ (45.347)} & \makecell{157.915 \\ (44.678)} \\
+ &  & 23 & \makecell{298.676 \\ (60.928)} & \makecell{299.437 \\ (60.018)} & \makecell{299.121 \\ (60.275)} & \makecell{299.933 \\ (60.418)} & \makecell{298.27 \\ (60.256)} & \makecell{291.426 \\ (54.161)} & \makecell{299.305 \\ (61.564)} & \makecell{298.262 \\ (60.842)} \\
+\cline{2-11}
+ & \multirow[t]{3}{*}{50} & 5 & \makecell{58.478 \\ (8.895)} & \makecell{56.326 \\ (8.352)} & \makecell{60.041 \\ (8.732)} & \makecell{55.643 \\ (8.258)} & \makecell{52.592 \\ (8.083)} & \makecell{58.55 \\ (9.343)} & \makecell{52.532 \\ (8.209)} & \makecell{59.195 \\ (8.924)} \\
+ &  & 25 & \makecell{352.75 \\ (70.694)} & \makecell{353.179 \\ (72.004)} & \makecell{352.526 \\ (71.89)} & \makecell{353.512 \\ (72.101)} & \makecell{353.35 \\ (71.954)} & \makecell{352.349 \\ (72.133)} & \makecell{352.161 \\ (68.27)} & \makecell{352.072 \\ (71.796)} \\
+ &  & 45 & \makecell{664.144 \\ (133.001)} & \makecell{663.053 \\ (131.957)} & \makecell{661.547 \\ (129.346)} & \makecell{663.788 \\ (128.434)} & \makecell{666.384 \\ (130.161)} & \makecell{663.345 \\ (131.016)} & \makecell{665.715 \\ (130.906)} & \makecell{660.788 \\ (128.093)} \\
+\cline{1-11} \cline{2-11}
+\bottomrule
+\label{tab:PredSim}
+\end{longtable}
+\end{landscape}
+
+%\subsection{Simulation Study for Variable Selection}
+
+%As described in the introductory part of this section, the variable selection part of the simulation study will explore how accurately specific models can estimate the underlying data generating process without worrying about predictive power on a test dataset.
+Thus, no validation set will be used to measure performance, but rather the deviation of the estimated coefficients to the true data generating coefficients.
+To showcase this overall procedure, the scenario
 
 \subsection{Implementation as Python Package}
+As mentioned before, this simulation study has been run using Python (Version 3.11.4) along with scikit-learn (Version 1.4.1.post1) and PyTorch (Version 2.2.2).
+The accompanying code, a list of packages used and its version and other material can be found on \href{https://github.com/therealLucasPaul/MScThesis_Econ}{GitHub}.
+The script \textit{tgr.py} can be used as a script to apply \textit{Triple-Gamma-Regularization} on a dataset of choice.
+To make its application easier, the following subsections provides important information on how to use it.
 
-This section provides a brief overview of the Python script, which has been used to run the simulations of the previous section, along with input/output descriptions of the defined functions.
-\begin{lightbluebox}
-How to use it. 
-Explanation of Functions. Input - Output Tables
-\end{lightbluebox}
+\subsubsection*{General Functions}
 
-\subsection{Computational Performance}
-Talking about Gradient Descent Methods in more depth. Why Gradient Clipping. Maybe more modern estimation techniques?
+\begin{longtable}{|p{4cm}|p{9cm}|}
+\hline
+\textbf{Function Name} & \textbf{Description} \\
+\hline
+\endfirsthead
 
-See how computation times change when increasing the size of the data set or when the number of parameter changes. => Use Stochastic Gradient Descent (SGD)
+\hline
+\textbf{Function Name} & \textbf{Description} \\
+\hline
+\endhead
 
-\begin{lightbluebox}
-Kurzes Ansprechen von Computations Efficieny
-\end{lightbluebox}
+\hline
+\endfoot
 
-\section{Possible Extensions and Criticism}
+\hline
+\endlastfoot
 
-\begin{lightbluebox}
-Interessante unifying properties, aber langsam implementiert. 
-\end{lightbluebox}
+\makecell{\texttt{TripleGamma-}\\\texttt{Regularization}} & Here a class is defining a simple neural network.
+It uses the \texttt{nn.Module} and initializes a linear model with 10 input features and 1 output feature without an intercept.
+\\
+\hline
+	\texttt{TripleGammaReg\_Loss} & This function computes the loss for the Triple Gamma Regularization.
+It takes the predicted values (\texttt{Y\_HAT}), the true values (\texttt{Y}), the coefficients of the model (\texttt{coefficients}), the regularization parameter (\texttt{lamda}), and the regularization parameters \texttt{a}, \texttt{c} and \texttt{kappa} as input.
+The loss is computed according to the theoretical formulation by using the script \texttt{log\_hyperu.py}, which approximates the log of the confluent hyper-geometric function of the second kind.
+\\
+\hline
+\texttt{TripleGammaModel} & This function trains the \textit{Triple-Gamma} Regularization model.
+It takes the feature matrix (\texttt{X}), the target values (\texttt{y}), the regularization parameter (\texttt{penalty}), regularization hyper-parameters \texttt{a}, \texttt{c}, \texttt{kappa}, the number of epochs (\texttt{num\_epochs}), and the learning rate (\texttt{lr}) as input.
+It initializes the \texttt{PyTorch} model and optimizer, uses Gradient Descent to train the model for the specified number of epochs, and returns the trained model, a list of model coefficients for each epoch, and a list of loss values for each epoch.\\
+\hline
+\end{longtable}
+
+\subsubsection*{Dependencies}
+To successfully run the script, the following dependencies are required:
+\begin{itemize}
+    \item \texttt{torch}: PyTorch library including sub modules \texttt{torch.nn} and \texttt{torch.optim} for building and training neural networks with at least version 2.2.2
+    \item \texttt{log\_hyperu as hyperu}: The custom module for computing the logarithm of the hypergeometric function, which can be found on GitHub.
+\end{itemize}
+
+\subsubsection*{Data Types of Inputs and Outputs of the Functions}
+\begin{itemize}
+  	\item \texttt{TripleGammaModel}
+    \begin{itemize}
+        \item \textbf{Input:} \texttt{X} (Tensor), \texttt{y} (Tensor), \texttt{penalty} (float), \texttt{a} (float), \texttt{c} (float), \texttt{kappa} (float), \texttt{num\_epochs} (int, default=1000), \texttt{lr} (float, default=0.01)
+        \item \textbf{Output:} \texttt{model} (Initialization of the class TripleGammaRegularization), \texttt{coef\_list} (list of Tensors), \texttt{loss\_list} (list of Tensors)
+    \end{itemize}
+\end{itemize}
+
+\section{Possible Extensions and Criticism}\label{sec:crit}
+The \textit{Triple-Gamma-Penalty} in its current form is very rudimentary and leaves plenty space for further scientific research and simulations.
+The three settings of the penalty given in figure \ref{fig:DifferentTGPSettings} are examples of how the penalty could be used and are showcasing its flexibility by using different hyperparamters.
+Nonetheless, having highlighted some of the advantages of using the \textit{Triple-Gamma-Regularization} approach in previous chapters, it is only reasonable to mention some of the downsides of it compared to methods in the existing body of literature as well.
+First, the introduced flexibility comes at the cost of mathematical simplicity.
+Existing methods like \textit{LASSO} and \textit{Ridge} still have the upper hand in practical applications due to its remarkable mathematical simplicity.
+Even more modern methods like \textit{Gaussian} or \textit{Arctan} regularization, which still only use rudimentary mathematical components, have troubles with establishing themselves as viable alternatives in practical application.
+It remains to be seen if the advantages of the \textit{Triple-Gamma} penalty outweigh its obvious downsides in this regard.
+Second, as statistical models become increasingly more extensive in the age of AI, computational efficiency, even though computational power has increased as well in recent decades, still remains an issue of utmost importance.
+This surely is a problem which needs to be solved or at least handled in an appropriate manner to make the method more viable.\\
+
+On the upside, these shortcomings still leave room for improvement and further research.
+Most importantly it will be important to explore the viability of the \textit{Triple-Gamma} penalty in other simulation settings and in different contexts.
+For example, more scenarios can be analysed with different data generating processes.
+In addition, these simulations can use more runs and more iterations in its estimation process to gain more robust results.
+As previously mentioned, an entire new estimation algorithm could be used as well to not only make the results more robust but possibly also solve the issue of computational efficiency.
+Another field of further research could explore more possibilities in the area of setting the hyperparameters.
+The three settings used in this thesis only represent a small subgroup of possible penalty structures that the \textit{Triple-Gamma} penalty can take on.
+A more extensive analysis of these settings or even a possible hands-off approach to setting these values could open up an entire new field of applications.
+Lastly, the \textit{Triple-Gamma} penalty has only been applied to a linear model setup, which is commonly used when dealing with cross-sectional data.
+As the variety of statistical models has increased in recent decades, it might also be interesting to see how this penalty applies to neural network scenarios or even time series problems.
+
 \section{Conclusion}
-\subsection{Implementation as Python Package}
-\begin{lightbluebox}
-ENDE
-\end{lightbluebox}
+
+This thesis introduced the \textit{Triple-Gamma Regularization (TGR)}, a novel non-convex penalty inspired by the Triple-Gamma Prior developed by \textcite{TGP2020}.
+This new regularization method bridges existing convex approaches like LASSO with newer non-convex penalties such as Arctan and Gaussian, offering increased flexibility in addressing the challenges of underfitting and overfitting in high-dimensional regression settings.
+The theoretical foundation of TGR was derived by leveraging the mathematical connection between frequentist regularization techniques and Bayesian shrinkage priors.
+Through this connection, a penalty structure was derived which allows for a more flexible tuning of hyperparameters to achieve a balance between bias and variance.
+The flexibility of TGR lies in its three hyperparameters, which control the behaviour of the penalty structure at both the origin and the tails.
+This allows it to handle scenarios where existing penalties may fall not sufficiently solve problems.\\
+
+A key feature of \textit{TGR} is its ability to perform both continuous shrinkage and variable selection, making it a versatile alternative in high-dimensional data analysis.
+Compared to existing regularization methods, such as LASSO and Ridge, \textit{TGR} offers the advantage of a more refined approach to penalization.
+This was supported by the simulation study conducted, which demonstrated that TGR performs competitively across a variety of high-dimensional settings, sometimes even outperforming conventional methods in terms of mean-squared error reduction.
+Downsides include the computational challenges posed by non-convex optimization problems, which are inherent in methods like \textit{TGR}.
+While the results presented here suggest that the \textit{Triple-Gamma} penalty is a promising addition to the regularization literature, it does not come without limitations.
+The penalty’s performance heavily depends on the tuning of hyperparameters, and further research is needed to refine selection procedures for these parameters.\\
+
+All in all, the Triple-Gamma Regularization offers a novel, flexible, and effective approach to penalized regression in high-dimensional settings.
+Its ability to unify and extend existing methods provides a valuable tool for both theoretical research and practical application in sparse modeling and high-dimensional data analysis.
+
+\section{Appendix}
+\subsection{Technical Specification of System used for Simulation}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{ll}
+\toprule
+\textbf{Specification} & \textbf{Details} \\
+\midrule
+Operating System       & Microsoft Windows 11 Pro, Version 10.0.22621 \\
+Processor              & \makecell[l]{Intel(R) Core(TM) i7-8565U CPU @ 1.80GHz\\4 Cores, 8 Threads} \\
+RAM                    & 16 GB DDR4 \\
+Graphics               & Intel(R) UHD Graphics 620 \\
+Storage                & 1TB SSD (C:) \\
+BIOS Version           & LENOVO N2HET74W (1.57), 01.06.2023 \\
+Virtualization Support & Enabled (Hyper-V, SLAT, Virtualization in Firmware) \\
+Available Virtual Memory & 28.8 GB \\
+Available Physical Memory & 15.8 GB \\
+\bottomrule
+\end{tabular}
+\caption{System specifications for simulation}
+\end{table}
+
 \newpage
-\section{List of Figures}
 \listoffigures
@@
 \newpage
-\section{List of Tables}
 \listoftables
+\newpage
 
 \newpage
-\section{References}
-
-\pagenumbering{roman}
-\setcounter{page}{\thesavepage}
+%\pagenumbering{roman}
+%\setcounter{page}{\thesavepage}
 \pagestyle{plain}

### 2024-10-06 01_latex/MScThesis_Econ.tex
Pre-Fix Up Commit

@@
 This thesis introduces the Triple-Gamma Regularization (TGR), a novel non-convex penalty term inspired by the Triple-Gamma prior, which provides increased flexibility in handling under- and overfitting in high-dimensional regression problems.
-The proposed method offers a unifying framework that bridges convex penalties like LASSO and non-convex penalties such as Gaussian and Arctan, allowing for fine-tuning of the regularization process through adjustable hyperparameters.
-First, a detailed theoretical derivation of the TGR is provided, highlighting its properties and advantages over existing regularization methods.
+The proposed method offers a unifying framework that bridges convex penalties like LASSO and non-convex penalties showing similar characteristics as Gaussian and Arctan penalites, allowing for fine-tuning of the regularization process through adjustable hyperparameters.
+First, a detailed theoretical derivation of the TGR is provided alongside an analysis of its properties and advantages over existing regularization methods.
 Then, a comprehensive simulation study is conducted to evaluate the performance of TGR under various high-dimensional scenarios.
-The results indicate that TGR can outperform traditional regularization techniques in several settings, particularly in terms of minimizing mean squared error.
+The results indicate that TGR can outperform traditional regularization techniques in several settings, specifically in terms of minimizing the mean squared error on validation sets.
 This thesis also addresses the computational challenges associated with non-convex optimization problems and explores potential solutions through gradient-based optimization techniques.
-These findings contribute to the growing body of literature on regularization methods and offer practical insights for future applications in sparse modeling and high-dimensional data analysis.
+These findings contribute to the growing body of literature on regularization methods and offer practical insights for future applications in sparse modelling and high-dimensional data analysis.
 \end{abstract}
@@
 
-This completion oft this thesis would not have been possible without so many amazing people in my life who supported me throughout the process of writing this master's thesis and the master program as a whole.
+The completion of this thesis would not have been possible without so many amazing people in my life who supported me throughout the process of writing this master's thesis and the master program as a whole.
 I want to thank my mum, Daniela, and my dad, Werner, who always picked me up when I lost my motivation to continue and who convinced me to keep going time after time.
 I want to thank my brother, Tobias, who always readily listened to me complaining for hours and hours on end about things he probably barely understood and yet always agreed with me about my computational issues while doing the simulations.
-And most of all I want to thank my advisor, Peter, who always supported me from the day I randomly dropped an e-mail into his e-mail inbox about becoming his tutor in econometrics, although not having met once during the distance learning phase of the COVID pandemic, up until today.
+And most of all I want to thank my advisor, Peter, who always supported me from the day I randomly dropped an e-mail into his e-mail inbox about becoming his tutor in econometrics, although not having met me once during the distance learning phase of the COVID pandemic, up until today.
 From working as a tutor in his team, writing a bachelor thesis, and to the support during this master thesis now.
-Even though sometimes living 12h time differences apart, one in Boston the other in Manila, he always answered any questions I had and supported me in whatever way he could and I want to sincerely thank him for that!
+Even though sometimes living 12h time differences apart, one in Boston and the other in Manila, he always answered any questions I had and supported me in whatever way he could and I want to sincerely thank him for that!
 
@@
 Its unifying properties and the fact that a closed-form solution for the marginal prior exists might lead to favourable properties in the realm of frequentist statistics.
-Before that it is necessary to have a closer look at what the exact problem is that Bayesian shrinkage priors and regularization approaches are trying to solve.
+Before that, it is necessary to have a closer look at what the exact problem is that Bayesian shrinkage priors and regularization approaches are trying to solve.
 An overview of this along with a theoretical basis of the necessary concepts will be presented in section 2.\\
@@
 
-The first of these two goals - \textit{inference} - aims at understanding the relationship that may or may not exist between the input variables $\mathbf{X_i}$ and the output $\mathbf{Y}$.
-Especially applied sciences like Economics, Psychology and Medicine often try to find a (causal) relationship within their theoretical framework to evaluate a policy, a medication or a new form of therapy.
+The first of these two goals - \textit{inference} - aims at understanding the relationship that may or may not exist between the input variables $\mathbf{X_p}$ and the output $\mathbf{Y}$.
+Especially applied sciences like economics, psychology and medicine often try to find a (causal) relationship within their theoretical framework to evaluate a policy, a medication or a new form of therapy.
 Linear models for example often provide a simple and straightforward framework which provide the scientist with interpretable effects.
-\textit{Prediction} on the other hand aims at forecasting the output variable $Y$ as accurately as possible and using every bit of information that is available, but disregards interpretability \parencite[21]{ESL2009}.
+\textit{Prediction} on the other hand aims at forecasting the output variable $\mathbf{Y}$ as accurately as possible and using every bit of information that is available, but disregards interpretability \parencite[21]{ESL2009}.
 These goals can be summarized by viewing it as a decision between \textit{prediction accuracy} and \textit{model interpretability}, which has thoroughly been explained by \textcite{ESL2009}.\\
@@
 In supervised learning, a model is fitted on an observed dataset where both inputs and outputs are given in pairs.
-Using this data a statistical model aims to find a functional form which maps these inputs into the output space and thus describes a relationship between those two spaces.
+Using this data, a statistical model aims to find a functional form which maps these inputs into the output space and thus describes a relationship between those two spaces.
 Naturally, one would assume to find a functional form which manages to describe the relationship as closely as possible by minimizing a chosen loss function.
@@
 
-In general, a linear regression model fitted with least squares on a sufficient amount of data points ($n \gg p$) will produce estimates which both have low bias and low variance and thus tends to perform well out of sample.
+In general, a linear regression model fitted with least squares on a sufficient amount of data points ($n \gg p$) will produce estimates which both have low bias and low variance and thus tends to perform well out-of-sample.
 However, problems arise with this approach arise when the sample size decreases, because the variance in the estimates will increase.
-The main idea behind this can be easily be visualized by trying to fit a polynomial curve on a two dimensional space and then altering the available sample for polynomials of different order.
+The main idea behind this can be easily be visualized by trying to fit a polynomial curve on a two dimensional space with only a few data points and then altering the available sample for polynomials of different order.
 \begin{figure}
@@
 \includegraphics[scale=0.5]{PolynomialFit_Plot.png}
-\caption{1st and 8th order polynomial fit to data \\ (\textcolor{green1}{Green} \& \textcolor{blue1}{Blue} Lines fitted with red data point; \textcolor{orange1}{Orange} \& \textcolor{red1}{Red} Lines fitted without).}
+\caption{1st and 8th order polynomial fit to data \\ (\textcolor{green1}{Green} \& \textcolor{blue1}{Blue} lines fitted with red data point; \textcolor{orange1}{Orange} \& \textcolor{red1}{Red} lines fitted without).}
 \label{fig:polyfit}
@@
 \]
-\textit{Regularization} in this thesis' context refers then to adding some penalty function $J(\beta)$ dependent on the set of parameters $\beta$, multiplied by some weighting parameter $\lambda$, to the empirical risk functional $R_{emp}(\beta)$.
-Thus, $R_{reg} = R_{emp}(\beta) + \lambda\cdot J(\beta)$.
+\textit{Regularization} in this thesis' context refers then to adding some penalty function $J(\mathbf{\beta})$ dependent on the set of parameters $\mathbf{\beta}$, multiplied by some weighting parameter $\lambda$, to the empirical risk functional $R_{emp}(\mathbf{\beta})$.
+Thus, $R_{reg} = R_{emp}(\beta) + \lambda\cdot J(\mathbf{\beta})$.
 This results in the overall optimization problem
@@
 
-It is important to note here that $J(\beta)$ is only a function of the coefficients $\beta$ and neither the targets $y_i$ nor the inputs $x_i$.
-Therefore, it only affects the generalization error of the model, not the training error given by the empirical risk functional $R_{emp}(\beta)$.
+It is important to note here that $J(\mathbf{\beta})$ is only a function of the coefficients $\beta$ and neither the targets $y_i$ nor the inputs $x_i$.
+Therefore, it only affects the generalization error of the model, not the training error given by the empirical risk functional $R_{emp}(\mathbf{\beta})$.
 
@@
 The closed from solution of the Ridge estimator is given by
-$$\hat{\beta}_{Ridge} = \left(X^TX+\lambda I\right)^{-1}X^Ty,$$
+$$\hat{\mathbf{\beta}}_{Ridge} = \left(\mathbf{X}^T\mathbf{X}+\lambda \mathbf{I}\right)^{-1}\mathbf{X}^T\mathbf{y},$$
 which adjusts the OLS estimator by shifting the main diagonal entries of the design matrix by $\lambda$ ($\lambda \geq 0$).
 It can be shown that this closed form estimator is equivalent to a Lagrangian problem of the following form \parencite{VanWieringen2015}:
-$$\hat{\beta}_{Ridge}(\lambda) = \underset{\beta}{\argmin}\left\{\norm{y-X\beta}_2^2 + \lambda\norm{\beta}_2^2\right\}.$$
-This resembles an example of the above defined regularization framework with squared residual loss and a penalty term of the form $\norm{\beta}_2^2$, which only depends on the parameter $\beta$.
+$$\hat{\beta}_{Ridge}(\lambda) = \underset{\beta}{\argmin}\left\{\norm{\mathbf{y}-\mathbf{X}\mathbf{\beta}}_2^2 + \lambda\norm{\mathbf{\beta}}_2^2\right\}.$$
+This resembles an example of the above defined regularization framework with squared residual loss and a penalty term of the form $\norm{\mathbf{\beta}}_2^2$, which only depends on the parameter $\beta$.
 In case of $\lambda$ being equal to zero, this reduces to the \textit{maximum likelihood (ML) estimator}.
@@
 
-$$\norm{\beta}_p =  \left(\sum_{i=1}^p|\beta_i|^p\right)^{1/p}.$$
-
-Work published by researchers in the nineties, like the previously mentioned \textcite{FrankFriedman1993} or \textcite{Fu1998}, as well as more recent literature like \textcite{WangEtAl2020} have repeatedly shown there is no go-to-method to tackle regularization problems, as the effectiveness of a specific approach highly depends on the data siuation at hand.
+$$\norm{\mathbf{\beta}}_p =  \left(\sum_{i=1}^p|\beta_i|^p\right)^{1/p}.$$
+
+Work published by researchers in the nineties, like the previously mentioned \textcite{FrankFriedman1993} or \textcite{Fu1998}, as well as more recent literature like \textcite{WangEtAl2020} have repeatedly shown there is no go-to-method to tackle regularization problems, as the effectiveness of a specific approach highly depends on the data situation at hand.
 Due to this particular situation in the literature, several other methods have been proposed in the recent years and decades.
 An approach combining the \textit{Ridge} and \textit{LASSO} methods is called \textit{Elastic Net} regularization and has been developed by \textcite{ZouHastie2005}.
-The authors there elaborate on some of the shortcomings of the LASSO method.
+There, the authors elaborate on some of the shortcomings of the LASSO method.
 For example, in a special case where there are more predictors $p$ than data points $n$ ($p > n$), LASSO only selects up to $n$ variables due to the nature of the convex optimization problem.
-Should several of the included variables be highly \textit{pairwise} correlated with each other, \textit{LASSO} tends to only select on of these variables.
-In its core, \textit{Elastic Net Regularization} linearly combines the penalty terms of \textit{Ridge} and \textit{LASSO} regularization, yielding a loss function of the form:\\
-$$J(\beta) = \lambda_1 \norm{\beta}_2^2 + \lambda_2 \norm{\beta}_1.$$
+Should several of the included variables be highly \textit{pairwise} correlated with each other, \textit{LASSO} tends to only select one of these variables.
+At its core, \textit{Elastic Net Regularization} linearly combines the penalty terms of \textit{Ridge} and \textit{LASSO} regularization, yielding a loss function of the form:\\
+$$J(\mathbf{\beta}) = \lambda_1 \norm{\mathbf{\beta}}_2^2 + \lambda_2 \norm{\mathbf{\beta}}_1.$$
 The authors have	 shown that, especially when it comes to encouraging the aforementioned grouping effects, \textit{Elastic Net} tends to perform better than the \textit{LASSO}.\\
@@
 (Is it smooth or singular at origin?) and (2) Is the underlying function convex or non-convex?
-To better incorporate the proposed concept of this thesis into this body of literature, I am proposing a third property to distinguish penalty terms: (3) How does the function behave in the limits?
+To better incorporate the proposed concept of this thesis into this body of literature, I am proposing a third property to distinguish penalty terms: (3) How does the function behave at its limits?
 (Does it converge or diverge?) Such a classification tree can be found in figure \ref{fig:Classification}.
@@
 \end{figure}
-As already mentioned earlier in section \ref{sec:theorysuper}, a penalty function is a function dependent on the parameter of the model and it does not depend on the data at hand.
+As already mentioned earlier in section \ref{sec:theorysuper}, a penalty function is a function dependent on the parameters of the model and it does not depend on the data at hand.
 Thus, changes in your data set does not effect the penalty directly, but only the overall optimization problem through the empirical risk functional $R_{emp}$.
 The following table \ref{tab:ClassificationOfPenalties} classifies some of the existing concepts based on the three criteria mentioned earlier.
-A visualisation of them can be found in figure \ref{fig:DifferentPenalties} in chapter \ref{subsec:comparepenalties}.\\
+A visualisation of some of them can be found in figure \ref{fig:DifferentPenalties} in chapter \ref{subsec:comparepenalties}.\\
 
@@
 SCAD & \textcite{FanLi2001} & Singular & NC &\\
-Laplace & \textcite{TrzaskoManduca2009} & NC &&\\
+Laplace & \textcite{TrzaskoManduca2009} & Singular & NC &\\
 Triple-Gamma & - & \makecell{Depending\\ on \\ parameters} & NC & Div. \\
@@
 Both approaches aim at tackling the issue of model complexity and overfitting by making it necessary for the data to be more convincing that the value of an estimate is statistically significant different from zero.
-As mentioned, Bayesian statistics use specific prior distributions with a usually a lot of mass around zero and heavy tails, whereas frequentist statisticians usually alter their optimization problems incorporating penalty terms into into their loss functions.
+As mentioned, Bayesian statistics use specific prior distributions with usually a lot of mass around zero and heavy tails, whereas frequentist statisticians usually alter their optimization problems by incorporating penalty terms into into their loss functions.
 On a first glance, these two approaches have no immediate mathematical connection, however this turns out to be wrong.\\
@@
 
-It turns out, as can be seen in \textcite[248--250]{ESL2009} and \textcite{VanWieringen2015} among others, that when choosing certain prior distributions and using standard assumptions in Bayesian modelling (ie the individual parameters of the parameter vector are independent a priori and the errors of the standard linear model are drawn from a normal distribution), that the mode of the posterior distributions correspond to the point estimates of a regularization approach in a frequentist setting.
+It turns out, as can be seen in \textcite[248--250]{ESL2009} and \textcite{VanWieringen2015} among others, that when choosing certain prior distributions and using standard assumptions in Bayesian modelling (ie the individual parameters of the parameter vector are independent a priori and the errors of the standard linear model are iid drawn from a normal distribution), that the mode of the posterior distributions correspond to the point estimates of a regularization approach in a frequentist setting.
 As this idea is essential to the entire thesis, a shortened derivation of this duality for the case of \textit{Ridge} regression will now be shown.\\
@@
 Assuming that a response variable $y_i$ follows a linear model with $p$ variables and errors $\epsilon_i \sim \mathcal{N}(0, \sigma^2)$, then the likelihood of the data is given by
-$$\mathcal{L}(y|X,\beta)=\frac{1}{(2\pi\sigma^2)^{n/2}}\exp\left(-\frac{1}{2\sigma^2}\sum_{i=1}^n(y_i-x_i^T\beta)^2\right).$$
-
-Under the previously mentioned assumption that $p(\beta) = \prod_{i=1}^k \beta_i$ and by choosing a Gaussian distribution with mean zero and variance $\tau^2$, we gain the prior distribution
-$$p(\beta) = \frac{1}{(2\pi\tau^2)^{p/2}}\exp\left(-\frac{1}{2\tau^2}\norm{\beta}_2^2\right).$$
+$$\mathcal{L}(\mathbf{y}|\mathbf{X},\mathbf{\beta})=\frac{1}{(2\pi\sigma^2)^{n/2}}\exp\left(-\frac{1}{2\sigma^2}\sum_{i=1}^n(y_i-\mathbf{x_i}^T\mathbf{\beta})^2\right).$$
+
+Under the previously mentioned assumption that $p(\beta) = \prod_{i=1}^p \beta_i$ and by choosing a Gaussian distribution with mean zero and variance $\tau^2$, we gain the prior distribution
+$$p(\beta) = \frac{1}{(2\pi\tau^2)^{p/2}}\exp\left(-\frac{1}{2\tau^2}\norm{\mathbf{\beta}}_2^2\right).$$
 
 Putting both together using Bayes' theorem and taking the $\log$ of the distribution yields
-$$\log(p(\beta|y,X)) \propto -\frac{1}{2\sigma^2}\sum_{i=1}^n (y_i-x_i^T\beta)^2  - \frac{1}{2\tau^2}\norm{\beta}_2^2.$$
-
-By viewing $\frac{1}{2\tau^2}$ as the weighting parameter $\lambda$, which controls the strength of the regularization.
+$$\log(p(\mathbf{\beta}|\mathbf{y},\mathbf{X})) \propto -\frac{1}{2\sigma^2}\sum_{i=1}^n (y_i-\mathbf{x_i}^T\mathbf{\beta})^2  - \frac{1}{2\tau^2}\norm{\mathbf{\beta}}_2^2.$$
+
+Here, $\frac{1}{2\tau^2}$ can be viewed as the weighting parameter $\lambda$, which controls the strength of the regularization.
 The \textit{maximum-a-priori} estimate $\hat{\beta}_{MAP}$, which can be viewed as trying to find the $\underset{\beta}{\argmax}$ of the $\log$-posterior, can be used to construct the following optimization problem:
 
-$$\hat{\beta}_{MAP} = \underset{\beta}{\argmin}\left\{\frac{1}{2\sigma^2}\sum_{i=1}^n \epsilon_i^2  + \frac{1}{2\tau^2}\norm{\beta}_2^2\right\}.$$
+$$\hat{\beta}_{MAP} = \underset{\beta}{\argmin}\left\{\frac{1}{2\sigma^2}\sum_{i=1}^n \epsilon_i^2  + \frac{1}{2\tau^2}\norm{\mathbf{\beta}}_2^2\right\}.$$
 
 This optimization problem constitutes the connection between the Bayesian and the frequentist approach as it can be interpreted as (1) finding the mode of the posterior distribution when using a Gaussian prior distribution and (2) finding the parameters which minimize the loss when using a Ridge regression with $\lambda = 1/(2\tau^2)$.
-The same connection exists for the case of \textit{LASSO} regression which can be derived using the same procedure and a double-exponential - also called \textit{Laplace} - distribution with mean zero and some scale parameter $\tau$ as the prior for the parameter vector $\beta$.
+The same connection exists for the case of \textit{LASSO} regression which can be derived using the same procedure and a double-exponential - also called \textit{Laplace} - distribution with mean zero and some scale parameter $\tau$ as the prior for the parameter vector $\mathbf{\beta}$.
 
@@
 Another advantage is its function as a bridge between spike-and-slab and continuous shrinkage prior as the hyperparameters can be used both for steering the shrinkage effect on noise while also preventing overshrinking the signal.
-Computationally the shrinkage prior performs better than commonly used spike-and-slab priors as it is a continuous shrinkage prior which can more easily be implemented using Markov-Chain-Monte-Carlo (MCMC) methods.\\
+Computationally, the shrinkage prior performs better than commonly used spike-and-slab priors as it is a continuous shrinkage prior which can more easily be implemented using Markov-Chain-Monte-Carlo (MCMC) methods.\\
 
@@
 Coming to the theoretical framework of the \textit{triple-gamma-regularization}, let's assume we have a response variable $y$ and $p$ predictors along with $n$ data points.
-More formally, let $y=[y_1  \quad y_2 \cdots y_n]^T$ and $x_i = [x_{i1} \quad x_{i2} \cdots x_{ip}]^T$ with $\forall i\in \{1,...,n\}: y_i, x_{ij} \in \mathbb{R}$.
-Here, $x_i$ is the $i$-th predictor, thus resulting in the design matrix $X = [x_1 \quad x_2 \cdots x_p]$.\\
+More formally, let $\mathbf{y}=[y_1  \quad y_2 \cdots y_n]^T$ and $\mathbf{x_i} = [x_{i1} \quad x_{i2} \cdots x_{ip}]^T$ with $\forall i\in \{1,...,n\}: y_i, x_{ij} \in \mathbb{R}$.
+Here, $x_i$ is the $i$-th data point, thus resulting in the design matrix $\mathbf{X} = [\mathbf{x_1} \quad \mathbf{x_2} \cdots \mathbf{x_n}]^T$.\\
 
@@
 \[
-y_i = x_i^T\cdot \beta + \varepsilon_i, \quad i\in \{1,...,n\}, 
+y_i = \mathbf{x_i}^T\cdot \mathbf{\beta} + \varepsilon_i, \quad i\in \{1,...,n\}, 
 \]
 with the assumed distribution of $\varepsilon_i \sim N(0,\sigma^2)$.
-Thus it follows that $y\sim N_n(X\beta,\sigma^2I)$.
-The posterior distribution of the parameter vector $\beta$, according to Bayes' Rule, is then proportional to the product of the likelihood of the data and the prior distribution, which can be seen in equation \ref{eq:bayes}.
+Thus, it follows that $y\sim N_n(\mathbf{X}\mathbf{\beta},\sigma^2I)$.
+The posterior distribution of the parameter vector $\mathbf{\beta}$, according to Bayes' Rule, is then proportional to the product of the likelihood of the data and the prior distribution, which can be seen in equation \ref{eq:bayes}.
 \begin{equation}\label{eq:bayes}
-p(\beta|y, X, \sigma^2) \propto \mathcal{L}(y|\beta, \sigma^2, X)\times p(\beta)
+p(\mathbf{\beta}|\mathbf{y}, \mathbf{X}, \sigma^2) \propto \mathcal{L}(\mathbf{y}|\mathbf{\beta}, \sigma^2, \mathbf{X})\times p(\mathbf{\beta})
 \end{equation}
 
-As stated above, each data point $y_i$ is assumed to be independently drawn from a normal distribution with mean $X\beta$ and variance $\sigma^2$, thus:
+As stated above, each data point $y_i$ is assumed to be independently drawn from a normal distribution with mean $\mathbf{X}\mathbf{\beta}$ and variance $\sigma^2$, thus:
 \begin{align}
-\mathcal{L}(\mathbf{y}|\beta, \sigma^2, X) 	&= \prod_i^n p(y_i|\beta, \sigma^2, x_i) \nonumber\\
-						&= \prod_i^n \frac{1}{\sqrt{2\pi\sigma^2}} \exp\left(-\frac{1}{2}\left(\frac{x_i-\mu}{\sigma}\right)^2\right) \nonumber\\
+\mathcal{L}(\mathbf{y}|\beta, \sigma^2, \mathbf{X}) 	&= \prod_i^n p(y_i|\beta, \sigma^2, \mathbf{x_i}) \nonumber\\
+						&= \prod_i^n \frac{1}{\sqrt{2\pi\sigma^2}} \exp\left(-\frac{1}{2}\left(\frac{\mathbf{x_i}-\mu}{\sigma}\right)^2\right) \nonumber\\
 						&= \frac{1}{(2\pi\sigma^2)^{n/2}}\exp\left(-\frac{1}{2\sigma^2}(\mathbf{y}-\mathbf{X}\beta)^\top(\mathbf{y}-\mathbf{X}\beta)\right) \label{eq:likelihood}
@@
 \begin{align}
-p(\beta) 	&= \prod_j^p p(\beta_j) \nonumber\\
+p(\mathbf{\beta}) 	&= \prod_j^p p(\beta_j) \nonumber\\
 			&= \prod_j^p p(\beta_j|\phi^\xi, a^\xi, c^\xi) \nonumber\\
@@
 \[
-\log(p(\beta))=\log(\prod_j^p p(\beta_j|\phi^\xi, a^\xi, c^\xi))=\sum_j^p \log(p(\beta_j|\phi^\xi, a^\xi, c^\xi)).
+\log(p(\mathbf{\beta}))=\log(\prod_j^p p(\beta_j|\phi^\xi, a^\xi, c^\xi))=\sum_j^p \log(p(\beta_j|\phi^\xi, a^\xi, c^\xi)).
 \]
@@
 \]
-where $f(x|\beta)$ describes the the probability density function of a variable $x$, which is parametrized by the parameter vector $\beta$.
-The second function $g(\beta)$ incorporates our prior information about the parameter vector $\beta$ into the optimization problem.\\
+where $f(x|\beta)$ describes the the probability density function of a variable $x$, which is parametrized by the parameter vector $\mathbf{\beta}$.
+The second function $g(\mathbf{\beta})$ incorporates our prior information about the parameter vector $\mathbf{\beta}$ into the optimization problem.\\
 
@@
 \begin{align}
-p(\beta|y, X, \sigma^2) 	&\propto p(y|X,\beta,\sigma)\times p(\beta) \nonumber\\
-						&\propto \frac{1}{(2\pi\sigma^2)^{n/2}}e^{-\frac{1}{2\sigma^2}(y-X\beta)^T(y-X\beta)} \times \prod_j^p U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right).\label{eq:posterior}
+p(\mathbf{\beta}|\mathbf{y}, \mathbf{X}, \sigma^2) 	&\propto p(\mathbf{y}|\mathbf{X},\mathbf{\beta},\sigma)\times p(\mathbf{\beta}) \nonumber\\
+						&\propto \frac{1}{(2\pi\sigma^2)^{n/2}}e^{-\frac{1}{2\sigma^2}(\mathbf{y}-\mathbf{X}\mathbf{\beta})^T(\mathbf{y}-\mathbf{X}\mathbf{\beta})} \times \prod_j^p U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right).\label{eq:posterior}
 \end{align}
@@
 \begin{align}
-\log(\beta| X, y, \sigma^2) 	&= \log\left(\frac{1}{(2\pi\sigma^2)^{n/2}}\right) - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \log\left(\prod_j^p U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right)\nonumber\\
+\log(\beta| \mathbf{X}, \mathbf{y}, \sigma^2) 	&= \log\left(\frac{1}{(2\pi\sigma^2)^{n/2}}\right) - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta}_2^2 + \log\left(\prod_j^p U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j^2}{2\phi^\xi}\right)\right)\nonumber\\
 							&= \log\left(\frac{1}{(2\pi\sigma^2)^{n/2}}\right) - \frac{1}{2\sigma^2}\norm{\mathbf{y} - \mathbf{X}\beta^2}_2^2 + \sum_j^p \log\left(U\left(c^\xi + \frac{1}{2}, \frac{3}{2}-a^\xi, \frac{\beta_j}{2\phi^\xi}\right)\right)\nonumber\\
@@
 In contrast to the \textit{LASSO} penalty, which uses the the absolute value of the coefficient, or the \textit{Ridge} penalty, which uses the square of the estimate, this penalty derived from \textcite{TGP2020} is based on the $\log$ of the confluent hyper-geometric of the second kind introduced by \textcite{Tricomi1947}.
-Notably, this penalty term has three additional hyper-parameters: $c^\xi$, $a^\xi$ and $\kappa_B$ as $\phi^\xi = (2c^\xi)/(\kappa^2_B a^\xi)$.
-Here, the restrictions $a^\xi>0.5$ and $0 < c^\xi < \infty$ are necessary to ensure that the penalty for a $\beta_j$ being equal to zero remains finite and not diverges to negative infinity at zero.
+Notably, this penalty term has three additional hyper-parameters: $c^\xi$, $a^\xi$ and $\kappa_B^2$ as $\phi^\xi = (2c^\xi)/(\kappa^2_B a^\xi)$.
+Here, the restrictions $a^\xi>0.5$ and $0 < c^\xi < \infty$ are necessary to ensure that the penalty for a $\beta_j$ being equal to zero remains finite and does not diverges to negative infinity at zero.
 This result, which has already been presented and proven as part of Theorem 2 in \textcite[5--6]{TGP2020}, ensures that the negative $\log$ of the hypergeometric function remains finite and thus does not produce parameter estimates which are zero for every variables.\\
@@
 It can easily be seen from the figure that $a^\xi$ steers the sharpness of the penalty in small neighbourhoods around $\beta=0$.
-As $a^\xi$ increases, the penalty because smoother at $\beta=0$ with it eventually converging a \textit{Gaussian Penalty} like behaviour.
+As $a^\xi$ increases, the penalty because smoother at $\beta=0$ with it eventually converging to a \textit{Gaussian Penalty} like behaviour.
 From a modelling perspective, this opens up the possibility of steering the degree of variable selection the penalty performs.
-Nonetheless, the overall structure of the penalty in the tails does not change systematically apart from a parallel shift, which can be readjusted by specifying a different weighting parameter $\lambda$ or a different value for $\kappa_B$ (more on effect of $\kappa_B$ on the penalty can be found later in this chapter).\\
+Nonetheless, the overall structure of the penalty in the tails does not change systematically apart from a parallel shift, which can be readjusted by specifying a different weighting parameter $\lambda$ or a different value for $\kappa_B$ (more on effect of $\kappa_B^2$ on the penalty can be found later in this chapter).\\
 
@@
 The effect of the first subset of values for $c^\xi$ which are strictly greater than $0$ but less or equal than $0.1$ can be found in figure \ref{fig:ChangeInC_SmallValues} (as already mentioned before, by definition, $c^\xi$ has to be strictly greater than zero: $c^\xi > 0$).
-Here, it can be seen that as the values for $c^\xi$ become smaller, a shifting effect takes place which generally does not influence the overall structure of the penalty, but increases the amount of penalty which is added to the risk function for $\beta$-values which are different from zero (In a sense, this has a similar effect to changes in $\kappa_B$, which will be explained later).
+Here, it can be seen that as the values for $c^\xi$ become smaller, a shifting effect takes place which generally does not influence the overall structure of the penalty, but increases the amount of penalty which is added to the risk function for $\beta$-values which are different from zero (In a sense, this has a similar effect to changes in $\kappa_B^2$, which will be explained later).
 Or, to put it differently, with values of $c^\xi$ closer to zero, the data has be even more convincing that the value is significantly different from zero.\\
@@
 
-\textit{Variations of the Hyperparameter $\kappa_B$}\\
+\textit{Variations of the Hyperparameter $\kappa_B^2$}\\
 
@@
 Setting 2&	$5$  &   $0.01$ & $2$\\
-Setting 3&  $0.51$  & $0.001$&$1$\\ \bottomrule
+Setting 3&  $0.51$  & $0.01$&$1$\\ \bottomrule
 \end{tabular}
@@
 
-\textit{Setting 1} is a \textit{LASSO} like regularization penalty, but still keeps the non-convex shape of the Triple-Gamma penalty.
+\textit{Setting 1} is a \textit{LASSO}-ish like regularization penalty, but still keeps the non-convex shape of the Triple-Gamma penalty.
 \textit{Setting 2} introduces the smooth-at-origin property but keeps a similar shape than \textit{setting 1} in the tails.
@@
 Additionally, a comparison of these \textit{Triple-Gamma} settings to a selection of other regularization penalties can be found in figure \ref{fig:DifferentPenalties}.
-As can be seen here, \textit{setting 1} of the \textit{Triple-Gamma} penalty imitates a \textit{LASSO} penalty with a slightly decreasing additional penalty, resulting in a weakened bias which is common to \textit{LASSO} estimates.
+As can be seen here, \textit{setting 1} of the \textit{Triple-Gamma} penalty imitates a \textit{LASSO}-ish like penalty with a slightly decreasing additional penalty, resulting in a weakened bias which is common to \textit{LASSO} estimates.
 \textit{Setting 3} has a similar structure than the non-convex penalties \textit{Gaussian} and \textit{Arctan}, but with a string singularity at zero.
@@
 \section{Simulation Study}\label{sec:simstudy_overall}
-To test the proposed method of section \ref{sec:modelderivation} a simulation study will now be conducted whether, and if so, in what scenarios, the \textit{Triple-Gamma} penalty might be valuable addition to the literature.
+To test the proposed method of section \ref{sec:modelderivation}, a simulation study will now be conducted whether, and if so, in what scenarios, the \textit{Triple-Gamma} penalty might be a valuable addition to the literature.
 Of course several previously introduced methods have also been tested using simulation studies, but the methodology behind these studies usually varies from paper to paper.
@@
 For the simulation study testing the models prediction accuracy the key metric to test performance will be the \textit{mean-squared-error (MSE)}.
-The data is being generated the following way: Given a set of scenario parameters $N_i$, $p_i$ and $sd_i$, the first $s_i*p_i$ coefficients, rounded to the next larger integer, will be set to $3$ and the remaining will be set to $0$.
+The data is being generated the following way: Given a set of scenario parameters $N_i$, $p_i$ and $s_i$, the first $s_i*p_i$ coefficients, rounded to the next larger integer, will be set to $3$ and the remaining will be set to $0$.
 Then, $N_i$ draws will be generated from a normal distribution with mean $0$ and variance $1$ for each of the $p_i$ features.
@@
 In terms of the regularization parameter $\lambda$, the search for the optimal $\lambda$ will be performed by using five-fold-cross-validation on the a set of possible $\lambda$ values.
-For every method and every run in every scenario separately, the optimal $\lambda^*_i$ will be chosen which generates the lowest validation loss on the testset.
+For every method and every run in every scenario separately, the optimal $\lambda^*_i$ will be chosen which generates the lowest validation loss on the test set.
 This grid-serach procedure will be performed for every $\lambda_i \in \{0.001, 0.01, 0.1, 0.25, 0.4, 0.5, 0.6, 0.75, 0.9, 0.95\}$.\\
@@
 \includegraphics[scale=0.6]{../02_simulation/021_simulation_figures/Boxplot_Scenario_100_50_25.png}
-\caption{Distribution of MSE on Validation Set in the Scenario with $100$ Observations, $50$ Features and $25$ non-zero Coefficients}
+\caption{Distribution of MSE on validation set in the scenario with $100$ observations, $50$ features and $25$ non-zero coefficients}
 \label{fig:SpecificScenario2}
@@
 \toprule
-\multicolumn{3}{c}{Scenario Parameters} & \multicolumn{2}{c}{Moment}\\
+\multicolumn{3}{c}{Scenario Parameters} & \multicolumn{2}{c}{Measure}\\
 \midrule
@@
 \end{tabular}
-\caption{Table showing the best performing methods according to smallest Mean and Median Loss accordingly}
+\caption{Table showing the best performing methods according to smallest mean and median loss accordingly}
 \label{tab:bestmethod}
@@
 \includegraphics[scale=0.6]{../02_simulation/021_simulation_figures/ComputationTime_Example.png}
-\caption{Time necessary to compute all three scenarios of the Triple-Gamma-Regularization with $N=100$ and $s=0.1$ dependent on the number of Features $p$}
+\caption{Time necessary to compute all three scenarios of the Triple-Gamma-Regularization with $N=100$ and $s=0.1$ dependent on the number of features $p$}
 \label{fig:ComputationTime}
@@
 Setting aside that it might even grow exponentially, it can be seen that the computation time also increasingly becomes more unstable.
-Several approaches might help in resolving these issues, like optimizing the underlying approximation of the confluent hypergeometric funciton or choosing a different estimation algorithm altogether (see section 6.1).
+Several approaches might help in resolving these issues, like optimizing the underlying approximation of the confluent hypergeometric function or choosing a different estimation algorithm altogether (see section 6.1).
 Another approach could be to implement the underlying estimation in a more efficient programming language when it comes to runtime like C++.
@@
 
-\caption{Mean and Standard Deviations of MSE on the Validation Set for different Scenarios (15 runs per scenario)} \\
+\caption{Mean and standard deviations of MSE on the validation set for different scenarios (15 runs per scenario)} \\
 \toprule
@@
 
-\makecell{\texttt{TripleGamma-}\\\texttt{Regularization}} & Here a class is defining a simple neural network.
+\makecell[l]{\texttt{TripleGamma-}\\\texttt{Regularization}} & Here a class is defining a simple neural network.
 It uses the \texttt{nn.Module} and initializes a linear model with 10 input features and 1 output feature without an intercept.
@@
 It takes the feature matrix (\texttt{X}), the target values (\texttt{y}), the regularization parameter (\texttt{penalty}), regularization hyper-parameters \texttt{a}, \texttt{c}, \texttt{kappa}, the number of epochs (\texttt{num\_epochs}), and the learning rate (\texttt{lr}) as input.
-It initializes the \texttt{PyTorch} model and optimizer, uses Gradient Descent to train the model for the specified number of epochs, and returns the trained model, a list of model coefficients for each epoch, and a list of loss values for each epoch.\\
+It initializes the \texttt{PyTorch} model and optimizer, uses Stochastic Gradient Descent to train the model for the specified number of epochs, and returns the trained model, a list of model coefficients for each epoch, and a list of loss values for each epoch.\\
 \hline
@@
 This new regularization method bridges existing convex approaches like LASSO with newer non-convex penalties such as Arctan and Gaussian, offering increased flexibility in addressing the challenges of underfitting and overfitting in high-dimensional regression settings.
-The theoretical foundation of TGR was derived by leveraging the mathematical connection between frequentist regularization techniques and Bayesian shrinkage priors.
+The theoretical foundation of TGR was derived by exploiting the mathematical connection between frequentist regularization  and Bayesian shrinkage priors.
 Through this connection, a penalty structure was derived which allows for a more flexible tuning of hyperparameters to achieve a balance between bias and variance.
 The flexibility of TGR lies in its three hyperparameters, which control the behaviour of the penalty structure at both the origin and the tails.
-This allows it to handle scenarios where existing penalties may fall not sufficiently solve problems.\\
+This allows it to handle scenarios where existing penalties may not sufficiently solve problems.\\
 
 A key feature of \textit{TGR} is its ability to perform both continuous shrinkage and variable selection, making it a versatile alternative in high-dimensional data analysis.
-Compared to existing regularization methods, such as LASSO and Ridge, \textit{TGR} offers the advantage of a more refined approach to penalization.
-This was supported by the simulation study conducted, which demonstrated that TGR performs competitively across a variety of high-dimensional settings, sometimes even outperforming conventional methods in terms of mean-squared error reduction.
+Compared to existing regularization methods, such as LASSO and Ridge, \textit{TGR} offers the advantage of a more adjustable approach to penalization.
+This was supported by the simulation study, which demonstrated that TGR can perform better across several high-dimensional data settings, sometimes even outperforming conventional methods in terms of mean-squared error reduction.
 Downsides include the computational challenges posed by non-convex optimization problems, which are inherent in methods like \textit{TGR}.
@@
 All in all, the Triple-Gamma Regularization offers a novel, flexible, and effective approach to penalized regression in high-dimensional settings.
-Its ability to unify and extend existing methods provides a valuable tool for both theoretical research and practical application in sparse modeling and high-dimensional data analysis.
+Its ability to unify and extend existing methods provides a valuable tool for both theoretical research and practical application in sparse modelling and high-dimensional data analysis.
+
+\newpage
 
